### 2022-09-26 docs/manuscript/main.tex
v0.0.1a9
Some manuscript updates

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{algorithm2e}

\title{AGEAS: Automated Machine Learning based Genetics Featrue Extraction System}

\author[1,2,*1,+]{Jack Yu}
% \author[1,2,*1]{Jack Yu}
\author[2,+]{Masayoshi Nakamoto}
\author[1,*2,+]{Jiawang Tao}

% \author[2,+]{Derek Author}
\affil[1]{Center for Health Research, Guangzhou Institutes of Biomedicine and Health, Chinese Academy of Sciences, Guangzhou 510530, China}
\affil[2]{Shenzhen Mozhou Technology Co., Ltd, Shenzhen, China}
% \affil[2]{Affiliation, department, city, postcode, country}
\affil[*1]{Correspondence: gyu17@alumni.jh.edu}
\affil[*2]{Correspondence: tao\_jiawang@gibh.ac.cn}

\affil[+]{these authors contributed equally to this work}
\keywords{Machine Learning, Gene Regulatory Network, RNA-Seq, Chip-Seq}

\begin{abstract}
  Abstract goes here
\end{abstract}

\begin{document}
\flushbottom
\maketitle

\thispagestyle{empty}
% \noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

\section*{Method}
  \label{method}
  The basic principle of \emph{AGEAS} is to find key genetic features regulating phenotype of interest through analyzing how well-performing classification models distinguish gene regulatory networks (GRNs) of sample with the phenotype from GRNs of samples.
  To reconstruct sufficient GRNs for each class, RNA-seq based expression data is segmented into subsets while each one is analogized as a pseudo-sample having discrete expression data.
  The pseudo-sample GRNs (psGRNs) are reconstructed accordingly; thus, classification models can be trained, evaluated, and interpreted having gene regulatory pathways (GRPs) as input factors.
  With heavily weighted GRPs and associated genes repeatedly obtained from interpretations of success sample class predictions, regulons could be formed and inferred as genetic feature complexes playing important role in differentiating the studying sample classes.
  The overall workflow can be summarized as Figure \ref{workflow}.
  Following sections describe each step of \emph{AGEAS} in more depth.
  % \begin{itemize}
  %   \item \hyperref[step1]{\textbf{\emph{Step 1}}}: Data preprocessing
  %   \item \hyperref[step2]{\textbf{\emph{Step 2}}}: Classification model selection.
  %   \item \hyperref[step3]{\textbf{\emph{Step 3}}}: Feature selection...
  %   \item \hyperref[step4]{\textbf{\emph{Step 4}}}: Top GRP extraction.
  %   \item \hyperref[step5]{\textbf{\emph{Step 5}}}: Key network reconstruction.
  % \end{itemize}
  \begin{figure}[ht]
  \centering
  % \includegraphics[width=0.8\linewidth, height=18cm, keepaspectratio,]{../images/summary_trans.png}
  \includegraphics[width=0.8\linewidth, keepaspectratio,]{../images/summary_trans.png}
  \caption{
    The overall workflow of \emph{AGEAS}:
    \textbf{\emph{(1)}} Reconstruct meta-level GRN (meta-GRN) with expression data of all samples.
    \textbf{\emph{(2)}} Build pseudo-samples with sliding window algorithm and reconstruct GRNs with GRPs identified in meta-GRN accordingly.
    \textbf{\emph{(3)}} Select best performing classifiers in predicting class labels of pseudo-sample GRNs (psGRNs).
    \textbf{\emph{(4)}} Interpret how top models make classifications and gradually exclude GRPs with low weights or outlier-level high weights.
    \textbf{\emph{(5)}} Repeatedly train classifiers with differnt set of psGRNs as training data to extract GRPs frequently ranked as top important features for decision.
    \textbf{\emph{(6)}} Reconstruct regulons with extracted GRPs and GRPs excluded as significant outliers.
  }
  \label{workflow}
  \end{figure}

  \subsection*{Step 1:Data preprocessing}
    \label{step1}
    The main purpose of this step is to build pseudo-samples and reconstruct corresponding pseudo-sample GRNs (psGRNs).
    % Instead of finding genes being important to differentiate sample classes and infer gene regulatory networks (GRNs) with the genes,
    For each sample class, gene expression matrices (GEMs) labeled with same class label are concatenated as one comprehensive expression matrix.
    With comprehensive GEMs, a meta-level GRN (meta-GRN) is reconstructed in advance of psGRNs to provide generic guidance on reconstruction.
    In general, the workflow of this step can be represented as Figure \ref{data_preprocess}.

    \subsubsection*{Reconstruct meta-GRN}
      Firstly, genes included in the comprehensive GEMs are assessed and determined whether having potential to form informative GRPs with other genes.
      Commonly, differentially expressed genes (DEGs) would be considered as important factors of studying feature.
      Here we apply the Mann-Whitney U rank test (MWW) implemented by \emph{SciPy}\cite{2020SciPy-NMeth} to exclude genes having indistinguishable expression level distribution across GEMs of different classes.
      The p-value for rejecting null hypothesis, that expression distribution underlying class 1 samples is the same as the expression distribution underlying class 2 samples, is set to 0.05 by default.
      Furthermore, a $\log_2$ fold change (log2FC) filter is also implemented in \emph{AGEAS}.
      However, enabling the log2FC filter is not encouraged considering upstream transcription factors (TFs) indirectly regulating key genes associated with feature of interest may not always have significant expression level difference between sample classes.
      The lof2FC filter shall mostly be used in order to decrease meta-GRN's GRP total amount in a compromising position caused by limited computational resources.
      After differential expression based filters, a standard deviation ($\sigma$) filter is applied to exclude genes either having low expression value or merely affected by dynamic expression status of other genes.
      By default, the $\sigma$ threshold is set to 1.0 consisting with the lowest expression level in raw gene count matrix gained from RNA-Seq data.
      The threshold value should be adjusted corresponding to prior knowledge of input GEMs, for example of what normalization method was applied to the GEMs.

      With candidate genes passed filters above, some gene pairs are formed and assessed potential of representing GRPs.
      To reduce overall computational complexity, a gene pair shall be formed with at least one TF which could be the regulatory source of GRP.
      If not further specified, TF list will be retrieved from integrated \emph{TRANSFAC}\cite{transfac} datasets according to the provided species information.
      Utilizing genetic interaction database like \emph{GTRD}\cite{gkaa1057} and \emph{BioGRID}\cite{biogrid}, \emph{AGEAS} checks whether the binding ability of gene pair is confirmed or not.
      By default, if TF being recorded to have binding site within target gene's promoter range (-1000 to +100) by Chip-Seq dataset retrieved from \emph{GTRD}\cite{gkaa1057}, the potential GRP gene pair will be passed to expression correlation assessment.
      For TFs not covered by interaction database, \emph{GRNBoost2}\cite{grnboost2}-like algorithm is initiated to predict potential regulatory target genes.
      The prediction importance threshold can either be set manually or automatically based on recorded interactions as:

      \centerline{$Threshold = min(GA(M_1, t)\, \uplus \, GA(M_2, t), \frac{1}{g})$}

      \noindent Here $GA()$ denotes \emph{GRNBoost2}\cite{grnboost2}-like algorithm;
      $M_1$ is concatenated class 1 samples GEM with genes passed filters;
      $M_2$ is concatenated class 2 samples GEM with genes passed filters;
      $t$ is the TF having largest amount of recorded interaction in dataset;
      $g$ is total amount of unique genes in all samples passed filters.

      After potential GRP gene pairs obtained, a expression correlation filter is used to exclude gene pairs having low covariance which implies weak relationship.
      To assess expression correlation, \emph{AGEAS} applies Pearson's Correlation coefficient\cite{pcc_2012} (PCC) whihc is one of the widely adopted methods\cite{cid_2019}.
      With default setting, gene pairs can reach absolute correlation coefficient of 0.2 while keeping correspond p-value lower than 0.05 are included in meta-GRN as validated GRP.

    \subsubsection*{Reconstruct psGRNs}
      The comprehensive GEMs is divided into few sample subsets with sliding window algorithm (SWA) to build pseudo-samples.
      With SWA, we can gain GEM of \emph{i-th} pseudo-sample through:

      \centerline{$SWA(i) = \left\{{x_j}_{j = i * p}^{j + k}\right\}, j + k < l$}

      \noindent Here $l$ is number of samples in a comprehensive GEM which can be expressed as $\left\{{x_j}_{j = 0}^{l}\right\}$; $k$ denotes window size; $p$ denotes padding stride.

      If sample amount is considerably low or imbalanced, customized window size and padding stride can be applied to generate sufficient amount of pseudo-samples for later classifier training and assessment processes.
      Utilizing meta-GRN, psGRNs are reconstructed with GEMs of pseudo-sample.
      Each GRP gene pair in meta-GRN is formed with expression data in pseudo-sample and filtered by same PCC filter in meta-GRN reconstruction process.
      After all pseudo-samples have been used to reconstruct psGRN, every psGRN will have GRP rearranged by unified order.

    \begin{figure}[ht]
      \centering
      % \includegraphics[width=0.8\linewidth, height=12cm, keepaspectratio,]{../images/data_preprocess_trans.png}
      \includegraphics[width=0.8\linewidth, keepaspectratio,]{../images/data_preprocess_trans.png}
      \caption{
        Workflow to reconstruct meta-GRN and psGRNs.
        \textbf{\emph{(1)}} Filter genes from GEMs with log2FC filter(optional), MWW filter, and $\sigma$ filter.
        \textbf{\emph{(2)}} Find candidate GRP gene pairs from either interaction database or predictions made by \emph{GRNBoost2}\cite{grnboost2}-like algorithm.
        \textbf{\emph{(3)}} Filter candidate GRP gene pairs with PCC filter and reconstruct meta-GRN with validated GRPs.
        \textbf{\emph{(4)}} Generate pseudo-samples with SWA.
        \textbf{\emph{(5)}} Utilize GRPs in meta-GRN as generic guidance to form candidate GRPs for pseudo-samples.
        \textbf{\emph{(6)}} Filter every candidate GRP for all pseudo-samples with PCC filter and reconstruct psGRNs with validated GRPs.
      }
      \label{data_preprocess}
    \end{figure}

  \subsection*{Step 2: Classification model selection}
    \label{step2}
    Since \emph{AGEAS} is not aiming to develop optimized model architectures for psGRN classification but gain insights from multiple models as divergent as possible, the main goal of this step is to select configurations of models capable to make correct psGRN classifications from provided configuration set.
    Regarding the fact that computational power is limited resource, portion of less efficient model configurations shall be pruned although interpreting success predictions of more classification models would lead to more comprehensive insight into sample class differences.
    Therefore, we apply a simple Hyperband\cite{hyperband}-based algorithm \ref{alg:one} which performs grid search for well-performing classification models with varying model training resource and pruning aggressiveness.

    %% This declares a command \Comment
    %% The argument will be surrounded by /* ... */
    \SetKwComment{Comment}{/* }{ */}
    \SetKwInput{kwInput}{Input}
    \SetKwInput{kwReturn}{Return}
    \RestyleAlgo{ruled}
    \begin{algorithm}
    \caption{Model selection algorithm}
    \label{alg:one}
    \kwInput{$R, C, I$ (default $I = 3$), $\alpha_{max}$(default $\alpha_{max} = 0.9$),  $k_{min}$(default $k_{min} = 0.5$)}
    $\alpha_{low} = \frac{1}{(2 ^ {I} - 1)}$\;
    % $X \gets x$\;
    \For{$i \in \{0, 1, ..., I-1\}$}{
      \eIf{$i == I-1$}{
        $\alpha = \alpha_{max}$\;
        % $X \gets X \times X$\;
        % $N \gets \frac{N}{2}$
        % \Comment*[r]{This is a comment}
      }{
        $alpha = 2^i \alpha_{low}$\;
      }
      $r = \alpha R$\;
      $P = \emptyset $\;
      \For{$c \in C$}{
        $p = run\_then\_evaluate(c, r, R)$\;
        Append $p$ to $P$\;
      }
      % \If{$N$ is odd}{
      %   }

      $k = max(1 - \alpha, k_{min}$)\;
  	  $C = top\_configs(C, P, k$)\;
    }
    \kwReturn{$C$}
    \end{algorithm}

    The model selection algorithm requires five inputs
    (1)$R$, the maximum amount of training resource, equivalent to all avaliable psGRNs
    (2)$C$, the total set of provided classification model configurations
    (3)$I$, the number of iterations for model pruning (default set as 3)
    (4)$\alpha_{max}$, the maximum portion of $R$ can be fed to single model (default set as 0.95)
    (5)$k_{min}$, the minimum portion of remaining model configurations will be kept by single pruning iteration (default set as 0.5).
    Furthermore, two functions are also required while need to be defined based on input model configurations:
    \begin{itemize}
    \setlength\itemsep{0em}
    \item \textbf{$run\_then\_evaluate(c, r, R)$}: trains classification model initialized using configuration $c$ for the allocated resource $r$, then returns prediction accuracy (ACC), the area under a receiver operating characteristic curve (AUROC)\cite{hanley_mcneil_1982} score, and total cross-entropy loss ($L_{CE}$) calculated through predicting sample class for all psGRNs $R$.

    \item \textbf{$top\_configs(C, P, k)$}: takes a set of model configurations $C$ with associated evaluation results $P$ and returns configurations having ACC, AUROC score, or $L_{CE}$ reaching top $k$ portion.
    \end{itemize}

    \noindent By default, \emph{AGEAS} initializes with 128 model configurations utilizing 9 integrated classification algorithms listed in Table \ref{models}.

    \begin{table}[ht]
      \centering
      \begin{tabular}{|l|l|l|l|l|}
      \specialrule{.2em}{.1em}{.1em}
      \textbf{Algorithm} & \textbf{$\# \lambda$} & \textbf{Categorical} & \textbf{Continuous} & \textbf{$\#$ Configs}\\
      \specialrule{.2em}{.1em}{.1em}
      \multicolumn{5}{|l|}{\emph{Implemented with Pytorch}\cite{NEURIPS2019_9015}} \\
      \hline
      Transformer & \textbf{14} & 4 & 10 & 32 \\
      \hline
      1D Convolutional Neural Network (1D-CNN) & \textbf{10} & 2 & 8 & 32 \\
      \hline
      Hybrid Convolutional Neural Network (Hybrid-CNN) & \textbf{10} & 2 & 8 & 32 \\
      \hline
      Gated Recurrent Unit (GRU) & \textbf{10} & 4 & 6 & 4 \\
      \hline
      Long Short-Term Memory (LSTM) & \textbf{11} & 4 & 7 & 4 \\
      \hline
      Standard Recurrent Neural Network (RNN) & \textbf{11} & 5 & 6 & 4 \\
      \specialrule{.2em}{.1em}{.1em}
      \multicolumn{5}{|l|}{\emph{Implemented with XGBoost}\cite{chen2016xgboost}} \\
      \hline
      Gradient Boosted Decision Trees (GBDT) & \textbf{18} & 5(1) & 13(4) & 16 \\
      \specialrule{.2em}{.1em}{.1em}
      \multicolumn{5}{|l|}{\emph{Implemented with scikit-learn}\cite{scikit-learn}} \\
      \hline
      Random Forests (RF) & \textbf{14} & 5(1) & 9(1) & 2 \\
      \hline
      Support Vector Machine (SVM) & \textbf{7} & 4 & 3(3) & 2 \\
      \specialrule{.2em}{.1em}{.1em}
      \end{tabular}
      \caption{
        \label{models}
        Classification model algorithms integrated in \emph{AGEAS} with correspond numbers of hyperparameter and preset model configurations.
        Categorical hyperparameters and continuous numerical hyperparameters are clarifed beside total number of hyperparameters ($\# \lambda$).
        Conditional hyperparameters which are required for selected other hyperparameters are shown in brackets if there is any.
        $\#$ Configs indicates total amount of configurations \emph{AGEAS} applies by default.
      }
    \end{table}

    The general architecture designs of 1D-CNN and Hybrid-CNN are implemented referring to 1D-CNN and 2D-Hybrid-CNN applied in recent cancer type prediction study\cite{mostavi_chiu_huang_chen_2020}.
    However, taking one convolution layer and adjacent max-pooling layer as a layer set, we implemented both CNN models with flexibilities on number of layer set, which is fixed as 1 in original research.
    An example of 1D-CNN with 2 convolution layer sets is illustrated in Figure \ref{1dCNN}.

    \begin{figure}[ht]
      \centering
      \includegraphics[width=0.8\linewidth]{../images/nn.png}
      \caption{1D-CNN with 2 convolution layer set.}
      \label{1dCNN}
    \end{figure}

    For transformer models, considering psGRNs are already be represented by numerical data matrix while GRPs should barely have positional relationships in the matrix, the embedding layer and positional encoding layer designed for input data tokenization in standard architecture \cite{transformer} are replaced with a single linear layer in \emph{AGEAS}.

  \subsection*{Step 3: Feature selection}
    \label{step3}
    With selected well-performing models, \emph{AGEAS} already can start repetition of model training and interpretation in \hyperref[step4]{Step 4} to extract key GRPs.
    However, few uninformative GRPs in training psGRNs merely relied by any model to make classification could be pruned in advance for saving computational power.
    Furthermore, to prevent classification models focusing on a small group of GRPs regardless of training psGRNs, GRPs draw excessive attention shall also be seperated from psGRNs to improve extraction comprehensiveness.
    Thus, in this step, \emph{AGEAS} iteratively train classificaion models with dynamic $\alpha_{max}$ portion of psGRNs and obtain feature importance scores as described in \hyperref[features_importances]{subsection} below to find GRPs either scored extremely high or considerably low.

    More specifically, at each iteration, GRPs having z-scores ranked as bottom $b$ portion (default set as 0.1) are discarded.
    Also, an $i$-th ranked GRP will be seperated from psGRNs and passed to \hyperref[step5]{Step 5} directly if having z-score fulfilling the condition:

    \centerline{
      $Z_{score}^{i} \ge max(Z_{score}^{thread}, \frac{Z_{score}^{i-1}}{3}, 3 \cdot IQR)$
    }

    \noindent The $Z_{score}^{thread}$ is input z-score threshold (default set as 3.0), and $IQR$ stands for interquartile range calculated by the beginning of each iteration.\
    With this criterion, \emph{AGEAS} ensures only GRPs draw significantly more attention shall be selected by each iteration despite the data distribution of varying z-score scalled importance values.

    By default, \emph{AGEAS} iterates this feature selection step for 3 times.

    \subsubsection*{Feature importance estimation}
      \label{features_importances}
      \emph{AGEAS} applies concept of The Shapley value\cite{roth_1988} for estimating importance of each input feature, equivalent to GRP of input psGRN, in any kind of classification model while making predictions.
      Specific Shapley value calculation or approximating methods are implemented with \emph{SHAP}\cite{lundberg2017unified} and applied to different algorithms as shown in Table \ref{shap}.
      Regarding the standard differences between feature importance estimating methods, we utilize \emph{softmax} function to normalize feature importances and define the normalized importance calculation function as:

      \centerline{$T(X) = softmax(\left\{ F(x) \right\}, x \in X)$}

      \noindent Here $X$ is total set of all features, and $F(x)$ is the importance estimating method of individual classification model being interpreted.\
      If the feature importances can be approached with internalized method $f(x)$, $F(x)$ is set as:

      \centerline{$F(x) = \frac{f(x)}{\sum_{x' \in X} f(x')}$}

      \noindent Otherwise, $F(x)$ is defined utilizing correctly classified input samples $S$, equivalent to psGRNs, with Shapley values $\phi$ of feature $x$ when predicting sample $s$ as class $c_1$ or class $c_2$:\

      \centerline{$F(x) = \sum_{s \in S}\frac{\left|\phi_{c_1,s}^{x}\right| + \left|\phi_{c_2,s}^{x}\right|}{2}$}

      \noindent After all selected classification models $M$ have been interpreted, we can intergrate the feature importances matrices weighted with corresponding models' $L_{CE}$ to one matrix $A$ as:\

      \centerline{
        $ A = \left\{ \sum_{m \in M}(1 - L_{CE}^{m})T_{m}(x) \right\}, x \in X $
      }

      \noindent Then, generalized importance values are obtained through z-score calculation and later sorted by descending order:\

      \centerline{
        $Z_{score} = \left\{\frac{a - \bar{A}}{\sigma_A}\right\}, a \in A$
      }

      \begin{table}[ht]
        \centering
        \begin{tabular}{|l|l|}
        \specialrule{.2em}{.1em}{.1em}
        \textbf{Algorithm} & \textbf{SHAP\cite{lundberg2017unified} Method}\\
        \hline
        Transformer & Gradient Explainer \\
        \hline
        1D-CNN & Deep Explainer \\
        \hline
        Hybrid-CNN & Deep Explainer \\
        \hline
        GRU & Gradient Explainer \\
        \hline
        LSTM & Gradient Explainer \\
        \hline
        RNN & Gradient Explainer \\
        \hline
        GBDT\textbf{*} & Tree Explainer \\
        \hline
        RF & Tree Explainer \\
        \hline
        SVM\textbf{*} & Linear Explainer / Kernel Explainer\\
        \specialrule{.2em}{.1em}{.1em}
        \end{tabular}
        \caption{
          \label{shap}
          Classifier algorithms with applicable Shapley value approximating methods.
          Algorithms marked with \textbf{*} have internalized feature importance estimating methods which will be applied with higher priority than Shapley value based methods.
          GBDT implemented with \emph{XGBoost}\cite{chen2016xgboost} can have feature importance approximated with average weight gain at each split involving the feature.
          Linear SVM implemented with \emph{scikit-learn}\cite{scikit-learn} can have the importance estimated with feature coefficient or using Linear Explainer.
          However, for SVM with kernel function, the feature coefficient estimation would be inappropriate, and feature importances should be approximated with Kernel Explainer.
        }
      \end{table}

  \subsection*{Step 4: Top GRP extraction}
    \label{step4}
    To extract GRPs can effectively define sample class differences, \emph{AGEAS} iteratively initializes classification models with configurations gained from \hyperref[step2]{Step 2}, trains them with varying $\alpha_{max}$ portion of psGRNs scaled after \hyperref[step3]{Step 3}, and interpret every models' correct predictions as mentioned in \hyperref[features_importances]{subsection} above.
    At each iteration, \emph{AGEAS} receives a z-score scaled feature importance matrix $A$ and add up each GRP's score accordingly from matrix $A'$ kept from previous iteration if there is one.
    Then, top $a$ (default set as 100) ranked GRPs having z-score greater than $0.0$ extracted from $A$ are compared with GRPs extracted from $A'$ by same setting.
    If less than $d$ (default set as 0.05) portion of GRPs are distinct for GRP sets stratified from $A$ and $A'$, \emph{AGEAS} will consider the GRP extration result from this iteration consists with previous one.
    Extraction iteration will terminate if either encountering $n$ (default set as 3) continuous consisting result or running out of preset iteration number (default set as 10).
    All feature importance scores in matrix $A$ from last iteration are divided by total extraction iteration number processed, and top $a$ ranked GRPs are considered as key GRPs for sample class differentiation and passed to next step.

  \subsection*{Step 5: Key network reconstruction}
    \label{step5}
    Analoging every GRP previously extracted or seperated with high z-score in \hyperref[step3]{Step 3} as a directional edge connecting two gene vertices, equivalent to a TF and a gene, in graph theory, \emph{AGEAS} attempts to reconstruct a network graph representing regulatory differences between query sample classes.
    Since there is no guarantee on all GRP edges can be connected, some regulatory relationships between gene vertices could be missed.
    Hence, \emph{AGEAS} utilizes meta-GRN gained from \hyperref[step1]{Step 1} to find GRPs which can further elucidate the regulatory relationships and adds the GRPs back to the network graph.

    For a limited iteration time (default set as  1), \emph{AGEAS} exhaustively search meta-GRN for TFs which can directly regulate any genes or TFs already covered in the network graph and add the returned TFs as new vertices.
    Next, any GRP in meta-GRN capable to connect two distinct vertices will be added if it is not covered yet.
    The network graph after expansion above represents the key genetic regulatory differences \emph{AGEAS} extracted from input sample classes.

  % With feature list ranked according to importance values, \emph{AGEAS} reconstructs regulon for top-ranked GRPs and extracts influential genes among the regulon.
  % If analoging regulon with the graph concept in discrete mathematics, one of the most common methods to analyze influence of a vertex, which is equivalent to a gene, is assessing correspond degree of the vertex.
  % Although the regulatory source and target of GRP can be determined by utilizing interaction database, such as \emph{GTRD}\cite{gkaa1057} which shows regulatory relationship of interactors, numerous computational prediction methods like \emph{GRNBoost2}\cite{grnboost2} and comprehensive interaction database, \emph{BioGRID}\cite{biogrid} for example, could not provide faithful indication on regulatory directions.
  % Consequently, based on choice of interaction database, the regulon reconstructed with \emph{AGEAS} cannot be guaranteed to be a directed graph but an undirected graph.
  % Therefore, in this step, \emph{odysseia} primarily extracts genes with high regulatory degrees in the regulon, regardless of they act as source or target in GRPs.
  % To limit total amount of output key genes, the default setting of \emph{AGEAS} reconstructs regulon for top 100 GRPs, and genes with regulatory degree higher than two in the regulon will be considered influential.
  % If regulatory directions can be clarifed, the regulatory sources capable of regulating multiple key genes and the regulatory targets influenced by multiple key genes can also be extracted according to GRN reconstruction guidance.
  %
  % In the circumstance of finding genes potentially inducing CS conversion, referred as \emph{Mogrify}\cite{mogrify_2016}, both CS deterministic genes and common regulators of these genes shall gain attention.
  % Herein, \emph{AGEAS} analogized key genes extracted from top GRPs as CS deterministic genes and TFs capable of regulating more than 2 listed key genes as significant common regulator.
  %
  % Both non-convergence issue and feature lost issue reflect on one of the key problems for $AutoML$: "No single machine learning method performs best on all datasets".\cite{NIPS2015_11d0e628}
  % Even though this problem can be solved while viewing $AutoML$ as a $CASH$ problem \cite{thornton2013auto}, such approach may not be directly deployable in our scenario considering comprehensive CS deterministic GFs or GRPs could be hardly labeled out.
  % Hence, in contrast with directly automating key features finding process, we decide to partially automate CS classification process and export candidate components of joint algorithm to feature importance analysis.
  % Compared with applying a particular $ML$ model, $CASH$ solving process during automation have higher potential to utilize comprehensive key features instead limited set of them.
  % Furthermore, due to the network-based essence of \emph{AGEAS}, some CS deterministic features failed to be detected after classification model analysis, if having close regulatory relationships with multiple confirmed GFs, can still be traced down during regulon-based analysis at post stage analysis.

\section*{Results}
  \label{res}

\section*{Discussion}
  \label{disc}

% \section*{Conclusion}
  % \label{conc}
  % Conclusion goes here

\bibliography{reference}

% For data citations of datasets uploaded to e.g. \emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.

\section*{Author contributions statement}
\textbf{J.Y.}: Methodology, Software, Writing- Original draft preparation, Project administration
\textbf{M.N.}: Methodology, Software
\textbf{J.T.}: Writing - Review \& Editing, Project administration

\section*{Additional information}
All scRNA-seq datasets are retrieved from Gene Expression Omnibus(GEO) as described in the Table below.

\begin{table}[ht]
  \centering
  \begin{tabular}{|l|l|}
  \specialrule{.2em}{.1em}{.1em}
  \textbf{Sample Class} & \textbf{Accession number}\\

  \specialrule{.2em}{.1em}{.1em}
  \multicolumn{2}{|l|}{GSE103221} \\
  \hline
  MEF & GSM3629847 \\
  \hline
  ESC & GSM3629848 \\

  \specialrule{.2em}{.1em}{.1em}
  \multicolumn{2}{|l|}{GSE137720 } \\
  \hline
  a6w hsc & GSM4085625 \\
  \hline
  a6w pf & GSM4085627 \\
  \hline
  healthy hsc & GSM4085623 \\
  \hline
  healthy pf & GSM4085626 \\

  \specialrule{.2em}{.1em}{.1em}
  \multicolumn{2}{|l|}{GSE185275 } \\
  \hline
  neural co-culture & GSM5609927 \\
  \hline
  purified neurons & GSM5609930 \\

  \specialrule{.2em}{.1em}{.1em}
  \multicolumn{2}{|l|}{GSE156482 } \\
  \hline
  p4 cm & GSM4732219 \\
  \hline
  p7 cm & GSM4732221 \\
  \hline
  p28 cm & GSM4732225 \\
  \hline
  p28 ncm & GSM4732226 \\

  \specialrule{.2em}{.1em}{.1em}
  \end{tabular}
  \caption{
    \label{geo_table}
    GEO data source table.
  }
\end{table}

% $CASH$        & Combined Algorithm Selection and Hyperparameter optimization\\
\end{document}

% \begin{enumerate}
% \setlength\itemsep{0em}
% \item {\textbf{Gene level}}:
% sth
% \begin{itemize}
% \setlength\itemsep{0em}
% \item \textbf{SD Filter}: sth
% sth
% \end{itemize}
% \item {\textbf{Pathway level}}:
% sth
% \begin{itemize}
% \setlength\itemsep{0em}
% \item \textbf{GRP Filter}: sth
% sth
% \end{itemize}
% \end{enumerate}

### 2022-09-26 ageas/__init__.py

@@ -25,8 +25,8 @@ AGEAS
 ========
 Summary
 -------
-AGEAS (AutoML-based Genomics fEatrue extrAction System)
-is to find key genomics factors, including genes and regulatory pathways,
+AGEAS (AutoML-based Genetics fEatrue extrAction System)
+is to find key genetics factors, including genes and regulatory pathways,
 in determining cellular phenotype.
 
 For more information, please visit our GitHub repo:
@@ -49,7 +49,7 @@ from ._unit import (
 )
 
 from ._visualizer import (
-    Plot_Regulon
+    Plot
 )
 
 from ._psgrn import (
@@ -65,5 +65,5 @@ __all__ = [
     'Data_Preprocess',
     'Launch',
     'Unit',
-    'Plot_Regulon',
+    'Plot',
 ]

### 2022-09-26 ageas/_main.py

@@ -40,8 +40,8 @@ class Launch:
 				 correlation_thread:float = 0.2,
 				 database_path:str = None,
 				 database_type:str = 'gem_files',
-				 group1_path:str = None,
-				 group2_path:str = None,
+				 class1_path:str = None,
+				 class2_path:str = None,
 				 interaction_database:str = 'gtrd',
 				 log2fc_thread:float = None,
 				 meta_load_path:str = None,
@@ -154,8 +154,8 @@ class Launch:
 			correlation_thread = correlation_thread,
 			database_path = database_path,
 			database_type = database_type,
-			group1_path = group1_path,
-			group2_path = group2_path,
+			class1_path = class1_path,
+			class2_path = class2_path,
 			interaction_database = interaction_database,
 			log2fc_thread = log2fc_thread,
 			meta_load_path = meta_load_path,
@@ -217,7 +217,7 @@ class Launch:
 
 	def save_reports(self,
 					 folder_path:str = None,
-					 regulon_header:str = 'regulon_',
+					 network_header:str = 'network_',
 					 save_unit_reports:bool = False,
 					):
 		"""
@@ -228,8 +228,8 @@ class Launch:
 		:param folder_path: <str Default = None>
 			Path to create folder for saving AGEAS report files.
 
-		:param regulon_header: <str Default = 'regulon_'>
-			The name header for each regulon in atlas.
+		:param network_header: <str Default = 'network_'>
+			The name header for each network in atlas.
 
 		:param save_unit_reports: <bool Default = False>
 			Whether saving key GRPs extracted by each AGEAS Unit or not.
@@ -257,7 +257,7 @@ class Launch:
 				atlas.grps.save(report_path + 'grps_importances.csv')
 				json.encode(atlas.outlier_grps, report_path + 'outlier_grps.js')
 
-		self.atlas.report(self.meta.grn, header = regulon_header).to_csv(
+		self.atlas.report(self.meta.grn, header = network_header).to_csv(
 			folder_path + 'report.csv',
 			index = False
 		)
@@ -268,8 +268,8 @@ class Launch:
 		)
 
 		json.encode(
-			{regulon_header + str(k):v.as_dict() for k,v in enumerate(
-				self.atlas.regulons)},
+			{network_header + str(k):v.as_dict() for k,v in enumerate(
+				self.atlas.nets)},
 			folder_path + 'full_atlas.js'
 		)
 
[…]

### 2022-09-26 ageas/_psgrn.py

@@ -27,8 +27,8 @@ import ageas.database_setup.binary_class as binary_db
 def Data_Preprocess(correlation_thread:float = 0.2,
 					database_path:str = None,
 					database_type:str = 'gem_files',
-					group1_path:str = None,
-					group2_path:str = None,
+					class1_path:str = None,
+					class2_path:str = None,
 					interaction_database:str = 'gtrd',
 					log2fc_thread:float = None,
 					meta_load_path:str = None,
@@ -54,10 +54,10 @@ def Data_Preprocess(correlation_thread:float = 0.2,
 	:param database_path: <str Default = None>
 		Database header.
 
-		If specified, group1_path and group2_path will be rooted here.
+		If specified, class1_path and class2_path will be rooted here.
 
 	:param database_type: <str Default = 'gem_files'>
-		Type of data group1_path and group1_path are directing to
+		Type of data class1_path and class1_path are directing to
 		Supporting:
 
 			'gem_files': Each path is directing to a GEM file.
@@ -72,11 +72,11 @@ def Data_Preprocess(correlation_thread:float = 0.2,
 
 		Pseudo-sample GRNs will be generated with sliding window method.
 
-	:param group1_path: <str Default = None>
-		Path to file or folder being considered as sample group 1 data
+	:param class1_path: <str Default = None>
+		Path to file or folder of class 1 samples data
 
-	:param group2_path: <str Default = None>
-		Path to file or folder being considered as sample group 2 data
+	:param class2_path: <str Default = None>
+		Path to file or folder of class 2 samples data
 
 	:param interaction_database: <str Default = 'gtrd'>
 		Which interaction database to use for confirming a GRP has a
@@ -155,12 +155,11 @@ def Data_Preprocess(correlation_thread:float = 0.2,
 
 	:param std_value_thread: <float Default = 1.0>
 		Set up gene expression standard deviation thread by value.
-		To filter genes having relatively constant expression in each
-		group.
+		To filter genes having relatively constant expression.
 
 	:param std_ratio_thread: <float Default = None>
 		Set up gene expression standard deviation thread by portion.
[…]

### 2022-09-26 ageas/_unit.py

@@ -106,7 +106,7 @@ class Unit(object):
 
         :param regulatory_trace_depth: <int Default = 1>
             Trace regulatory upstream of regulatory sources included in key
-            regulons extracted.
+            networks extracted.
 
         :param stabilize_patient: <int Default = 3>
             If stabilize iterations continuously having consistent
@@ -207,9 +207,9 @@ class Unit(object):
                 start = time.time()
                 prev_grps = self.atlas.top_grps.index
                 rm = self.__get_grp_remove_list(
-                            grp_importances.result,
-                            self.feature_dropout_ratio,
-                            self.outlier_thread
+                    grp_importances.result,
+                    self.feature_dropout_ratio,
+                    self.outlier_thread
                 )
 
                 self.pseudo_grns.update_with_remove_list(rm)
@@ -272,21 +272,21 @@ class Unit(object):
 
             print('Time to stabilize key GRPs : ', time.time() - start)
 
-    # Construct Regulons with Extracted GRPs and Access Them
+    # Construct networks with Extracted GRPs and Access Them
     def generate_atlas(self,):
         """
-        Function to build regulon networks with extracted GRPs.
+        Function to build networks with extracted GRPs.
         """
-        print('\nBuilding Regulons with key GRPs')
+        print('\nBuilding networks with key GRPs')
         start = time.time()
-        self.atlas.build_regulon(meta_grn = self.meta.grn,)
+        self.atlas.build_network(meta_grn = self.meta.grn,)
 
-        # Trace regulatory sources of regulons in atlas extracted
+        # Trace regulatory sources of networks in atlas extracted
         for i in range(self.regulatory_trace_depth):
             self.atlas.add_reg_sources(meta_grn = self.meta.grn,)
 
         self.atlas.find_bridges(meta_grn = self.meta.grn)
-        print('Time to build key regulons : ', time.time() - start)
+        print('Time to build key networks : ', time.time() - start)
         return self.atlas
 
     # take out some GRPs based on feature dropout ratio

### 2022-09-26 ageas/_visualizer.py

@@ -24,17 +24,17 @@ TYPES = ['Standard', 'Outer', 'Bridge', 'Mix']
 
 
 
-class Plot_Regulon(object):
+class Plot(object):
     """
-    Visualize full or partial Regulon extracted with AGEAS.
+    Visualize GRN or Regulon extracted with AGEAS.
 
     """
 
     def __init__(self,
                  depth:int = 1,
                  hide_bridge:bool = True,
-                 plot_group:str = 'all',
-                 regulon = None,
+                 plot_class:str = 'all',
+                 network = None,
                  root_gene:str = None,
                  weight_thread:float = 0.0,
                 ):
@@ -49,21 +49,21 @@ class Plot_Regulon(object):
             Whether hide non-AGEAS-extracted GRPs which can link key genes or
             not.
 
-        :param plot_group: <str Default = 'all'>
+        :param plot_class: <str Default = 'all'>
             What kind of information to show for GRPs on plot.
 
             Supporting:
 
-                'all': Which group of samples a GRP has higher correlation.
+                'all': In which sample class a GRP has higher correlation.
 
-                'group1': GRP's correlation value calculated with samples in
-                group1
+                'class1': GRP's correlation value calculated with samples in
+                class1
 
-                'group2': GRP's correlation value calculated with samples in
-                group2
+                'class2': GRP's correlation value calculated with samples in
+                class2
 
-        :param regulon: <ageas.tool.grn.GRN Default = None>
-            Which regulon to plot out.
+        :param network: <ageas.tool.grn.GRN Default = None>
+            Which network to plot out.
 
         :param root_gene: <str Default = None>
             Specific gene of interest. Only GRPs being capable to link with this
@@ -73,13 +73,13 @@ class Plot_Regulon(object):
         :param weight_thread: <float Default = 0.0>
             Minimun weight for a GRP to be kept on plot.
         """
-        super(Plot_Regulon, self).__init__()
-        self.plot_group = str(plot_group)
+        super(Plot, self).__init__()
+        self.plot_class = str(plot_class)
 
         if root_gene is not None:
-            grps_to_plot = regulon.get_grps_from_gene(root_gene, depth)
[…]

### 2022-09-26 ageas/classifier/__init__.py

@@ -121,13 +121,10 @@ class Make_Template:
 	# common func to evaluate both torch based and sklearn based API models
 	def _evaluate(self, output, label):
 		assert len(output) == len(label)
-		correct_predictions = []
-		for i in range(len(output)):
-			if output[i][0] > output[i][1] and label[i] == 0:
-				correct_predictions.append(i)
-			elif output[i][0] < output[i][1] and label[i] == 1:
-				correct_predictions.append(i)
-
+		correct_predictions = [
+			i for i in range(len(output)) if list(
+				output[i]).index(max(output[i])) == label[i]
+		]
 		auroc = roc_auc_score(label, output[:, 1], average = None)
 		loss = torch.nn.CrossEntropyLoss()(
 			torch.tensor(output, dtype = torch.float),

### 2022-09-26 ageas/classifier/gru.py

@@ -24,7 +24,9 @@ class GRU(nn.Module):
                  hidden_size,
                  dropout,
                  learning_rate,
-                 n_class = 2
+                 n_class = 2,
+                 bias = 'True',
+                 bidirectional = 'False',
                 ):
         super(GRU, self).__init__()
         self.id = id
@@ -36,7 +38,9 @@ class GRU(nn.Module):
             input_size,
             self.hidden_size,
             self.num_layers,
-            batch_first = True
+            batch_first = True,
+            bias = bias,
+            bidirectional = bidirectional
         )
         self.fc = nn.Linear(self.hidden_size, n_class)
         self.optimizer = torch.optim.Adam(self.parameters(), lr = learning_rate)

### 2022-09-26 ageas/classifier/lstm.py

@@ -27,7 +27,10 @@ class LSTM(nn.Module):
                  hidden_size,
                  dropout,
                  learning_rate,
-                 n_class = 2
+                 n_class = 2,
+                 bias = 'True',
+                 bidirectional = 'False',
+                 proj_size = 0,
                 ):
         super(LSTM, self).__init__()
         self.id = id
@@ -39,7 +42,10 @@ class LSTM(nn.Module):
             input_size,
             self.hidden_size,
             self.num_layers,
-            batch_first = True
+            batch_first = True,
+            bias = bias,
+            bidirectional = bidirectional,
+            proj_size = proj_size
         )
         self.fc = nn.Linear(self.hidden_size, n_class)
         self.optimizer = torch.optim.Adam(self.parameters(), lr = learning_rate)

### 2022-09-26 ageas/classifier/rnn.py

@@ -24,7 +24,11 @@ class RNN(nn.Module):
                  hidden_size,
                  dropout,
                  learning_rate,
-                 n_class = 2
+                 n_class = 2,
+                 nonlinearity = 'tanh',
+                 bias = 'True',
+                 bidirectional = 'False',
+
                 ):
         super(RNN, self).__init__()
         self.id = id
@@ -36,7 +40,10 @@ class RNN(nn.Module):
             input_size,
             self.hidden_size,
             self.num_layers,
-            batch_first = True
+            batch_first = True,
+            nonlinearity = nonlinearity,
+            bias = bias,
+            bidirectional = bidirectional
         )
         self.fc = nn.Linear(self.hidden_size, n_class)
         self.optimizer = torch.optim.Adam(self.parameters(), lr = learning_rate)

### 2022-09-26 ageas/classifier/transformer.py

@@ -11,7 +11,10 @@ import math
 import torch
 import torch.nn as nn
 import torch.nn.functional as func
-from torch.nn import TransformerEncoder, TransformerEncoderLayer
+from torch.nn import TransformerEncoder
+from torch.nn import TransformerEncoderLayer
+from torch.nn import TransformerDecoder
+from torch.nn import TransformerDecoderLayer
 import ageas.classifier as classifier
 
 
@@ -70,51 +73,67 @@ class Transformer(nn.Module):
                  has_mask = True, # whether using mask or not
                  emsize = 512, # size after encoder
                  nhead = 8, # number of heads in the multiheadattention models
-                 nhid = 200, # number of hidden units per layer
-                 nlayers = 2, # number of layers
+                 num_encoder_layers = 6,
+                 num_decoder_layers = 6,
+                 dim_feedforward = 512, # number of hidden units per layer
                  dropout = 0.5, # dropout ratio
+                 activation = 'relu',
+                 layer_norm_eps = 1e-05,
                  learning_rate = 0.1,
                  n_class = 2, # number of class for classification
                 ):
         super(Transformer, self).__init__()
         self.id = id
-        self.has_mask = has_mask
         self.model_type = 'Transformer'
         self.emsize = emsize
-        self.mask = None
-        self.encoder = nn.Linear(num_features, emsize)
-        self.pos_encoder = Positional_Encoding(emsize, dropout)
-        encoder_layers = TransformerEncoderLayer(emsize, nhead, nhid, dropout)
-        self.transformer_encoder = TransformerEncoder(encoder_layers, nlayers)
-        self.decoder = nn.Linear(emsize, n_class)
-        #self.optimizer = torch.optim.AdamW(self.parameters(), lr=learning_rate)
-        self.optimizer = None
+        self.has_mask = has_mask
+        self.embed = nn.Linear(num_features, emsize)
+        # self.pos_encoder = Positional_Encoding(emsize, dropout)
+
+        encoder_layer = TransformerEncoderLayer(
+            emsize, nhead, dim_feedforward, dropout, activation, layer_norm_eps
+        )
+        self.encoder = TransformerEncoder(encoder_layer, num_encoder_layers)
+
+        decoder_layer = TransformerDecoderLayer(
+            emsize, nhead, dim_feedforward, dropout, activation, layer_norm_eps
+        )
+        self.decoder = TransformerDecoder(decoder_layer, num_decoder_layers)
+
[…]

### 2022-09-26 ageas/data/config/list_config.js

@@ -17,20 +17,26 @@
       ],
       "nhead":[
         8,
-        4
+        16
       ],
-      "nhid":[
-        200
+      "dim_feedforward":[
+        256
       ],
-      "nlayers":[
-        2,
-        4
+      "num_encoder_layers":[
+        6
+      ],
+      "num_decoder_layers":[
+        6
+      ],
+      "layer_norm_eps":[
+        1e-05
       ],
       "learning_rate":[
           0.01
       ],
       "dropout":[
-          0.2
+          0.2,
+          0.1
       ]
   },
   "RFC": {
@@ -181,6 +187,15 @@
       ],
       "dropout":[
           0.2
+      ],
+      "nonlinearity":[
+          "tanh"
+      ],
+      "bias":[
+          true
+      ],
+      "bidirectional":[
+          false
       ]
   },
   "LSTM": {
@@ -203,6 +218,15 @@
       ],
       "dropout":[
           0.2
+      ],
+      "bias":[
+          true
+      ],
+      "bidirectional":[
+          false
+      ],
+      "proj_size":[
+          0
       ]
   },
   "GRU": {
@@ -225,6 +249,12 @@
       ],
       "dropout":[
           0.2
+      ],
+      "bias":[
+          true
+      ],
+      "bidirectional":[
+          false
       ]
   }
 }

### 2022-09-26 ageas/data/config/sample_config.js

@@ -4,11 +4,13 @@
             "config": {
                 "has_mask": false,
                 "emsize": 1024,
-                "nhead": 4,
-                "nhid": 200,
-                "nlayers": 4,
+                "nhead": 16,
+                "dim_feedforward": 256,
+                "num_encoder_layers": 6,
+                "num_decoder_layers": 6,
+                "layer_norm_eps": 1e-05,
                 "learning_rate": 0.01,
-                "dropout": 0.2
+                "dropout": 0.1
             },
             "epoch": 2,
             "batch_size": 10
@@ -17,11 +19,13 @@
             "config": {
                 "has_mask": false,
                 "emsize": 1024,
-                "nhead": 4,
-                "nhid": 200,
-                "nlayers": 4,
+                "nhead": 16,
+                "dim_feedforward": 256,
+                "num_encoder_layers": 6,
+                "num_decoder_layers": 6,
+                "layer_norm_eps": 1e-05,
                 "learning_rate": 0.01,
-                "dropout": 0.2
+                "dropout": 0.1
             },
             "epoch": 2,
             "batch_size": 5
@@ -30,9 +34,11 @@
             "config": {
                 "has_mask": false,
                 "emsize": 1024,
-                "nhead": 4,
-                "nhid": 200,
-                "nlayers": 2,
+                "nhead": 16,
+                "dim_feedforward": 256,
+                "num_encoder_layers": 6,
+                "num_decoder_layers": 6,
+                "layer_norm_eps": 1e-05,
                 "learning_rate": 0.01,
                 "dropout": 0.2
             },
@@ -43,9 +49,11 @@
             "config": {
                 "has_mask": false,
                 "emsize": 1024,
-                "nhead": 4,
-                "nhid": 200,
-                "nlayers": 2,
+                "nhead": 16,
+                "dim_feedforward": 256,
+                "num_encoder_layers": 6,
+                "num_decoder_layers": 6,
+                "layer_norm_eps": 1e-05,
                 "learning_rate": 0.01,
                 "dropout": 0.2
             },
@@ -57,10 +65,12 @@
                 "has_mask": false,
                 "emsize": 1024,
                 "nhead": 8,
-                "nhid": 200,
-                "nlayers": 4,
+                "dim_feedforward": 256,
+                "num_encoder_layers": 6,
+                "num_decoder_layers": 6,
+                "layer_norm_eps": 1e-05,
                 "learning_rate": 0.01,
[…]

### 2022-09-26 ageas/database_setup/binary_class.py

@@ -33,8 +33,8 @@ class Setup:
     def __init__(self,
                  database_path = None,
                  database_type = 'gem_files',
-                 group1_path = 'CT1',
-                 group2_path = 'CT2',
+                 class1_path = 'CT1',
+                 class2_path = 'CT2',
                  specie = 'mouse',
                  interaction_db = 'biogrid',
                  sliding_window_size = None,
@@ -43,13 +43,13 @@ class Setup:
         super(Setup, self).__init__()
         # Auto GEM folder finder
         if database_path is None:
-            assert os.path.exists(group1_path) and os.path.exists(group2_path)
-        elif group1_path is None or group2_path is None:
+            assert os.path.exists(class1_path) and os.path.exists(class2_path)
+        elif class1_path is None or class2_path is None:
             if len(os.listdir(database_path)) != 2:
                 raise DB_Error('Please specify classes for binary clf')
             else:
-                group1_path = os.listdir(database_path)[0]
-                group2_path = os.listdir(database_path)[1]
+                class1_path = os.listdir(database_path)[0]
+                class2_path = os.listdir(database_path)[1]
 
         # Initialization
         self.db_path = database_path
@@ -59,10 +59,10 @@ class Setup:
         self.sliding_window_size = sliding_window_size
         self.sliding_window_stride = sliding_window_stride
         # Get classes'correspond folder paths
-        self.group1_path = self.__cast_path(group1_path)
-        self.group2_path = self.__cast_path(group2_path)
+        self.class1_path = self.__cast_path(class1_path)
+        self.class2_path = self.__cast_path(class2_path)
         # Perform label encoding
-        self.label_transformer = Label_Encode(group1_path, group2_path)
+        self.label_transformer = Label_Encode(class1_path, class2_path)
         self.label1 = self.label_transformer.get_label1()
         self.label2 = self.label_transformer.get_label2()
 
@@ -83,12 +83,12 @@ class Label_Encode:
     Transform labels into ints
     """
 
-    def __init__(self, group1_path, group2_path):
+    def __init__(self, class1_path, class2_path):
         super(Label_Encode, self).__init__()
         # Initialization
-        self.encoder = LabelEncoder().fit([group1_path, group2_path])
+        self.encoder = LabelEncoder().fit([class1_path, class2_path])
         self.transformed_labels = self.encoder.transform(
-            [group1_path, group2_path]
+            [class1_path, class2_path]
         )
 
     # Perform inverse_transform
@@ -118,39 +118,39 @@ class Load_GEM:
 
[…]

### 2022-09-26 ageas/lib/atlas_extractor.py

@@ -19,7 +19,7 @@ GRP_TYPES = ['Standard', 'Outer', 'Bridge', 'Mix']
 
 class Atlas(object):
 	"""
-	Object to extract Atalas of key Regulons from the most important GRPs.
+	Object to extract Atalas of key networks from the most important GRPs.
 	"""
 
 	def __init__(self,
@@ -29,17 +29,17 @@ class Atlas(object):
 				 outlier_grps = dict(),
 				 top_grp_amount = None
 				):
-		self.regulons = list()
+		self.nets = list()
 		self.key_atlas = None
 		self.grps = grp_importances
 		self.outlier_grps = outlier_grps
 		self.correlation_thread = correlation_thread
-		# will be deleted after recorded in self.regulons
+		# will be deleted after recorded in self.nets
 		if grp_importances is not None:
 			self.top_grps=grp_importances.stratify(score_thread, top_grp_amount)
 
 	# as named
-	def build_regulon(self, meta_grn):
+	def build_network(self, meta_grn):
 		# set outlier bonus score to max score of standard GRPs
 		outlier_bonus_score = self.top_grps.iloc[0]['importance']
 		# process standard grps
@@ -50,7 +50,7 @@ class Atlas(object):
 				raise lib.Error('GRP', id, 'not in Meta GRN')
 			grp.type = GRP_TYPES[0]
 			grp.score = self.top_grps.loc[id]['importance']
-			self.update_regulon_with_grp(grp, meta_grn)
+			self.update_net_with_grp(grp, meta_grn)
 		del self.top_grps
 		for id in self.outlier_grps:
 			try:
@@ -59,19 +59,19 @@ class Atlas(object):
 				raise lib.Error('GRP', id, 'not in Meta GRN')
 			grp.type = GRP_TYPES[1]
 			grp.score = self.outlier_grps[id] + outlier_bonus_score
-			self.update_regulon_with_grp(grp, meta_grn)
+			self.update_net_with_grp(grp, meta_grn)
 		self.key_atlas = self.get_key_atlas()
 
 	def find_bridges(self, meta_grn = None):
-		# link regulons if bridge can be build with factors already in regulons
+		# link networks if bridge can be build with factors already in networks
 		i = 0
 		j = 1
 		checked_grps = {}
 		while True:
-			if i == len(self.regulons) or j == len(self.regulons): break
+			if i == len(self.nets) or j == len(self.nets): break
 			combining = False
-			reg1_genes = self.regulons[i].genes.keys()
[…]

### 2022-09-26 ageas/lib/clf_interpreter.py

@@ -134,9 +134,9 @@ class Interpret:
 
     # Update feature importance matrix with newer matrix
     def add(self, df):
-        self.result = self.result.add(
-                                        df, axis = 0, fill_value = 0
-                                     ).sort_values('importance',ascending=False)
+        self.result = self.result.add(df, axis = 0, fill_value = 0).sort_values(
+            'importance', ascending = False
+        )
 
     # divide importance value with stabilizing iteration times
     def divide(self, denominator):

### 2022-09-26 ageas/lib/grp_predictor.py

@@ -21,8 +21,8 @@ class Predict:
     def __init__(self, gem_data, sample_grps = None, thread = None):
         super(Predict, self).__init__()
         assert sample_grps is not None or thread is not None
-        self.group1_gem = gem_data.group1
-        self.group2_gem = gem_data.group2
+        self.class1_gem = gem_data.class1
+        self.class2_gem = gem_data.class2
         # roughly set thread simply with amount of genes in GEMs
         self.thread = 1 / len(gem_data.genes)
 
@@ -38,20 +38,20 @@ class Predict:
     # documented targets
     def expand_meta_grn(self, meta_grn, genes, correlation_thread):
         for gene in genes:
-            group1_targets, group2_targets = self.__predict_key_targets(gene)
+            class1_targets, class2_targets = self.__predict_key_targets(gene)
             self.__update_grps_to_meta_grn(
                 meta_grn,
                 correlation_thread,
                 gene,
-                self.group1_gem.data.index,
-                group1_targets,
+                self.class1_gem.data.index,
+                class1_targets,
             )
             self.__update_grps_to_meta_grn(
                 meta_grn,
                 correlation_thread,
                 gene,
-                self.group2_gem.data.index,
-                group2_targets,
+                self.class2_gem.data.index,
+                class2_targets,
             )
         return meta_grn
 
@@ -71,8 +71,8 @@ class Predict:
                     meta_grn.update_grn(
 						source = gene,
 						target = gene_list[i],
-						gem1 = self.group1_gem,
-						gem2 = self.group2_gem,
+						gem1 = self.class1_gem,
+						gem2 = self.class2_gem,
 						correlation_thread = correlation_thread
 					)
         return
@@ -96,20 +96,20 @@ class Predict:
         # Choose a key presenting in both classes
         grps = None
         for i, src in enumerate(regulatory_sources):
-            if (src in self.group1_gem.data.index and
-                src in self.group2_gem.data.index):
+            if (src in self.class1_gem.data.index and
+                src in self.class2_gem.data.index):
                 grps = regulatory_sources[src]
-                group1_targets, group2_targets = self.__predict_key_targets(
+                class1_targets, class2_targets = self.__predict_key_targets(
                     src, True
                 )
-                assert len(self.group1_gem.data.index) == len(group1_targets)
-                assert len(self.group2_gem.data.index) == len(group2_targets)
+                assert len(self.class1_gem.data.index) == len(class1_targets)
[…]

### 2022-09-26 ageas/lib/meta_grn_caster.py

@@ -48,7 +48,7 @@ class Analysis(object):
         # adding log2FC
         for ele in temp:
             exp = meta_grn.genes[ele[0]].expression_sum
-            ele.append(abs(np.log2(exp['group1']+1) - np.log2(exp['group2']+1)))
+            ele.append(abs(np.log2(exp['class1']+1) - np.log2(exp['class2']+1)))
 
         # changing to dataframe type
         self.result = pd.DataFrame(
@@ -98,17 +98,17 @@ class Cast:
                 std_value_thread,
                 std_ratio_thread):
         # Standard Deviation Filter here
-        group1_genes = tool.STD_Filter(
-            df = gem_data.group1.data,
+        class1_genes = tool.STD_Filter(
+            df = gem_data.class1.data,
             std_value_thread = std_value_thread,
             std_ratio_thread = std_ratio_thread
         )
-        group2_genes = tool.STD_Filter(
-            df = gem_data.group2.data,
+        class2_genes = tool.STD_Filter(
+            df = gem_data.class2.data,
             std_value_thread = std_value_thread,
             std_ratio_thread = std_ratio_thread
         )
-        std_filtered_genes = list(set().union(group1_genes, group2_genes))
+        std_filtered_genes = list(set().union(class1_genes, class2_genes))
 
         # proces guidance casting process based on avaliable information
         if gem_data.interactions is not None:
@@ -232,8 +232,8 @@ class Cast:
                     self.grn.update_grn(
                         source = source,
                         target = target,
-                        gem1 = data.group1,
-                        gem2 = data.group2,
+                        gem1 = data.class1,
+                        gem2 = data.class2,
                         correlation_thread = correlation_thread
                     )
         return
@@ -312,8 +312,8 @@ class Cast:
                     self.grn.update_grn(
                         source = source,
                         target = target,
-                        gem1 = data.group1,
-                        gem2 = data.group2,
+                        gem1 = data.class1,
+                        gem2 = data.class2,
                         correlation_thread = correlation_thread
                     )
         return
@@ -335,8 +335,8 @@ class Cast:
                 self.grn.update_grn(
                     source = source,
                     target = target,
-                    gem1 = data.group1,
-                    gem2 = data.group2,
+                    gem1 = data.class1,
+                    gem2 = data.class2,
                     correlation_thread = correlation_thread
                 )
         return

### 2022-09-26 ageas/test/__init__.py

@@ -7,8 +7,8 @@ author: jy, nkmtmsys
 
 import ageas
 from pkg_resources import resource_filename
-group1_path = resource_filename(__name__, 'ips.csv.gz')
-group2_path = resource_filename(__name__, 'mef.csv.gz')
+class1_path = resource_filename(__name__, 'ips.csv.gz')
+class2_path = resource_filename(__name__, 'mef.csv.gz')
 
 
 
@@ -16,22 +16,22 @@ def Test(**kwargs):
 	"""
 	Function to test whether AGEAS is performing properly or not.
 
-	:param kwargs: All args in ageas.Launch except **group1_path**,
-		**group2_path**, **sliding_window_size**
+	:param kwargs: All args in ageas.Launch except **class1_path**,
+		**class2_path**, **sliding_window_size**
 
 	:return: <ageas._main.Launch object>
 	"""
 	print('Start Test')
 	easy = ageas.Launch(
-		group1_path = group1_path,
-		group2_path = group2_path,
+		class1_path = class1_path,
+		class2_path = class2_path,
 		sliding_window_size = 10,
 		**kwargs
 		# meta_load_path = resource_filename(__name__, 'metaGRN.js'),
 		# psgrn_load_path = resource_filename(__name__, 'psGRNs.js'),
 	)
-	assert 'Nanog' in easy.atlas.regulons[0].genes
-	assert 'Klf4' in easy.atlas.regulons[0].genes
+	assert 'Nanog' in easy.atlas.nets[0].genes
+	assert 'Klf4' in easy.atlas.nets[0].genes
 	print('Finished Test. LGTM')
 	return easy
 

### 2022-09-26 ageas/test/get_gene_symbols.py

@@ -1,0 +1,67 @@
+# import mygene
+# import pandas as pd
+# import ageas.tool.json as json
+#
+#
+# def _update_grn(grn, symbol_dict):
+# 	for id, record in grn['genes'].items():
+# 		symbol = symbol_dict[id]
+# 		if record['symbol'] != symbol and record['symbol'] == id:
+# 			record['symbol'] = symbol
+# 		else:
+# 			print('WTF?')
+#
+# def get_gene_symbols(path):
+# 	# Get Meta GRN, all Gens should be included here
+# 	if path[-1] != '/': path += '/'
+# 	key_atlas = json.decode(path + 'key_atlas.js')
+# 	full_atlas = json.decode(path + 'full_atlas.js')
+# 	psGRNs = json.decode(path + 'pseudo_sample_GRNs.js')
+# 	report = pd.read_csv(path + 'report.csv', header = 0)
+# 	meta_grn = json.decode(path + 'meta_GRN.js')
+# 	meta_report = pd.read_csv(path + 'meta_report.csv', header = 0)
+#
+# 	mygene_query = mygene.MyGeneInfo().querymany(
+# 		meta_grn['genes'].keys(),
+# 		scopes = 'ensembl.gene'
+# 	)
+# 	symbol_dict = dict()
+# 	for ele in mygene_query:
+# 		# only take one gene symbol from mygene
+# 		if ele['query'] not in symbol_dict:
+# 			symbol_dict[ele['query']] = None
+# 		else:
+# 			continue
+# 		# add gene symbol to dict
+# 		try:
+# 			symbol_dict[ele['query']] = ele['symbol']
+# 		except:
+# 			symbol_dict[ele['query']] = None
+# 	del mygene_query
+#
+# 	# Change Gene Symbols for GRNs
+# 	_update_grn(meta_grn, symbol_dict)
+# 	_update_grn(key_atlas, symbol_dict)
+# 	for id, network in full_atlas.items():
+# 		_update_grn(network, symbol_dict)
+# 	for id, grn in psGRNs['class1'].items():
+# 		_update_grn(grn, symbol_dict)
+# 	for id, grn in psGRNs['class2'].items():
+# 		_update_grn(grn, symbol_dict)
+#
+# 	# Change Gene Symbols in Reports
+# 	report['Gene Symbol'] = [symbol_dict[id] for id in report['ID']]
[…]

### 2022-09-26 ageas/tool/__init__.py

@@ -41,7 +41,7 @@ def STD_Filter(df = None, std_value_thread = None, std_ratio_thread = None):
     data = df.transpose()
     sd_list = data[data.columns].std().sort_values(ascending = False)
 
-    # filter by stdev threshod value
+    # filter by stdev threshold value
     if std_value_thread is not None:
         for i in range(len(sd_list)):
             if sd_list[i] < std_value_thread: break

### 2022-09-26 ageas/tool/grn.py

@@ -37,42 +37,42 @@ class GRN(object):
 			return
 
 		# Test out global scale correlation
-		cor_group1 = None
-		cor_group2 = None
+		cor_class1 = None
+		cor_class2 = None
 		passed = False
 
-		# check cor_group1
+		# check cor_class1
 		if source in gem1.data.index and target in gem1.data.index:
-			cor_group1 = tool.Get_Pearson(
+			cor_class1 = tool.Get_Pearson(
 				gem1.data.loc[[source]].values[0],
 				gem1.data.loc[[target]].values[0]
 			)
 
-		# check cor_group2
+		# check cor_class2
 		if source in gem2.data.index and target in gem2.data.index:
-			cor_group2 = tool.Get_Pearson(
+			cor_class2 = tool.Get_Pearson(
 				gem2.data.loc[[source]].values[0],
 				gem2.data.loc[[target]].values[0]
 			)
 
-		# Go through abs(correlation) threshod check
-		if cor_group1 is None and cor_group2 is None:
+		# Go through abs(correlation) threshold check
+		if cor_class1 is None and cor_class2 is None:
 			return
-		if cor_group1 is None and abs(cor_group2) > correlation_thread:
+		if cor_class1 is None and abs(cor_class2) > correlation_thread:
 			passed = True
-			cor_group1 = 0
-		elif cor_group2 is None and abs(cor_group1) > correlation_thread:
+			cor_class1 = 0
+		elif cor_class2 is None and abs(cor_class1) > correlation_thread:
 			passed = True
-			cor_group2 = 0
-		elif cor_group1 is not None and cor_group2 is not None:
-			if abs(cor_group1 - cor_group2) > correlation_thread:
+			cor_class2 = 0
+		elif cor_class1 is not None and cor_class2 is not None:
+			if abs(cor_class1 - cor_class2) > correlation_thread:
 				passed = True
 
 		# update GRN if passed correlation filter
 		if passed:
 			correlations = {
-				'group1':float(cor_group1),
-				'group2':float(cor_group2)
+				'class1':float(cor_class1),
+				'class2':float(cor_class2)
 			}
 			self.add_grp(grp_id, source, target, correlations)
 			if source not in self.genes:
@@ -94,18 +94,18 @@ class GRN(object):
 	def add_gene(self, id, gem1, gem2):
 		assert id not in self.genes
[…]

### 2022-09-26 setup.py

@@ -8,7 +8,7 @@ setuptools.setup(
     version = "v0.0.1-alpha7",
     author = "nkmtmsys and JackSSK",
     author_email = "gyu17@alumni.jh.edu",
-    description = "AutoML-based Genomics fEatrue extrAction System",
+    description = "AutoML-based Genetics fEatrue extrAction System",
     long_description = long_description,
     long_description_content_type = "text/markdown",
     url = "https://github.com/JackSSK/Ageas",

### 2022-10-01 docs/manuscript/main.tex
v0.01a9
Some result part in manuscript

@@
 
-\title{AGEAS: Automated Machine Learning based Genetics Featrue Extraction System}
+\title{AGEAS: Automated Machine Learning based Genetic Featrue Extraction System}
 
@@
 \begin{abstract}
-  Abstract goes here
+  TBD
 \end{abstract}
@@
 \section*{Introduction}
+  \label{introduction}
+  TBD
+  % If analoging regulon with the graph concept in discrete mathematics, one of the most common methods to analyze influence of a vertex, which is equivalent to a gene, is assessing correspond degree of the vertex.
+  % Although the regulatory source and target of GRP can be determined by utilizing interaction database, such as \emph{GTRD}\cite{gkaa1057} which shows regulatory relationship of interactors, numerous computational prediction methods like \emph{GRNBoost2}\cite{grnboost2} and comprehensive interaction database, \emph{BioGRID}\cite{biogrid} for example, could not provide faithful indication on regulatory directions.
+  % Consequently, based on choice of interaction database, the regulon reconstructed with \emph{AGEAS} cannot be guaranteed to be a directed graph but an undirected graph.
+  % Therefore, in this step, \emph{odysseia} primarily extracts genes with high regulatory degrees in the regulon, regardless of they act as source or target in GRPs.
+  % To limit total amount of output key genes, the default setting of \emph{AGEAS} reconstructs regulon for top 100 GRPs, and genes with regulatory degree higher than two in the regulon will be considered influential.
+  % If regulatory directions can be clarifed, the regulatory sources capable of regulating multiple key genes and the regulatory targets influenced by multiple key genes can also be extracted according to GRN reconstruction guidance.
+  %
+  % In the circumstance of finding genes potentially inducing CS conversion, referred as \emph{Mogrify}\cite{mogrify_2016}, both CS deterministic genes and common regulators of these genes shall gain attention.
+  % Herein, \emph{AGEAS} analogized key genes extracted from top GRPs as CS deterministic genes and TFs capable of regulating more than 2 listed key genes as significant common regulator.
+  %
+  % Both non-convergence issue and feature lost issue reflect on one of the key problems for $AutoML$: "No single machine learning method performs best on all datasets".\cite{NIPS2015_11d0e628}
+  % Even though this problem can be solved while viewing $AutoML$ as a $CASH$ problem \cite{thornton2013auto}, such approach may not be directly deployable in our scenario considering comprehensive CS deterministic GFs or GRPs could be hardly labeled out.
+  % Hence, in contrast with directly automating key features finding process, we decide to partially automate CS classification process and export candidate components of joint algorithm to feature importance analysis.
+  % Compared with applying a particular $ML$ model, $CASH$ solving process during automation have higher potential to utilize comprehensive key features instead limited set of them.
+  % Furthermore, due to the network-based essence of \emph{AGEAS}, some CS deterministic features failed to be detected after classification model analysis, if having close regulatory relationships with multiple confirmed GFs, can still be traced down during regulon-based analysis at post stage analysis.
 
@@
   \label{method}
-  The basic principle of \emph{AGEAS} is to find key genetic features regulating phenotype of interest through analyzing how well-performing classification models distinguish gene regulatory networks (GRNs) of sample with the phenotype from GRNs of samples.
-  To reconstruct sufficient GRNs for each class, RNA-seq based expression data is segmented into subsets while each one is analogized as a pseudo-sample having discrete expression data.
+  The basic principle of \emph{AGEAS} is to find key genetic features regulating phenotype of interest through analyzing how well-performing classification models distinguish gene regulatory networks (GRNs) of sample with the phenotype from GRNs of samples without.
+  To reconstruct sufficient GRNs for each class, RNA-Seq based expression data is segmented into subsets while each one is analogized as a pseudo-sample having discrete expression data.
   The pseudo-sample GRNs (psGRNs) are reconstructed accordingly; thus, classification models can be trained, evaluated, and interpreted having gene regulatory pathways (GRPs) as input factors.
-  With heavily weighted GRPs and associated genes repeatedly obtained from interpretations of success sample class predictions, regulons could be formed and inferred as genetic feature complexes playing important role in differentiating the studying sample classes.
+  With heavily weighted GRPs and associated genes repeatedly obtained from interpretations of success sample class predictions, GRNs could be formed and inferred as genetic feature complexes playing important role in differentiating the studying sample classes.
   The overall workflow can be summarized as Figure \ref{workflow}.
+  By default setting, four seperate extractor units in workflow run parallelly after data preprocessing part, and all extracted genetic features are used to form GRNs later combined into one atlas.
   Following sections describe each step of \emph{AGEAS} in more depth.
@@
     \textbf{\emph{(5)}} Repeatedly train classifiers with differnt set of psGRNs as training data to extract GRPs frequently ranked as top important features for decision.
-    \textbf{\emph{(6)}} Reconstruct regulons with extracted GRPs and GRPs excluded as significant outliers.
+    \textbf{\emph{(6)}} Reconstruct GRNs with extracted GRPs and GRPs excluded as significant outliers.
   }
@@
       After differential expression based filters, a standard deviation ($\sigma$) filter is applied to exclude genes either having low expression value or merely affected by dynamic expression status of other genes.
-      By default, the $\sigma$ threshold is set to 1.0 consisting with the lowest expression level in raw gene count matrix gained from RNA-Seq data.
+      By default, the $\sigma$ threshold is set to 1.0, the lowest expression level in raw gene count matrix gained from RNA-Seq data.
       The threshold value should be adjusted corresponding to prior knowledge of input GEMs, for example of what normalization method was applied to the GEMs.
@@
       Utilizing genetic interaction database like \emph{GTRD}\cite{gkaa1057} and \emph{BioGRID}\cite{biogrid}, \emph{AGEAS} checks whether the binding ability of gene pair is confirmed or not.
-      By default, if TF being recorded to have binding site within target gene's promoter range (-1000 to +100) by Chip-Seq dataset retrieved from \emph{GTRD}\cite{gkaa1057}, the potential GRP gene pair will be passed to expression correlation assessment.
+      By default, if TF being recorded to have binding site within target gene's promoter range (-1000 to +100) by Chromatin Immunoprecipitation Sequencing (ChIP-Seq) dataset retrieved from \emph{GTRD}\cite{gkaa1057}, the potential GRP gene pair will be passed to expression correlation assessment.
       For TFs not covered by interaction database, \emph{GRNBoost2}\cite{grnboost2}-like algorithm is initiated to predict potential regulatory target genes.
@@
       Each GRP gene pair in meta-GRN is formed with expression data in pseudo-sample and filtered by same PCC filter in meta-GRN reconstruction process.
-      After all pseudo-samples have been used to reconstruct psGRN, every psGRN will have GRP rearranged by unified order.
+
+      After all pseudo-samples have been used to reconstruct psGRN, every psGRN can be represented as matrix comprising GRPs' PCC values and corresponding genes' expression values.
+      The order of GRPs in each psGRN is also unified through adding GRPs included in other psGRNs with 0.0 PCC value.
 
@@
       \specialrule{.2em}{.1em}{.1em}
-      \multicolumn{5}{|l|}{\emph{Implemented with Pytorch}\cite{NEURIPS2019_9015}} \\
+      \multicolumn{5}{|l|}{\emph{Implemented with Pytorch}\cite{pytorch}} \\
       \hline
@@
     \label{step4}
-    To extract GRPs can effectively define sample class differences, \emph{AGEAS} iteratively initializes classification models with configurations gained from \hyperref[step2]{Step 2}, trains them with varying $\alpha_{max}$ portion of psGRNs scaled after \hyperref[step3]{Step 3}, and interpret every models' correct predictions as mentioned in \hyperref[features_importances]{subsection} above.
+    To extract GRPs can effectively define sample class differences, \emph{AGEAS} iteratively initializes classification models with configurations gained from \hyperref[step2]{Step 2}, trains them with randomly selected $\alpha_{max}$ portion of psGRNs scaled after \hyperref[step3]{Step 3}, and interpret every models' correct predictions as mentioned in \hyperref[features_importances]{subsection} above.
     At each iteration, \emph{AGEAS} receives a z-score scaled feature importance matrix $A$ and add up each GRP's score accordingly from matrix $A'$ kept from previous iteration if there is one.
     Then, top $a$ (default set as 100) ranked GRPs having z-score greater than $0.0$ extracted from $A$ are compared with GRPs extracted from $A'$ by same setting.
-    If less than $d$ (default set as 0.05) portion of GRPs are distinct for GRP sets stratified from $A$ and $A'$, \emph{AGEAS} will consider the GRP extration result from this iteration consists with previous one.
-    Extraction iteration will terminate if either encountering $n$ (default set as 3) continuous consisting result or running out of preset iteration number (default set as 10).
+    If less than $d$ (default set as 0.05) portion of GRPs are distinct for GRP sets stratified from $A$ and $A'$, \emph{AGEAS} will consider the GRP extration result from this iteration being consistent with previous one.
+    Extraction iteration will terminate if either encountering $n$ (default set as 3) continuous consistent result or running out of preset iteration number (default set as 10).
     All feature importance scores in matrix $A$ from last iteration are divided by total extraction iteration number processed, and top $a$ ranked GRPs are considered as key GRPs for sample class differentiation and passed to next step.
@@
 
-  % With feature list ranked according to importance values, \emph{AGEAS} reconstructs regulon for top-ranked GRPs and extracts influential genes among the regulon.
-  % If analoging regulon with the graph concept in discrete mathematics, one of the most common methods to analyze influence of a vertex, which is equivalent to a gene, is assessing correspond degree of the vertex.
-  % Although the regulatory source and target of GRP can be determined by utilizing interaction database, such as \emph{GTRD}\cite{gkaa1057} which shows regulatory relationship of interactors, numerous computational prediction methods like \emph{GRNBoost2}\cite{grnboost2} and comprehensive interaction database, \emph{BioGRID}\cite{biogrid} for example, could not provide faithful indication on regulatory directions.
-  % Consequently, based on choice of interaction database, the regulon reconstructed with \emph{AGEAS} cannot be guaranteed to be a directed graph but an undirected graph.
-  % Therefore, in this step, \emph{odysseia} primarily extracts genes with high regulatory degrees in the regulon, regardless of they act as source or target in GRPs.
-  % To limit total amount of output key genes, the default setting of \emph{AGEAS} reconstructs regulon for top 100 GRPs, and genes with regulatory degree higher than two in the regulon will be considered influential.
-  % If regulatory directions can be clarifed, the regulatory sources capable of regulating multiple key genes and the regulatory targets influenced by multiple key genes can also be extracted according to GRN reconstruction guidance.
-  %
-  % In the circumstance of finding genes potentially inducing CS conversion, referred as \emph{Mogrify}\cite{mogrify_2016}, both CS deterministic genes and common regulators of these genes shall gain attention.
-  % Herein, \emph{AGEAS} analogized key genes extracted from top GRPs as CS deterministic genes and TFs capable of regulating more than 2 listed key genes as significant common regulator.
-  %
-  % Both non-convergence issue and feature lost issue reflect on one of the key problems for $AutoML$: "No single machine learning method performs best on all datasets".\cite{NIPS2015_11d0e628}
-  % Even though this problem can be solved while viewing $AutoML$ as a $CASH$ problem \cite{thornton2013auto}, such approach may not be directly deployable in our scenario considering comprehensive CS deterministic GFs or GRPs could be hardly labeled out.
-  % Hence, in contrast with directly automating key features finding process, we decide to partially automate CS classification process and export candidate components of joint algorithm to feature importance analysis.
-  % Compared with applying a particular $ML$ model, $CASH$ solving process during automation have higher potential to utilize comprehensive key features instead limited set of them.
-  % Furthermore, due to the network-based essence of \emph{AGEAS}, some CS deterministic features failed to be detected after classification model analysis, if having close regulatory relationships with multiple confirmed GFs, can still be traced down during regulon-based analysis at post stage analysis.
-
 \section*{Results}
   \label{res}
+  To assess \emph{AGEAS}'s predictive power, we first applied \emph{AGEAS} to study somatic reprogramming to induced pluripotent stem cells (iPSC) achieved in mice by
+  the year 2006 \cite{yamanaka_2006}, milestone discovery of cell plasticity \cite{cell_repro_review}.
+  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, single-cell RNA sequencing (scRNA-Seq) based gene expression matrices (GEMs) of embryonic stem cell (ESC) and mouse embryonic fibroblast (MEF) were used as input.
+  The extraction result is summarized as TF regulons, collections of a TF and corresponding direct regulatory targets, in ... % fig ../images/mef_esc.png
+  Since Pou5f1 (Oct4), Nanog, and Sox2 not only are forming sizeable regulons with extracted GRPs but also have most significant expression changes between MEF and ESC, we can infer them as important factors closely related with cell type differences.
+  Multiple previous studies have confirmed that all of Oct4, Nanog, and Sox2 are playing important role in maintaing pluripotency \cite{niwa_2007} and inducing cell conversion \cite{yamanaka_2006, ips7f, ipsOK, oct4_nanog_sox2_lin28, oct4_nanog_sox2}.
+
+  To further address \emph{AGEAS}'s applicability and limitation,
+
+  radial glial coculture to dopaminergic neurons...
+
+  Postnatal p7-p28 cardiomyocyte mature
+
+  HSC activation in CCl4 injury model
+
+  To demonstrate empirically the predictive capabilities...
+
+  % \begin{table}[ht]
+  %     \centering
+  %     \begin{tabular}{|l|l|l|l|}
+  %       \hline
+  %       \textbf{Gene} & \textbf{Main Exp Class} & \textbf{$|log2FC|$} & \textbf{Description}  \\
+  %       \hline
+  %
+  %       Pou5f1 (Oct4) & ESC & 13.36 & The Yamanaka factor\cite{yamanaka_2006} \\
+  %       \hline
+  %       Cebpb & MEF & 2.24 & part of the AP-1 complex network \\
+  %       \hline
+  %       Nanog & ESC & 10.46 & Can reprogram MEF into iPSC with other GFs\cite{ips7f, oct4_nanog_sox2_lin28, oct4_nanog_sox2} \\
+  %       \hline
+  %       Sox2 & ESC & 9.64 & The Yamanaka factor\cite{yamanaka_2006} \\
+  %       \hline
+  %       Junb & MEF & 0.17 & Subunit of AP-1 which can prohibit iPSC reprogramming\cite{ips7f, ipsAP1} \\
+  %       \hline
+  %       Jun & MEF & 0.45 & Subunit of AP-1 which can prohibit iPSC reprogramming\cite{ips7f, ipsAP1} \\
+  %       \hline
+  %       Jund & ESC & 1.38 & Subunit of AP-1 which can prohibit iPSC reprogramming\cite{ips7f, ipsAP1} \\
+  %       \hline
+  %       Hdca2 & ESC & 1.01 & Knockdown of Hdac2 improves OSKM-mediated iPS cell generation \\
+  %       \hline
+  %       Twist2 & MEF & 3.64 & fibroblastic master gene\\
+  %       \hline
+  %       Fos & MEF & 0.58 & Subunit of AP-1 which can prohibit iPSC reprogramming\cite{ips7f, ipsAP1} \\
+  %       \hline
+  %       Klf4+39 & ESC & 2.71 & The Yamanaka factor\cite{yamanaka_2006} \\
+  %
+  %       \hline
+  %     \end{tabular}
+  %     \caption{
+  %       \label{mef_esc_result}
+  %       In total of 47 Genes
+  %     }
+  % \end{table}
+  %
+  % \begin{table}[ht]
+  %     \centering
+  %     \begin{tabular}{|l|l|l|l|}
+  %       \hline
+  %       \textbf{Gene} & \textbf{Main Exp Class} & \textbf{$|log2FC|$} & \textbf{Description}  \\
+  %       \hline
+  %
+  %       EBF1 & 1 & 2.91 & sth \\
+  %       \hline
+  %       PBX3 & 2 & 3.02 & sss \\
+  %       \hline
+  %       NR3C1 & 3 & 0.40 & sss \\
+  %       \hline
+  %       SOX2 & 4 & 2.94 & sss \\
+  %       \hline
+  %       ELF3 & 5 & 5.91 & sss \\
+  %       \hline
+  %       ISL1 & 6 & 9.13 & sss \\
+  %       \hline
+  %       CEBPD & 7 & 3.20 & sss \\
+  %       \hline
+  %       MAZ & 8 & 1.00 & sss \\
+  %       \hline
+  %       PHOX2B & 9 & 7.38 & sss\\
+  %       \hline
+  %       FOXP1 & 10 & 0.12 & sss \\
+  %       \hline
+  %       ASCL1 & 12 & 0.30 & sss \\
+  %       \hline
+  %       NEUROD1 & 59 & 1.26 & sss \\
+  %
+  %       \hline
+  %     \end{tabular}
+  %     \caption{
+  %       \label{neuron_result}
+  %       In total of 68 Genes
+  %     }
+  % \end{table}
+  %
+  % \begin{table}[ht]
+  %     \centering
+  %     \begin{tabular}{|l|l|l|l|}
+  %       \hline
+  %       \textbf{Gene} & \textbf{Main Exp Class} & \textbf{$|log2FC|$} & \textbf{Description}  \\
+  %       \hline
+  %
+  %       Sp1 & 1 & 4.68 & sth \\
+  %       \hline
+  %       Esr1 & 2 & 4.63 & sss \\
+  %       \hline
+  %       Srf & 3 & 0.02 & sss \\
+  %       \hline
+  %       Cebpb & 4 & 2.53 & sss \\
+  %       \hline
+  %       Nfe2l2 & 5 & 0.38 & sss \\
+  %       \hline
+  %       Nfib & 6 & 1.87 & sss \\
+  %       \hline
+  %       Cbfb & 7 & 0.16 & sss \\
+  %       \hline
+  %       Fosl2 & 8 & 0.64 & sss \\
+  %       \hline
+  %       Nkx2-5 & 9 & 0.06 & cardiac-specific structural genes\\
+  %       \hline
+  %       Rest & 10 & 1.67 & sss \\
+  %
+  %
+  %       \hline
+  %     \end{tabular}
+  %     \caption{
+  %       \label{CMp7p28_result}
+  %       In total of 119 Genes
+  %     }
+  % \end{table}
+  %
+  %
+  % \begin{table}[ht]
+  %     \centering
+  %     \begin{tabular}{|l|l|l|l|}
+  %       \hline
+  %       \textbf{Gene} & \textbf{Main Exp Class} & \textbf{$|log2FC|$} & \textbf{Description}  \\
+  %       \hline
+  %
+  %       Mef2c & 1 & 1.82 & sth \\
+  %       \hline
+  %       Jun & 2 & 0.55 & sss \\
+  %       \hline
+  %       Jund & 3 & 0.37 & sss \\
+  %       \hline
+  %       Klf4 & 4 & 0.23 & sss \\
+  %       \hline
+  %       Ebf1 & 5 & 6.33 & sss \\
+  %       \hline
+  %       Fos & 6 & 0.32 & sss \\
+  %       \hline
+  %       Hand2 & 7 & 2.59 & sss \\
+  %       \hline
+  %       Lhx2 & 8 & 7.02 & sss \\
+  %       \hline
+  %       Nfib & 9 & 0.65 & sss\\
+  %       \hline
+  %       Nr4a1 & 10 & 0.07 & sss \\
+  %
+  %
+  %       \hline
+  %     \end{tabular}
+  %     \caption{
+  %       \label{ccl4liver_result}
+  %       In total of 35 Genes
+  %     }
+  % \end{table}
 
@@
 \section*{Additional information}
-All scRNA-seq datasets are retrieved from Gene Expression Omnibus(GEO) as described in the Table below.
+All scRNA-Seq datasets are retrieved from Gene Expression Omnibus(GEO) as described in the Table below.
 

### 2022-10-01 ageas/__init__.py

@@ -25,8 +25,8 @@ AGEAS
 ========
 Summary
 -------
-AGEAS (AutoML-based Genetics fEatrue extrAction System)
-is to find key genetics factors, including genes and regulatory pathways,
+AGEAS (AutoML-based Genetic fEatrue extrAction System)
+is to find key genetic factors, including genes and regulatory pathways,
 in determining cellular phenotype.
 
 For more information, please visit our GitHub repo:

### 2022-10-01 setup.py

@@ -8,7 +8,7 @@ setuptools.setup(
     version = "v0.0.1-alpha7",
     author = "nkmtmsys and JackSSK",
     author_email = "gyu17@alumni.jh.edu",
-    description = "AutoML-based Genetics fEatrue extrAction System",
+    description = "AutoML-based Genetic fEatrue extrAction System",
     long_description = long_description,
     long_description_content_type = "text/markdown",
     url = "https://github.com/JackSSK/Ageas",

### 2022-10-02 docs/manuscript/main.tex
v0.0.1a9
Get Result done tmr!

@@
 \usepackage{algorithm2e}
+\usepackage{subcaption}
+\usepackage[labelformat=parens,labelsep=quad,skip=3pt]{caption}
+\usepackage{graphicx}
 
@@
   With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, single-cell RNA sequencing (scRNA-Seq) based gene expression matrices (GEMs) of embryonic stem cell (ESC) and mouse embryonic fibroblast (MEF) were used as input.
-  The extraction result is summarized as TF regulons, collections of a TF and corresponding direct regulatory targets, in ... % fig ../images/mef_esc.png
-  Since Pou5f1 (Oct4), Nanog, and Sox2 not only are forming sizeable regulons with extracted GRPs but also have most significant expression changes between MEF and ESC, we can infer them as important factors closely related with cell type differences.
-  Multiple previous studies have confirmed that all of Oct4, Nanog, and Sox2 are playing important role in maintaing pluripotency \cite{niwa_2007} and inducing cell conversion \cite{yamanaka_2006, ips7f, ipsOK, oct4_nanog_sox2_lin28, oct4_nanog_sox2}.
+  The extraction result can be summarized as TF regulons, collections of a TF and corresponding direct regulatory targets, and TFs forming largest regulons with extracted GRPs are shown in Figure \ref{result_figs}(a).
+  Among TFs with sizeable regulons, Pou5f1 (Oct4), Nanog, and Sox2 also have most significant expression changes between MEF and ESC.
+  Thus, we can infer these TFs as import factors closely related with cell type differences.
+  Multiple previous studies have confirmed that all of Oct4, Nanog, and Sox2 are playing important role in maintaing pluripotency \cite{niwa_2007} and inducing conversion from somatic cell to iPSC \cite{yamanaka_2006, ips7f, ipsOK, oct4_nanog_sox2_lin28, oct4_nanog_sox2}.
 
-  To further address \emph{AGEAS}'s applicability and limitation,
+  To further address \emph{AGEAS}'s applicability and limitation, we applied \emph{AGEAS} to three other scRNA-Seq based studies in distinct research areas.
+  With all default settings and analytical procedure applied above, we can assess \emph{AGEAS}'s performance in following scenarios:
 
-  radial glial coculture to dopaminergic neurons...
+  \subsection*{Dopaminergic neuron generation}
+  (Cell subtype differentiation)
+  iPSC-derived radial glial/neuronal co-culture to dopaminergic (DA) neurons...
+  ISL1: essential functions of Isl1 in prethalamic dopaminergic neuron development
+  % doi:10.1016/j.ydbio.2012.06.010
+  PHOX2B: Phox2b Influences Dopaminergic Development
+  % https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3522650/pdf/pone.0052118.pdf
+  ELF3: ELF3 was found to be associated with mouse neural stem cell development
+  % (Tang, Y.; Katuri, V.; Iqbal, S.; Narayan, T.; Wang, Z.; Lu, R.S.; Mishra, L.; Mishra, B.
+ELF a β-spectrin is a neuronal precursor cell marker in developing mammalian brain; structure and organization of the elf/β-G spectrin gene.
+Oncogene 2002, 21, 5255–5267.)
+  (ASCL1 also extracted as 12th but not having significant exp change -> how to better analysis result)
 
-  Postnatal p7-p28 cardiomyocyte mature
+  \subsection*{Postnatal cardiomyocyte maturation}
+  (Physiological development)
+  Postnatal CM p7 to p28
+  Esr1: estrogenic regulation for normal myocardial development was primarily via ER-alpha(Esr1)
+  % (10.1016/j.mce.2013.11.011)
+  % (http://dx.doi.org/10.1016/j.mce.2013.11.011)
+  Cebpb: The Transcription Factor CEBP-beta Serves as a Master Regulator of physiologic Cardiac Hypertrophy
+  % (Cell. 2010;143:1072–1083)
+  % (Originally published4 Feb 2011https://doi.org/10.1161/RES.0b013e31820ff484Circulation Research. 2011;108:277–278)
+  Sp1:
 
-  HSC activation in CCl4 injury model
+  \subsection*{Hepatic stellate cell activation in $CCl_4$ acute liver model}
+  (Pathological development)
+  HSCs p6w vs PFs p6w analoging activated HSCs
+  Lhx2
+  Osr1
+  Ebf1
 
-  To demonstrate empirically the predictive capabilities...
+  \begin{figure}
+    \begin{subfigure}{0.49\linewidth}
+      \centering
+      \includegraphics[width=\linewidth, keepaspectratio,]{../images/MEF_ESC_top.png}
+      \caption{}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \centering
+      \includegraphics[width=\linewidth, keepaspectratio,]{../images/N_cocul_top.png}
+      \caption{}
+    \end{subfigure}
 
-  % \begin{table}[ht]
-  %     \centering
-  %     \begin{tabular}{|l|l|l|l|}
-  %       \hline
-  %       \textbf{Gene} & \textbf{Main Exp Class} & \textbf{$|log2FC|$} & \textbf{Description}  \\
-  %       \hline
-  %
-  %       Pou5f1 (Oct4) & ESC & 13.36 & The Yamanaka factor\cite{yamanaka_2006} \\
-  %       \hline
-  %       Cebpb & MEF & 2.24 & part of the AP-1 complex network \\
-  %       \hline
-  %       Nanog & ESC & 10.46 & Can reprogram MEF into iPSC with other GFs\cite{ips7f, oct4_nanog_sox2_lin28, oct4_nanog_sox2} \\
-  %       \hline
-  %       Sox2 & ESC & 9.64 & The Yamanaka factor\cite{yamanaka_2006} \\
-  %       \hline
-  %       Junb & MEF & 0.17 & Subunit of AP-1 which can prohibit iPSC reprogramming\cite{ips7f, ipsAP1} \\
-  %       \hline
-  %       Jun & MEF & 0.45 & Subunit of AP-1 which can prohibit iPSC reprogramming\cite{ips7f, ipsAP1} \\
-  %       \hline
-  %       Jund & ESC & 1.38 & Subunit of AP-1 which can prohibit iPSC reprogramming\cite{ips7f, ipsAP1} \\
-  %       \hline
-  %       Hdca2 & ESC & 1.01 & Knockdown of Hdac2 improves OSKM-mediated iPS cell generation \\
-  %       \hline
-  %       Twist2 & MEF & 3.64 & fibroblastic master gene\\
-  %       \hline
-  %       Fos & MEF & 0.58 & Subunit of AP-1 which can prohibit iPSC reprogramming\cite{ips7f, ipsAP1} \\
-  %       \hline
-  %       Klf4+39 & ESC & 2.71 & The Yamanaka factor\cite{yamanaka_2006} \\
-  %
-  %       \hline
-  %     \end{tabular}
-  %     \caption{
-  %       \label{mef_esc_result}
-  %       In total of 47 Genes
-  %     }
-  % \end{table}
+    \begin{subfigure}{0.49\linewidth}
+      \centering
+      \includegraphics[width=\linewidth, keepaspectratio,]{../images/CMp7d_CMp28d_top.png}
+      \caption{}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+      \centering
+      \includegraphics[width=\linewidth, keepaspectratio,]{../images/HSCp6w_PFp6w_top.png}
+      \caption{}
+    \end{subfigure}
+
+    \caption{
+      TFs forming largest regulons with GRPs extracted by \emph{AGEAS}.
+      Each TF has regulon size indicating amount of direct regulatory genes and $log_2$ gene expression levels in binary sample classes.
+      \textbf{\emph{(a)}} Mouse embryonic fibroblast vs. Embryonic stem cell
+      \textbf{\emph{(b)}} Purified dopaminergic neuron vs. Radial glial/neuronal co-culture
+      \textbf{\emph{(c)}} 7 days postnatal cardiomyocyte vs. 28 days postnatal cardiomyocyte
+      \textbf{\emph{(d)}} Hepatic stellate cell vs. Portal fibroblast (both after 6 weeks of CCl4 administration)
+    }
+    \label{result_figs}
+  \end{figure}
+
+  \vspace{\baselineskip}
+  \noindent To demonstrate empirically the predictive capabilities...
+
   %
@@
   \label{disc}
+  TBD
 

### 2022-10-03 docs/manuscript/main.tex
v0.0.1a9
Result part almost done

@@
   the year 2006 \cite{yamanaka_2006}, milestone discovery of cell plasticity \cite{cell_repro_review}.
-  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, single-cell RNA sequencing (scRNA-Seq) based gene expression matrices (GEMs) of embryonic stem cell (ESC) and mouse embryonic fibroblast (MEF) were used as input.
+  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, single-cell RNA sequencing (scRNA-Seq) based gene expression matrices (GEMs) of embryonic stem cells (ESCs) and mouse embryonic fibroblasts (MEFs) were used as input.
   The extraction result can be summarized as TF regulons, collections of a TF and corresponding direct regulatory targets, and TFs forming largest regulons with extracted GRPs are shown in Figure \ref{result_figs}(a).
-  Among TFs with sizeable regulons, Pou5f1 (Oct4), Nanog, and Sox2 also have most significant expression changes between MEF and ESC.
+  Among TFs with sizeable regulons, Pou5f1 (Oct4), Nanog, and Sox2 also have most significant expression difference between MEF and ESC samples.
   Thus, we can infer these TFs as import factors closely related with cell type differences.
@@
   \subsection*{Dopaminergic neuron generation}
-  (Cell subtype differentiation)
-  iPSC-derived radial glial/neuronal co-culture to dopaminergic (DA) neurons...
-  ISL1: essential functions of Isl1 in prethalamic dopaminergic neuron development
-  % doi:10.1016/j.ydbio.2012.06.010
-  PHOX2B: Phox2b Influences Dopaminergic Development
-  % https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3522650/pdf/pone.0052118.pdf
-  ELF3: ELF3 was found to be associated with mouse neural stem cell development
-  % (Tang, Y.; Katuri, V.; Iqbal, S.; Narayan, T.; Wang, Z.; Lu, R.S.; Mishra, L.; Mishra, B.
-ELF a β-spectrin is a neuronal precursor cell marker in developing mammalian brain; structure and organization of the elf/β-G spectrin gene.
-Oncogene 2002, 21, 5255–5267.)
-  (ASCL1 also extracted as 12th but not having significant exp change -> how to better analysis result)
+  Analyzing difference between human iPSC-derived radial glial / neuronal co-culture, as neural progenitors\cite{ASCL1_dopaminergic_neuron_2021}, and tyrosine hydroxylase (TH) expressing purified dopaminergic (DA) neurons, we address the applicability of \emph{AGEAS} on cell subtype differentiation problems.
+
+  From extracted TFs shown in Figure \ref{result_figs}(a), we hypothesize ISL1, PHOX2B, and ELF3 are regulating essential functions differentiating DA neurons from neural progenitors.
+  Both ISL1 and PHOX2B were found related with DA phenotype in previous studies:
+  ISL1 is essential for differentiation of prethalamic DA neurons\cite{isl1_da},
+  and PHOX2B is connected with TH expression influencing DA neuron development and improving DA activity \cite{phox2_caudal_da, phox2_rat_da}
+  Moreover, ELF3 was found to be neuronal precursor cell marker associated with neural stem cell development \cite{ELF3_precursor_marker}, consistent with it's high expression level in neuronal co-culture class.
+
+  ASCL1, found as necessary factor regulating DA neurotransmitter selection by original research where we retrieved scRNA-Seq data\cite{ASCL1_dopaminergic_neuron_2021}, is also forming substantial regulon with extracted GRPs.
 
   \subsection*{Postnatal cardiomyocyte maturation}
-  (Physiological development)
-  Postnatal CM p7 to p28
+  To address the performance of \emph{AGEAS} while analyzing cell physiological development, scRNA-Seq data of cardiomyocytes (CMs) in postnatal day 7 mice (P7) and day 28 mice (P28) are used as input for extracting key genetic features in postnatal cardiomyocyte maturation.
+
   Esr1: estrogenic regulation for normal myocardial development was primarily via ER-alpha(Esr1)
@@
   % (Originally published4 Feb 2011https://doi.org/10.1161/RES.0b013e31820ff484Circulation Research. 2011;108:277–278)
-  Sp1:
+  % https://doi.org/10.1016/j.mce.2014.03.007
+  Sp1: upregulates the expression of GATA4 and atrial natriuretic peptide (ANP) in cardiomyoblast cells promote hypertrophy
+  % https://doi.org/10.1142/S0192415X18500532 (2018).
+  % Sp1 and Sp3 transcription factors are required for trans-activation of the human SERCA2 promoter in cardiomyocytes: Electrophysiology and Ca2+ handling
+  % https://doi.org/10.1016/S0008-6363(03)00529-7, 10.1161/CIRCRESAHA.119.315862
 
-  \subsection*{Hepatic stellate cell activation in $CCl_4$ acute liver model}
-  (Pathological development)
-  HSCs p6w vs PFs p6w analoging activated HSCs
+  \subsection*{Hepatic stellate cell activation in $CCl_4$ induced liver fibrosis}
+  Here we address \emph{AGEAS}'s applicability on cell pathological development studies through analyzing hepatic stellate cells (HSCs) in mice liver administrated with chronic carbon tetrachloride ($CCl_4$) for 6 weeks and according portal fibroblasts (PF) simulating activated HSCs.
+
   Lhx2
@@
   \vspace{\baselineskip}
-  \noindent To demonstrate empirically the predictive capabilities...
+  \noindent To demonstrate empirically the predictive capabilities... in vitro experiment Lhx2 repressing HSC activation...
 
-  %
   % \begin{table}[ht]
@@
   %       \hline
-  %
-  %       EBF1 & 1 & 2.91 & sth \\
-  %       \hline
-  %       PBX3 & 2 & 3.02 & sss \\
-  %       \hline
-  %       NR3C1 & 3 & 0.40 & sss \\
-  %       \hline
-  %       SOX2 & 4 & 2.94 & sss \\
-  %       \hline
-  %       ELF3 & 5 & 5.91 & sss \\
-  %       \hline
-  %       ISL1 & 6 & 9.13 & sss \\
-  %       \hline
-  %       CEBPD & 7 & 3.20 & sss \\
-  %       \hline
-  %       MAZ & 8 & 1.00 & sss \\
-  %       \hline
-  %       PHOX2B & 9 & 7.38 & sss\\
-  %       \hline
-  %       FOXP1 & 10 & 0.12 & sss \\
-  %       \hline
-  %       ASCL1 & 12 & 0.30 & sss \\
-  %       \hline
-  %       NEUROD1 & 59 & 1.26 & sss \\
-  %
-  %       \hline
-  %     \end{tabular}
-  %     \caption{
-  %       \label{neuron_result}
-  %       In total of 68 Genes
-  %     }
-  % \end{table}
-  %
-  % \begin{table}[ht]
-  %     \centering
-  %     \begin{tabular}{|l|l|l|l|}
-  %       \hline
-  %       \textbf{Gene} & \textbf{Main Exp Class} & \textbf{$|log2FC|$} & \textbf{Description}  \\
-  %       \hline
-  %
-  %       Sp1 & 1 & 4.68 & sth \\
-  %       \hline
-  %       Esr1 & 2 & 4.63 & sss \\
-  %       \hline
-  %       Srf & 3 & 0.02 & sss \\
-  %       \hline
-  %       Cebpb & 4 & 2.53 & sss \\
-  %       \hline
-  %       Nfe2l2 & 5 & 0.38 & sss \\
-  %       \hline
-  %       Nfib & 6 & 1.87 & sss \\
-  %       \hline
-  %       Cbfb & 7 & 0.16 & sss \\
-  %       \hline
-  %       Fosl2 & 8 & 0.64 & sss \\
-  %       \hline
-  %       Nkx2-5 & 9 & 0.06 & cardiac-specific structural genes\\
-  %       \hline
-  %       Rest & 10 & 1.67 & sss \\
-  %
-  %
-  %       \hline
-  %     \end{tabular}
-  %     \caption{
-  %       \label{CMp7p28_result}
-  %       In total of 119 Genes
-  %     }
-  % \end{table}
-  %
-  %
-  % \begin{table}[ht]
-  %     \centering
-  %     \begin{tabular}{|l|l|l|l|}
-  %       \hline
-  %       \textbf{Gene} & \textbf{Main Exp Class} & \textbf{$|log2FC|$} & \textbf{Description}  \\
-  %       \hline
-  %
   %       Mef2c & 1 & 1.82 & sth \\
-  %       \hline
-  %       Jun & 2 & 0.55 & sss \\
-  %       \hline
-  %       Jund & 3 & 0.37 & sss \\
-  %       \hline
-  %       Klf4 & 4 & 0.23 & sss \\
-  %       \hline
-  %       Ebf1 & 5 & 6.33 & sss \\
-  %       \hline
-  %       Fos & 6 & 0.32 & sss \\
-  %       \hline
-  %       Hand2 & 7 & 2.59 & sss \\
-  %       \hline
-  %       Lhx2 & 8 & 7.02 & sss \\
-  %       \hline
-  %       Nfib & 9 & 0.65 & sss\\
-  %       \hline
-  %       Nr4a1 & 10 & 0.07 & sss \\
-  %
-  %
   %       \hline

### 2022-10-03 docs/manuscript/main.tex
v0.0.1a9
guess I should leave liver fibrosis stuffs to pro

@@
 
-      After all pseudo-samples have been used to reconstruct psGRN, every psGRN can be represented as matrix comprising GRPs' PCC values and corresponding genes' expression values.
+      After all pseudo-samples have been used to reconstruct psGRN, every psGRN can be represented as matrix comprising GRPs' PCC values.
       The order of GRPs in each psGRN is also unified through adding GRPs included in other psGRNs with 0.0 PCC value.
@@
 
-  From extracted TFs shown in Figure \ref{result_figs}(a), we hypothesize ISL1, PHOX2B, and ELF3 are regulating essential functions differentiating DA neurons from neural progenitors.
+  From extracted TFs shown in Figure \ref{result_figs}(b), we hypothesize ISL1, PHOX2B, and ELF3, referring to their correspond regulon sizes and expression changes, are regulating essential functions differentiating DA neurons from neural progenitors.
   Both ISL1 and PHOX2B were found related with DA phenotype in previous studies:
@@
 
-  ASCL1, found as necessary factor regulating DA neurotransmitter selection by original research where we retrieved scRNA-Seq data\cite{ASCL1_dopaminergic_neuron_2021}, is also forming substantial regulon with extracted GRPs.
+  EBF1, which forms the largest regulon with extracted GRPs, was determined as key neuronal differentiation regulator in the ventral telencephalon, nature source of neuronal and glial cells \cite{ebf1_striatum, ebf1_cell_diff}.
+  Furthermore, EBF1 plays important role in mesodiencephalic DA neuron migration. \cite{ebf1_migration}
+  ASCL1, found as necessary factor regulating DA neurotransmitter selection by original research where we retrieved scRNA-Seq data\cite{ASCL1_dopaminergic_neuron_2021}, is also forming substantial regulon.
+  % SOX2 and NR3C1 also have reports in neuronal differentiation...
 
@@
 
-  Esr1: estrogenic regulation for normal myocardial development was primarily via ER-alpha(Esr1)
-  % (10.1016/j.mce.2013.11.011)
-  % (http://dx.doi.org/10.1016/j.mce.2013.11.011)
-  Cebpb: The Transcription Factor CEBP-beta Serves as a Master Regulator of physiologic Cardiac Hypertrophy
-  % (Cell. 2010;143:1072–1083)
-  % (Originally published4 Feb 2011https://doi.org/10.1161/RES.0b013e31820ff484Circulation Research. 2011;108:277–278)
-  % https://doi.org/10.1016/j.mce.2014.03.007
-  Sp1: upregulates the expression of GATA4 and atrial natriuretic peptide (ANP) in cardiomyoblast cells promote hypertrophy
-  % https://doi.org/10.1142/S0192415X18500532 (2018).
-  % Sp1 and Sp3 transcription factors are required for trans-activation of the human SERCA2 promoter in cardiomyocytes: Electrophysiology and Ca2+ handling
-  % https://doi.org/10.1016/S0008-6363(03)00529-7, 10.1161/CIRCRESAHA.119.315862
+  Following same regulon size and expression change based analytical procedure, we primarily investigated three TFs shown in Figure \ref{result_figs}(c): Sp1, Esr1 ($ER\alpha$), and Cebpb.
+  Previous studies demonstrated that Sp1 promotes CM hypertrophy \cite{sp1_hypertrophy} and maturation of electrophysiology and $Ca^{2+}$ handling \cite{Sp1_electrophysiologt, CM_mature}.
+  % trans-activation of the SERCA2 promoter
+  Esr1 was found modulating myocardial development for postnatal cardiac growth\cite{esr1_cm, esr1_cm_growth}, and Cebpb's role as repressor of CM growth and proliferation while preventing pathological CM hypertrophy also demonstrated by several studeis\cite{cebpb_1, cebpb_2}.
+
+  Other TFs known playing important roles in CM maturation, such as Srf\cite{CM_mature, cebpb_1}, Nkx2-5\cite{cebpb_1, nkx25}, and Yap1\cite{CM_mature, yap1}, are also forming sizeable regulons in GRN atlas returned by \emph{AGEAS} .
 
@@
 
-  Lhx2
-  Osr1
-  Ebf1
+  Within TFs shown in Figure \ref{result_figs}(d), we suppose Lhx2, Osr1, and Ebf1 are regulating phenotypes clearly differentiating HSCs from PFs considering their correspond TF regulon sizes and expression changes.
+
+  Osr1 fibrogenic regulation
+
+  Ebf1 ...
+
+  Lhx2 halt quiescent HSCs
+
+  Furthermore, Mef2c forming top TF regulon is main regulator of collagen expression...
 
@@
   \vspace{\baselineskip}
-  \noindent To demonstrate empirically the predictive capabilities... in vitro experiment Lhx2 repressing HSC activation...
+  \noindent To demonstrate empirically the predictive capabilities...
+  Since Lhx2 has largest expression change while favoring in HSCs...
+  but not directly regulating fibrogenic genes as Mef2c does...
+  in vitro experiment overexpression of Lhx2 repressing HSC activation...
 

### 2022-10-05 docs/manuscript/main.tex
v0.0.1a9
Introduction, discussion to go!

--- 2022-10-02 docs/manuscript/main.tex
@@
 
-\title{AGEAS: Automated Machine Learning based Genetic Featrue Extraction System}
+\title{AGEAS: Automated Machine Learning based Genetic Regulatory Element Extraction System}
 
@@
 \begin{abstract}
-  TBD
+  As rapid progress in sequencing technology since last decade, numerous mechanisms underlying cell functions and developmental processes have been revealed as complex regulations of gene expressions.
+  While single-cell RNA sequencing (scRNA-Seq) made high-resolution transcriptomic view increasingly accessible, precise identification of gene regulatory network (GRN) describing cell states became achievable.
+  However, extracting key regulatory elements, including gene regulatory pathways (GRPs), transcription factors (TFs), and downstream genes, accurately reflecting main functionality changes remain challenging.
+  Herein, we describe AGEAS, an automated machine learning (AutoML) based genetic regulatory element extraction system that assesses importances of GRPs in differentiating sample classes, such as cell types and developmental stages.
+  With several case studies in divergent research areas, we show that AGEAS can indeed extract informative regulatory elements and reconstruct networks referring phenotype or biological process of interest.
+  Furthermore, wet lab experiment validations...
+  Overall, AGEAS provides an ...
+
+  \subsection*{Availabilityand implementation}
+  The AGEAS code is available at \url{https://github.com/JackSSK/Ageas}.
 \end{abstract}
@@
   % Although the regulatory source and target of GRP can be determined by utilizing interaction database, such as \emph{GTRD}\cite{gkaa1057} which shows regulatory relationship of interactors, numerous computational prediction methods like \emph{GRNBoost2}\cite{grnboost2} and comprehensive interaction database, \emph{BioGRID}\cite{biogrid} for example, could not provide faithful indication on regulatory directions.
-  % Consequently, based on choice of interaction database, the regulon reconstructed with \emph{AGEAS} cannot be guaranteed to be a directed graph but an undirected graph.
+  % Consequently, based on choice of interaction database, the regulon reconstructed with AGEAS cannot be guaranteed to be a directed graph but an undirected graph.
   % Therefore, in this step, \emph{odysseia} primarily extracts genes with high regulatory degrees in the regulon, regardless of they act as source or target in GRPs.
-  % To limit total amount of output key genes, the default setting of \emph{AGEAS} reconstructs regulon for top 100 GRPs, and genes with regulatory degree higher than two in the regulon will be considered influential.
+  % To limit total amount of output key genes, the default setting of AGEAS reconstructs regulon for top 100 GRPs, and genes with regulatory degree higher than two in the regulon will be considered influential.
   % If regulatory directions can be clarifed, the regulatory sources capable of regulating multiple key genes and the regulatory targets influenced by multiple key genes can also be extracted according to GRN reconstruction guidance.
@@
   % In the circumstance of finding genes potentially inducing CS conversion, referred as \emph{Mogrify}\cite{mogrify_2016}, both CS deterministic genes and common regulators of these genes shall gain attention.
-  % Herein, \emph{AGEAS} analogized key genes extracted from top GRPs as CS deterministic genes and TFs capable of regulating more than 2 listed key genes as significant common regulator.
+  % Herein, AGEAS analogized key genes extracted from top GRPs as CS deterministic genes and TFs capable of regulating more than 2 listed key genes as significant common regulator.
   %
@@
   % Compared with applying a particular $ML$ model, $CASH$ solving process during automation have higher potential to utilize comprehensive key features instead limited set of them.
-  % Furthermore, due to the network-based essence of \emph{AGEAS}, some CS deterministic features failed to be detected after classification model analysis, if having close regulatory relationships with multiple confirmed GFs, can still be traced down during regulon-based analysis at post stage analysis.
+  % Furthermore, due to the network-based essence of AGEAS, some CS deterministic features failed to be detected after classification model analysis, if having close regulatory relationships with multiple confirmed GFs, can still be traced down during regulon-based analysis at post stage analysis.
 
@@
   \label{method}
-  The basic principle of \emph{AGEAS} is to find key genetic features regulating phenotype of interest through analyzing how well-performing classification models distinguish gene regulatory networks (GRNs) of sample with the phenotype from GRNs of samples without.
+  The basic principle of AGEAS is to find key regulatory elements associated with phenotype of interest through analyzing how well-performing classification models distinguish GRNs of sample with the phenotype from GRNs of samples without.
   To reconstruct sufficient GRNs for each class, RNA-Seq based expression data is segmented into subsets while each one is analogized as a pseudo-sample having discrete expression data.
-  The pseudo-sample GRNs (psGRNs) are reconstructed accordingly; thus, classification models can be trained, evaluated, and interpreted having gene regulatory pathways (GRPs) as input factors.
-  With heavily weighted GRPs and associated genes repeatedly obtained from interpretations of success sample class predictions, GRNs could be formed and inferred as genetic feature complexes playing important role in differentiating the studying sample classes.
+  The pseudo-sample GRNs (psGRNs) are reconstructed accordingly; thus, classification models can be trained, evaluated, and interpreted having GRPs as input factors.
+  With heavily weighted GRPs and associated genes repeatedly obtained from interpretations of success sample class predictions, GRNs could be formed and inferred playing important role in differentiating the studying sample classes.
   The overall workflow can be summarized as Figure \ref{workflow}.
-  By default setting, four seperate extractor units in workflow run parallelly after data preprocessing part, and all extracted genetic features are used to form GRNs later combined into one atlas.
-  Following sections describe each step of \emph{AGEAS} in more depth.
+  By default setting, four seperate extractor units in workflow run parallelly after data preprocessing part, and all extracted regulatory elements are used to form GRNs later combined into one atlas.
+  Following sections describe each step of AGEAS in more depth.
   % \begin{itemize}
@@
   \caption{
-    The overall workflow of \emph{AGEAS}:
+    The overall workflow of AGEAS:
     \textbf{\emph{(1)}} Reconstruct meta-level GRN (meta-GRN) with expression data of all samples.
@@
       The p-value for rejecting null hypothesis, that expression distribution underlying class 1 samples is the same as the expression distribution underlying class 2 samples, is set to 0.05 by default.
-      Furthermore, a $\log_2$ fold change (log2FC) filter is also implemented in \emph{AGEAS}.
-      However, enabling the log2FC filter is not encouraged considering upstream transcription factors (TFs) indirectly regulating key genes associated with feature of interest may not always have significant expression level difference between sample classes.
+      Furthermore, a $\log_2$ fold change (log2FC) filter is also implemented in AGEAS.
+      However, enabling the log2FC filter is not encouraged considering upstream TFs indirectly regulating key genes associated with feature of interest may not always have significant expression level difference between sample classes.
       The lof2FC filter shall mostly be used in order to decrease meta-GRN's GRP total amount in a compromising position caused by limited computational resources.
@@
       If not further specified, TF list will be retrieved from integrated \emph{TRANSFAC}\cite{transfac} datasets according to the provided species information.
-      Utilizing genetic interaction database like \emph{GTRD}\cite{gkaa1057} and \emph{BioGRID}\cite{biogrid}, \emph{AGEAS} checks whether the binding ability of gene pair is confirmed or not.
+      Utilizing genetic interaction database like \emph{GTRD}\cite{gkaa1057} and \emph{BioGRID}\cite{biogrid}, AGEAS checks whether the binding ability of gene pair is confirmed or not.
       By default, if TF being recorded to have binding site within target gene's promoter range (-1000 to +100) by Chromatin Immunoprecipitation Sequencing (ChIP-Seq) dataset retrieved from \emph{GTRD}\cite{gkaa1057}, the potential GRP gene pair will be passed to expression correlation assessment.
@@
       After potential GRP gene pairs obtained, a expression correlation filter is used to exclude gene pairs having low covariance which implies weak relationship.
-      To assess expression correlation, \emph{AGEAS} applies Pearson's Correlation coefficient\cite{pcc_2012} (PCC) whihc is one of the widely adopted methods\cite{cid_2019}.
+      To assess expression correlation, AGEAS applies Pearson's Correlation coefficient\cite{pcc_2012} (PCC) whihc is one of the widely adopted methods.\cite{cid_2019}
       With default setting, gene pairs can reach absolute correlation coefficient of 0.2 while keeping correspond p-value lower than 0.05 are included in meta-GRN as validated GRP.
@@
     \label{step2}
-    Since \emph{AGEAS} is not aiming to develop optimized model architectures for psGRN classification but gain insights from multiple models as divergent as possible, the main goal of this step is to select configurations of models capable to make correct psGRN classifications from provided configuration set.
+    Since AGEAS is not aiming to develop optimized model architectures for psGRN classification but gain insights from multiple models as divergent as possible, the main goal of this step is to select configurations of models capable to make correct psGRN classifications from provided configuration set.
     Regarding the fact that computational power is limited resource, portion of less efficient model configurations shall be pruned although interpreting success predictions of more classification models would lead to more comprehensive insight into sample class differences.
@@
 
-    \noindent By default, \emph{AGEAS} initializes with 128 model configurations utilizing 9 integrated classification algorithms listed in Table \ref{models}.
+    \noindent By default, AGEAS initializes with 128 model configurations utilizing 9 integrated classification algorithms listed in Table \ref{models}.
 
@@
         \label{models}
-        Classification model algorithms integrated in \emph{AGEAS} with correspond numbers of hyperparameter and preset model configurations.
+        Classification model algorithms integrated in AGEAS with correspond numbers of hyperparameter and preset model configurations.
         Categorical hyperparameters and continuous numerical hyperparameters are clarifed beside total number of hyperparameters ($\# \lambda$).
         Conditional hyperparameters which are required for selected other hyperparameters are shown in brackets if there is any.
-        $\#$ Configs indicates total amount of configurations \emph{AGEAS} applies by default.
+        $\#$ Configs indicates total amount of configurations AGEAS applies by default.
       }
@@
 
-    The general architecture designs of 1D-CNN and Hybrid-CNN are implemented referring to 1D-CNN and 2D-Hybrid-CNN applied in recent cancer type prediction study\cite{mostavi_chiu_huang_chen_2020}.
+    The general architecture designs of 1D-CNN and Hybrid-CNN are implemented referring to 1D-CNN and 2D-Hybrid-CNN applied in recent cancer type prediction study.\cite{mostavi_chiu_huang_chen_2020}
     However, taking one convolution layer and adjacent max-pooling layer as a layer set, we implemented both CNN models with flexibilities on number of layer set, which is fixed as 1 in original research.
@@
 
-    For transformer models, considering psGRNs are already be represented by numerical data matrix while GRPs should barely have positional relationships in the matrix, the embedding layer and positional encoding layer designed for input data tokenization in standard architecture \cite{transformer} are replaced with a single linear layer in \emph{AGEAS}.
+    For transformer models, considering psGRNs are already be represented by numerical data matrix while GRPs should barely have positional relationships in the matrix, the embedding layer and positional encoding layer designed for input data tokenization in standard architecture \cite{transformer} are replaced with a single linear layer in AGEAS.
 
@@
     \label{step3}
-    With selected well-performing models, \emph{AGEAS} already can start repetition of model training and interpretation in \hyperref[step4]{Step 4} to extract key GRPs.
+    With selected well-performing models, AGEAS already can start repetition of model training and interpretation in \hyperref[step4]{Step 4} to extract key GRPs.
     However, few uninformative GRPs in training psGRNs merely relied by any model to make classification could be pruned in advance for saving computational power.
     Furthermore, to prevent classification models focusing on a small group of GRPs regardless of training psGRNs, GRPs draw excessive attention shall also be seperated from psGRNs to improve extraction comprehensiveness.
-    Thus, in this step, \emph{AGEAS} iteratively train classificaion models with dynamic $\alpha_{max}$ portion of psGRNs and obtain feature importance scores as described in \hyperref[features_importances]{subsection} below to find GRPs either scored extremely high or considerably low.
+    Thus, in this step, AGEAS iteratively train classificaion models with dynamic $\alpha_{max}$ portion of psGRNs and obtain feature importance scores as described in \hyperref[features_importances]{subsection} below to find GRPs either scored extremely high or considerably low.
 
@@
     \noindent The $Z_{score}^{thread}$ is input z-score threshold (default set as 3.0), and $IQR$ stands for interquartile range calculated by the beginning of each iteration.\
-    With this criterion, \emph{AGEAS} ensures only GRPs draw significantly more attention shall be selected by each iteration despite the data distribution of varying z-score scalled importance values.
+    With this criterion, AGEAS ensures only GRPs draw significantly more attention shall be selected by each iteration despite the data distribution of varying z-score scalled importance values.
 
-    By default, \emph{AGEAS} iterates this feature selection step for 3 times.
+    By default, AGEAS iterates this feature selection step for 3 times.
 
@@
       \label{features_importances}
-      \emph{AGEAS} applies concept of The Shapley value\cite{roth_1988} for estimating importance of each input feature, equivalent to GRP of input psGRN, in any kind of classification model while making predictions.
+      AGEAS applies concept of The Shapley value\cite{roth_1988} for estimating importance of each input feature, equivalent to GRP of input psGRN, in any kind of classification model while making predictions.
       Specific Shapley value calculation or approximating methods are implemented with \emph{SHAP}\cite{lundberg2017unified} and applied to different algorithms as shown in Table \ref{shap}.
@@
     \label{step4}
-    To extract GRPs can effectively define sample class differences, \emph{AGEAS} iteratively initializes classification models with configurations gained from \hyperref[step2]{Step 2}, trains them with randomly selected $\alpha_{max}$ portion of psGRNs scaled after \hyperref[step3]{Step 3}, and interpret every models' correct predictions as mentioned in \hyperref[features_importances]{subsection} above.
-    At each iteration, \emph{AGEAS} receives a z-score scaled feature importance matrix $A$ and add up each GRP's score accordingly from matrix $A'$ kept from previous iteration if there is one.
+    To extract GRPs can effectively define sample class differences, AGEAS iteratively initializes classification models with configurations gained from \hyperref[step2]{Step 2}, trains them with randomly selected $\alpha_{max}$ portion of psGRNs scaled after \hyperref[step3]{Step 3}, and interpret every models' correct predictions as mentioned in \hyperref[features_importances]{subsection} above.
+    At each iteration, AGEAS receives a z-score scaled feature importance matrix $A$ and add up each GRP's score accordingly from matrix $A'$ kept from previous iteration if there is one.
     Then, top $a$ (default set as 100) ranked GRPs having z-score greater than $0.0$ extracted from $A$ are compared with GRPs extracted from $A'$ by same setting.
-    If less than $d$ (default set as 0.05) portion of GRPs are distinct for GRP sets stratified from $A$ and $A'$, \emph{AGEAS} will consider the GRP extration result from this iteration being consistent with previous one.
+    If less than $d$ (default set as 0.05) portion of GRPs are distinct for GRP sets stratified from $A$ and $A'$, AGEAS will consider the GRP extration result from this iteration being consistent with previous one.
     Extraction iteration will terminate if either encountering $n$ (default set as 3) continuous consistent result or running out of preset iteration number (default set as 10).
@@
     \label{step5}
-    Analoging every GRP previously extracted or seperated with high z-score in \hyperref[step3]{Step 3} as a directional edge connecting two gene vertices, equivalent to a TF and a gene, in graph theory, \emph{AGEAS} attempts to reconstruct a network graph representing regulatory differences between query sample classes.
+    Analoging every GRP previously extracted or seperated with high z-score in \hyperref[step3]{Step 3} as a directional edge connecting two gene vertices, equivalent to a TF and a gene, in graph theory, AGEAS attempts to reconstruct a network graph representing regulatory differences between query sample classes.
     Since there is no guarantee on all GRP edges can be connected, some regulatory relationships between gene vertices could be missed.
-    Hence, \emph{AGEAS} utilizes meta-GRN gained from \hyperref[step1]{Step 1} to find GRPs which can further elucidate the regulatory relationships and adds the GRPs back to the network graph.
+    Hence, AGEAS utilizes meta-GRN gained from \hyperref[step1]{Step 1} to find GRPs which can further elucidate the regulatory relationships and adds the GRPs back to the network graph.
 
-    For a limited iteration time (default set as  1), \emph{AGEAS} exhaustively search meta-GRN for TFs which can directly regulate any genes or TFs already covered in the network graph and add the returned TFs as new vertices.
+    For a limited iteration time (default set as  1), AGEAS exhaustively search meta-GRN for TFs which can directly regulate any genes or TFs already covered in the network graph and add the returned TFs as new vertices.
     Next, any GRP in meta-GRN capable to connect two distinct vertices will be added if it is not covered yet.
-    The network graph after expansion above represents the key genetic regulatory differences \emph{AGEAS} extracted from input sample classes.
+    The network graph after expansion above represents the key genetic regulatory differences AGEAS extracted from input sample classes.
 
@@
   \label{res}
-  To assess \emph{AGEAS}'s predictive power, we first applied \emph{AGEAS} to study somatic reprogramming to induced pluripotent stem cells (iPSC) achieved in mice by
-  the year 2006 \cite{yamanaka_2006}, milestone discovery of cell plasticity \cite{cell_repro_review}.
-  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, single-cell RNA sequencing (scRNA-Seq) based gene expression matrices (GEMs) of embryonic stem cell (ESC) and mouse embryonic fibroblast (MEF) were used as input.
+  To assess AGEAS's predictive power, we first applied AGEAS to study somatic reprogramming to induced pluripotent stem cells (iPSC) achieved in mice by the year 2006, \cite{yamanaka_2006} milestone discovery of cell plasticity.
+\cite{cell_repro_review}
+  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, public scRNA-Seq based gene expression matrices (GEMs) of embryonic stem cells (ESCs) and mouse embryonic fibroblasts (MEFs) shown in Table \ref{geo_table} were used as input.
   The extraction result can be summarized as TF regulons, collections of a TF and corresponding direct regulatory targets, and TFs forming largest regulons with extracted GRPs are shown in Figure \ref{result_figs}(a).
-  Among TFs with sizeable regulons, Pou5f1 (Oct4), Nanog, and Sox2 also have most significant expression changes between MEF and ESC.
+  Among TFs with sizeable regulons, Pou5f1 (Oct4), Nanog, and Sox2 are also most differentially expressed in MEF and ESC samples.
   Thus, we can infer these TFs as import factors closely related with cell type differences.
-  Multiple previous studies have confirmed that all of Oct4, Nanog, and Sox2 are playing important role in maintaing pluripotency \cite{niwa_2007} and inducing conversion from somatic cell to iPSC \cite{yamanaka_2006, ips7f, ipsOK, oct4_nanog_sox2_lin28, oct4_nanog_sox2}.
+  Multiple previous studies confirmed that all of Oct4, Nanog, and Sox2 are playing important role in maintaing pluripotency \cite{niwa_2007} and inducing conversion from somatic cell to iPSC.
+\cite{yamanaka_2006, ips7f, ipsOK, oct4_nanog_sox2_lin28, oct4_nanog_sox2}
 
-  To further address \emph{AGEAS}'s applicability and limitation, we applied \emph{AGEAS} to three other scRNA-Seq based studies in distinct research areas.
-  With all default settings and analytical procedure applied above, we can assess \emph{AGEAS}'s performance in following scenarios:
+  To further address AGEAS's applicability and limitation, we applied AGEAS to three other scRNA-Seq based studies in distinct research areas.
+  With all default settings and analytical procedure applied above, we can assess AGEAS's performance in following scenarios with public data set shown in Table \ref{geo_table}:
 
-  \subsection*{Dopaminergic neuron generation}
-  (Cell subtype differentiation)
-  iPSC-derived radial glial/neuronal co-culture to dopaminergic (DA) neurons...
-  ISL1: essential functions of Isl1 in prethalamic dopaminergic neuron development
-  % doi:10.1016/j.ydbio.2012.06.010
-  PHOX2B: Phox2b Influences Dopaminergic Development
-  % https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3522650/pdf/pone.0052118.pdf
-  ELF3: ELF3 was found to be associated with mouse neural stem cell development
-  % (Tang, Y.; Katuri, V.; Iqbal, S.; Narayan, T.; Wang, Z.; Lu, R.S.; Mishra, L.; Mishra, B.
-ELF a β-spectrin is a neuronal precursor cell marker in developing mammalian brain; structure and organization of the elf/β-G spectrin gene.
-Oncogene 2002, 21, 5255–5267.)
-  (ASCL1 also extracted as 12th but not having significant exp change -> how to better analysis result)
+  \begin{itemize}
+    \setlength\itemsep{0em}
+    \item {\textbf{Dopaminergic neuron generation}}:
 
-  \subsection*{Postnatal cardiomyocyte maturation}
-  (Physiological development)
-  Postnatal CM p7 to p28
-  Esr1: estrogenic regulation for normal myocardial development was primarily via ER-alpha(Esr1)
-  % (10.1016/j.mce.2013.11.011)
-  % (http://dx.doi.org/10.1016/j.mce.2013.11.011)
-  Cebpb: The Transcription Factor CEBP-beta Serves as a Master Regulator of physiologic Cardiac Hypertrophy
-  % (Cell. 2010;143:1072–1083)
-  % (Originally published4 Feb 2011https://doi.org/10.1161/RES.0b013e31820ff484Circulation Research. 2011;108:277–278)
-  Sp1:
+      Analyzing difference between human iPSC-derived radial glial / neuronal co-culture, as neural progenitors,\cite{ASCL1_dopaminergic_neuron_2021} and tyrosine hydroxylase (TH) expressing purified dopaminergic (DA) neurons, we address the applicability of AGEAS on cell subtype differentiation problems.
 
-  \subsection*{Hepatic stellate cell activation in $CCl_4$ acute liver model}
-  (Pathological development)
-  HSCs p6w vs PFs p6w analoging activated HSCs
-  Lhx2
-  Osr1
-  Ebf1
+      From extracted TFs shown in Figure \ref{result_figs}(b), we hypothesize ISL1, PHOX2B, and ELF3, referring to their correspond regulon sizes and differential expression profiles, are regulating essential functions differentiating DA neurons from neural progenitors.
+      Both ISL1 and PHOX2B were found related with DA phenotype in previous studies:
+      ISL1 is essential for differentiation of prethalamic DA neurons,\cite{isl1_da}
+      and PHOX2B is connected with TH expression influencing DA neuron development and improving DA activity. \cite{phox2_caudal_da, phox2_rat_da}
+      Moreover, ELF3 was found to be neuronal precursor cell marker associated with neural stem cell development, \cite{ELF3_precursor_marker} consistent with it's high expression level in neuronal co-culture class.
+
+      EBF1, which forms the largest regulon with extracted GRPs, was determined as key neuronal differentiation regulator in the ventral telencephalon, nature source of neuronal and glial cells.
+\cite{ebf1_striatum, ebf1_cell_diff}
+      Furthermore, EBF1 plays important role in mesodiencephalic DA neuron migration. \cite{ebf1_migration}
+      ASCL1, found as necessary factor regulating DA neurotransmitter selection by original research where we retrieved scRNA-Seq data,\cite{ASCL1_dopaminergic_neuron_2021} is also forming substantial regulon.
+      % SOX2 and NR3C1 also have reports in neuronal differentiation...
+      Remarkably, within extracted network, ASCL1 appears to act as upstream regulator of several large TF regulons, including ISL1 and PHOX2B, in purified DA neurons.
+
+    \item {\textbf{Postnatal cardiomyocyte maturation}}:
+
+      To address the performance of AGEAS while analyzing cell physiological development, scRNA-Seq data of cardiomyocytes (CMs) in postnatal day 7 mice (P7) and day 28 mice (P28) are used as input for extracting key genetic regulatory elements in postnatal cardiomyocyte maturation.
+
+      Following same regulon size and expression profile based analytical procedure, we primarily investigated three TFs shown in Figure \ref{result_figs}(c): Sp1, Esr1 ($ER\alpha$), and Cebpb.
+      Previous studies demonstrated that Sp1 promotes CM hypertrophy \cite{sp1_hypertrophy} and maturation of electrophysiology and $Ca^{2+}$ handling. \cite{Sp1_electrophysiologt, CM_mature}
+      % trans-activation of the SERCA2 promoter
+      Esr1 was found modulating myocardial development for postnatal cardiac growth,\cite{esr1_cm, esr1_cm_growth} and Cebpb's role as repressor of CM growth and proliferation while preventing pathological CM hypertrophy also demonstrated by several studeis.\cite{cebpb_1, cebpb_2}
+
+      Other TFs known playing important roles in CM maturation, such as Srf, \cite{CM_mature, cebpb_1} Nkx2-5,\cite{cebpb_1, nkx25, CM_posnatal_mature} and Yap1,\cite{CM_mature, yap1, CM_posnatal_mature} are also forming sizeable regulons in GRN atlas returned by AGEAS.
+
+    \item {\textbf{Hepatic stellate cell activation in $CCl_4$ induced liver fibrosis}}:
+
+      Here we address AGEAS's applicability on cell pathological development studies through analyzing hepatic stellate cells (HSCs) in mice liver administrated with chronic carbon tetrachloride ($CCl_4$) for 6 weeks and according portal fibroblasts (PF) simulating activated HSCs.
+
+      Within TFs shown in Figure \ref{result_figs}(d), we suppose Lhx2, Osr1, and Ebf1 are regulating HSC activation considering their correspond TF regulon sizes and expression changes.
+      Previously, Lhx2 was found indispensable for quiescent HSCs. \cite{lhx2_fibro, Lhx2_hsc_1}
+      Extensive studies found Osr1 related with pathological fibrogenic process in liver fibroblast. \cite{osr1_1, osr1_2, osr1_3}
+      However, little literature address Ebf1's role in liver fibrosis.
+      One recent study reported the expression of Ebf1 increases concurrent with Acta2, marker gene of myofibroblast formation\cite{acta2_myofb_marker} which is essential for fibrosis, in wound fibroblast.
+\cite{ebf1_fibroblast}
+      Also, Ebf1 was found associated with lung fibrosis.\cite{ebf1_lung}
+
+      Furthermore, Mef2c, forming largest TF regulon, has been well-documented as key regulator in HSC activation. \cite{mef2c_1, mef2c_2, mef2c_3}
+
+  \end{itemize}
 
@@
     \caption{
-      TFs forming largest regulons with GRPs extracted by \emph{AGEAS}.
+      TFs forming largest regulons with GRPs extracted by AGEAS.
       Each TF has regulon size indicating amount of direct regulatory genes and $log_2$ gene expression levels in binary sample classes.
@@
 
-  \vspace{\baselineskip}
-  \noindent To demonstrate empirically the predictive capabilities...
+  To demonstrate empirically the predictive capabilities...
+  Since Lhx2's expression pattern is strongly favoring HSC than PF, and previous study proved Lhx2 KO promotes liver fibrosis\cite{lhx2_fibro}...
+  We suppose overexpression of Lhx2 could halt HSC as quiescent in order to prevent pathological fibrogenic process...
+  In vitro experiment goes here...
 
-  %
   % \begin{table}[ht]
@@
   \label{disc}
-  TBD
+
+  In present study, we showed AGEAS's applicability in analyzing scRNA-Seq derived data in cell reprogramming development, cell subtype differentiation .
+  According to test cases so far, key TFs closely related with sample class difference appear to either form substantial regulon with extracted GRPs or high regulatory influence on other key genes.
+  Without any previous knowledge on studying CSs, Gene Ontology (GO) enrichment analysis can potentially narrow down key cellular functions changed in different CSs.
+
+  However, larger scales of applicability test can further confirm AGEAS's capability on guiding frontier researches.
+  While more computational resources become available, other classification algorithms and according interpretation methods will be added and tested with current version on larger scales.
+
+  With result achieved so far, we anticipate that AGEAS will become useful in providing insightful advices on not only learning differences between CSs and cell subtypes, but also finding key GFs to induce CS conversions unachievable so far.
+
+  Limitations...
+  Fidelity of GRPs...
+  Reconstruct GRN with ATAC-Seq by motif enrichment instead of ChIP-Seq... (especially considering technology like Share-Seq which can perform scRNA-Seq with scATAC-Seq in same cell simultaneously...)
+  Apply AGEAS on tissue studies with spatial transcriptomics...
 
@@
   \hline
-  a6w hsc & GSM4085625 \\
+  $CCl_4$ a6w hsc & GSM4085625 \\
   \hline
-  a6w pf & GSM4085627 \\
-  \hline
-  healthy hsc & GSM4085623 \\
-  \hline
-  healthy pf & GSM4085626 \\
+  $CCl_4$ a6w pf & GSM4085627 \\
+  % \hline
+  % healthy hsc & GSM4085623 \\
+  % \hline
+  % healthy pf & GSM4085626 \\
 
@@
   \hline
-  neural co-culture & GSM5609927 \\
+  glial/neuronal co-culture & GSM5609927 \\
   \hline
-  purified neurons & GSM5609930 \\
+  purified DA neurons & GSM5609930 \\
 
@@
   \multicolumn{2}{|l|}{GSE156482 } \\
+  % \hline
+  % p4 cm & GSM4732219 \\
   \hline
-  p4 cm & GSM4732219 \\
+  p7 CM & GSM4732221 \\
   \hline
-  p7 cm & GSM4732221 \\
-  \hline
-  p28 cm & GSM4732225 \\
-  \hline
-  p28 ncm & GSM4732226 \\
+  p28 CM & GSM4732225 \\
+  % \hline
+  % p28 ncm & GSM4732226 \\
 
@@
     \label{geo_table}
-    GEO data source table.
   }
@@
 \end{document}
-
-% \begin{enumerate}
-% \setlength\itemsep{0em}
-% \item {\textbf{Gene level}}:
-% sth
-% \begin{itemize}
-% \setlength\itemsep{0em}
-% \item \textbf{SD Filter}: sth
-% sth
-% \end{itemize}
-% \item {\textbf{Pathway level}}:
-% sth
-% \begin{itemize}
-% \setlength\itemsep{0em}
-% \item \textbf{GRP Filter}: sth
-% sth
-% \end{itemize}
-% \end{enumerate}

### 2022-10-05 ageas/__init__.py

@@ -25,8 +25,8 @@ AGEAS
 ========
 Summary
 -------
-AGEAS (AutoML-based Genetic fEatrue extrAction System)
-is to find key genetic factors, including genes and regulatory pathways,
+AGEAS (AutoML-based Genetic regulatory Element extrAction System)
+is to find key genetic regulatory elements, including genes and regulatory pathways,
 in determining cellular phenotype.
 
 For more information, please visit our GitHub repo:

### 2022-10-05 setup.py

@@ -8,7 +8,7 @@ setuptools.setup(
     version = "v0.0.1-alpha7",
     author = "nkmtmsys and JackSSK",
     author_email = "gyu17@alumni.jh.edu",
-    description = "AutoML-based Genetic fEatrue extrAction System",
+    description = "AutoML-based Genetic regulatory Element extrAction System",
     long_description = long_description,
     long_description_content_type = "text/markdown",
     url = "https://github.com/JackSSK/Ageas",

### 2022-10-05 docs/manuscript/main.tex
v0.0.1a9
minor stuffs

@@
   While single-cell RNA sequencing (scRNA-Seq) made high-resolution transcriptomic view increasingly accessible, precise identification of gene regulatory network (GRN) describing cell states became achievable.
-  However, extracting key regulatory elements, including gene regulatory pathways (GRPs), transcription factors (TFs), and downstream genes, accurately reflecting main functionality changes remain challenging.
+  However, extracting key regulatory elements, including gene regulatory pathways (GRPs), transcription factors (TFs), and downstream genes, accurately and comprehensively reflecting main functionality changes remains challenging.
   Herein, we describe AGEAS, an automated machine learning (AutoML) based genetic regulatory element extraction system that assesses importances of GRPs in differentiating sample classes, such as cell types and developmental stages.
@@
       Firstly, genes included in the comprehensive GEMs are assessed and determined whether having potential to form informative GRPs with other genes.
-      Commonly, differentially expressed genes (DEGs) would be considered as important factors of studying feature.
+      Commonly, differentially expressed genes (DEGs) would be considered as important factors of studying phenotype.
       Here we apply the Mann-Whitney U rank test (MWW) implemented by \emph{SciPy}\cite{2020SciPy-NMeth} to exclude genes having indistinguishable expression level distribution across GEMs of different classes.
@@
       Furthermore, a $\log_2$ fold change (log2FC) filter is also implemented in AGEAS.
-      However, enabling the log2FC filter is not encouraged considering upstream TFs indirectly regulating key genes associated with feature of interest may not always have significant expression level difference between sample classes.
+      However, enabling the log2FC filter is not encouraged considering upstream TFs indirectly regulating key genes associated with phenotype of interest may not always have significant expression level difference between sample classes.
       The lof2FC filter shall mostly be used in order to decrease meta-GRN's GRP total amount in a compromising position caused by limited computational resources.

### 2022-10-09 docs/manuscript/main.tex
v0.0.1a9
Manuscript draft done

--- 2022-10-05 docs/manuscript/main.tex
@@
 \affil[+]{these authors contributed equally to this work}
-\keywords{Machine Learning, Gene Regulatory Network, RNA-Seq, Chip-Seq}
+\keywords{Machine Learning, Gene Regulatory Network, RNA-seq, Chip-seq}
 
@@
   As rapid progress in sequencing technology since last decade, numerous mechanisms underlying cell functions and developmental processes have been revealed as complex regulations of gene expressions.
-  While single-cell RNA sequencing (scRNA-Seq) made high-resolution transcriptomic view increasingly accessible, precise identification of gene regulatory network (GRN) describing cell states became achievable.
-  However, extracting key regulatory elements, including gene regulatory pathways (GRPs), transcription factors (TFs), and downstream genes, accurately reflecting main functionality changes remain challenging.
-  Herein, we describe AGEAS, an automated machine learning (AutoML) based genetic regulatory element extraction system that assesses importances of GRPs in differentiating sample classes, such as cell types and developmental stages.
-  With several case studies in divergent research areas, we show that AGEAS can indeed extract informative regulatory elements and reconstruct networks referring phenotype or biological process of interest.
-  Furthermore, wet lab experiment validations...
-  Overall, AGEAS provides an ...
+  While single-cell RNA sequencing (scRNA-seq) made high-resolution transcriptomic view increasingly accessible, precise identification of gene regulatory network (GRN) describing cell types and cell states became achievable.
+  However, extracting key regulatory elements, including gene regulatory pathways (GRPs), transcription factors (TFs), and targetomes, accurately and completely reflecting functionality changes in biological phenomena remains challenging.
+  Herein, we describe AGEAS, an semi-supervised automated machine learning (AutoML) based genetic regulatory element extraction system that assesses importances of GRPs in resulting biological phenomena, such as cell type differentiation, physiological and pathological development, and reconstruct GRNs with extracted important GRPs for comprehensive inference.
+  With several case studies in divergent research areas, we show that AGEAS can indeed extract informative regulatory elements and reconstruct networks referring biological phenomena of interest.
+  Furthermore, we validated applicability of AGEAS with empirical evidence that LIM homeobox 2 (Lhx2), key quiescent hepatic stellate cell (HSC) factor AGEAS extracted through analyzing chronic carbon tetrachloride ($CCl_4$) induced liver fibrosis data, can indeed halt HSC activation to prevent fibrogenic process.
 
-  \subsection*{Availabilityand implementation}
+  \subsection*{Availability and implementation}
   The AGEAS code is available at \url{https://github.com/JackSSK/Ageas}.
@@
   \label{introduction}
-  TBD
-  % If analoging regulon with the graph concept in discrete mathematics, one of the most common methods to analyze influence of a vertex, which is equivalent to a gene, is assessing correspond degree of the vertex.
-  % Although the regulatory source and target of GRP can be determined by utilizing interaction database, such as \emph{GTRD}\cite{gkaa1057} which shows regulatory relationship of interactors, numerous computational prediction methods like \emph{GRNBoost2}\cite{grnboost2} and comprehensive interaction database, \emph{BioGRID}\cite{biogrid} for example, could not provide faithful indication on regulatory directions.
-  % Consequently, based on choice of interaction database, the regulon reconstructed with AGEAS cannot be guaranteed to be a directed graph but an undirected graph.
-  % Therefore, in this step, \emph{odysseia} primarily extracts genes with high regulatory degrees in the regulon, regardless of they act as source or target in GRPs.
-  % To limit total amount of output key genes, the default setting of AGEAS reconstructs regulon for top 100 GRPs, and genes with regulatory degree higher than two in the regulon will be considered influential.
-  % If regulatory directions can be clarifed, the regulatory sources capable of regulating multiple key genes and the regulatory targets influenced by multiple key genes can also be extracted according to GRN reconstruction guidance.
-  %
-  % In the circumstance of finding genes potentially inducing CS conversion, referred as \emph{Mogrify}\cite{mogrify_2016}, both CS deterministic genes and common regulators of these genes shall gain attention.
-  % Herein, AGEAS analogized key genes extracted from top GRPs as CS deterministic genes and TFs capable of regulating more than 2 listed key genes as significant common regulator.
-  %
-  % Both non-convergence issue and feature lost issue reflect on one of the key problems for $AutoML$: "No single machine learning method performs best on all datasets".\cite{NIPS2015_11d0e628}
-  % Even though this problem can be solved while viewing $AutoML$ as a $CASH$ problem \cite{thornton2013auto}, such approach may not be directly deployable in our scenario considering comprehensive CS deterministic GFs or GRPs could be hardly labeled out.
-  % Hence, in contrast with directly automating key features finding process, we decide to partially automate CS classification process and export candidate components of joint algorithm to feature importance analysis.
-  % Compared with applying a particular $ML$ model, $CASH$ solving process during automation have higher potential to utilize comprehensive key features instead limited set of them.
-  % Furthermore, due to the network-based essence of AGEAS, some CS deterministic features failed to be detected after classification model analysis, if having close regulatory relationships with multiple confirmed GFs, can still be traced down during regulon-based analysis at post stage analysis.
+  As high-resolution sequencing technologies become increasingly applicable and accessible, an efficient and robost analytical system capable of extracting key genetic features responsible for cell types and cell states difference with limited prior biological knowledge also become highly demanded.
+  Several methodologies like SCENIC \cite{Scenic} already demonstrated informativeness and robustness in studying cellular phenotypes with GRN analysis.
+  Regulons, collections of a TF and corresponding targetomes, can successfully address cell identities with more comprehensive information compared with differential expressing genes (DEGs).
+\cite{Scenic, pySCENIC}
+  Even though limited computational methods are capable to completely and precisly extract key genetic regulatory elements in biological process of interest, Mogrify\cite{mogrify_2016} and CellNet\cite{cellnet_2014} have demonstrated GRN based methods can help to analysis cell type differentiation and implement cell reprogramming.
+  However, either method may require large scale of additional background data to be applicable in other studies such as analyzing physiological or pathological development of selected cell type.
+  The scREMOTE \cite{scREMOTE} published in 2022 shows great potential as generalized regulatory element extraction method since limited background data is required with sequencing data representing sample classes.
+  But prior knowledge on key TFs and marker genes is still indispensable.
+  Indeed, a regulation trajectory of DEGs or regulons showing significant activity difference after GRN reconstruction would be able to reveal the developmental pathways as generalized approach, but numerous noisy signals are expected due to general gene regulatory nature of TFs.
+  Therefore, here we present AGEAS with feasibility in extracting key regulatory elements for biological phenomena of interest even with scarce prior knowledge and potentially promote further experiments.
+
+  Several reasons motivated us to develop semi-supervised AutoML based method.
+  Firstly, accurate labeling of regulatory elements' relativeness in biological phenomena would require extensive prior knowledge in according research area that may hardly available.
+  While unsupervised clustering can potentially extract factos playing important roles, this approach would result in lossing comprehensiveness through focusing on specific aspects with regulatory elements showing similar patterns.
+  As a result, we chose to apply biological phenomena reflecting sample classes, such as cell types and cell states which should be easily retrievable, as labels for classification models to predict with masked GRN as input and then interpret success predictions to extract key regulatory elements.
+  Secondly, developing a generalized classificaton model in differentiating GRNs is still hard to guarantee comprehensiveness considering that capturing few significant differences would be sufficient for the model to reach outstanding accuracy.
+  Hence, a extraction system with multiple independent classification models implemented with various algorithms should be helpful to recover from potential comprehensiveness loss.
+  Thirdly, the process of interpreting all success prediction made by every classificaion model and integrating corresponding interpretation results is expected to be extremely computational expensive.
+  Thus, applying AutoML-based model and feature selection procedure that can effectively decreas interpretation cost would be necessary to increase feasibility of the method.
+
+  To evaluate performance of AGEAS, we primarily applied AGEAS in studying somatic cell reprogramming process and then further addressed performance in analyzing 3 other biological process in cell subtype differentiation, physiological and pathological development.
+  Later, we also addressed the applicability of AGEAS extraction result in guiding further studies about biological phenomena with $in$ $vitro$ experiments in determining Lhx2, key TF regulating liver fibrosis extracted with AGEAS, can indeed inhibit HSC activation.
 
@@
   \label{method}
-  The basic principle of AGEAS is to find key regulatory elements associated with phenotype of interest through analyzing how well-performing classification models distinguish GRNs of sample with the phenotype from GRNs of samples without.
-  To reconstruct sufficient GRNs for each class, RNA-Seq based expression data is segmented into subsets while each one is analogized as a pseudo-sample having discrete expression data.
+  The basic principle of AGEAS is to find key regulatory elements associated with biological phenomena of interest through analyzing how well-performing classification models distinguish GRNs of sample with the phenomena from GRNs of samples without.
+  To reconstruct sufficient GRNs for each class, RNA-seq based expression data is segmented into subsets while each one is analogized as a pseudo-sample having discrete expression data.
   The pseudo-sample GRNs (psGRNs) are reconstructed accordingly; thus, classification models can be trained, evaluated, and interpreted having GRPs as input factors.
-  With heavily weighted GRPs and associated genes repeatedly obtained from interpretations of success sample class predictions, GRNs could be formed and inferred playing important role in differentiating the studying sample classes.
+  With heavily weighted GRPs and correspond genes repeatedly obtained from interpretations of success sample class predictions, GRNs could be formed and potentially playing important role in differentiating the studying sample classes.
   The overall workflow can be summarized as Figure \ref{workflow}.
-  By default setting, four seperate extractor units in workflow run parallelly after data preprocessing part, and all extracted regulatory elements are used to form GRNs later combined into one atlas.
+  By default setting, four seperate extractor units in workflow run parallelly after data preprocessing part in order to increase output stability considering stochastic nature of AGEAS, and all extracted regulatory elements are used to form GRNs later combined into one atlas.
   Following sections describe each step of AGEAS in more depth.
@@
   % \end{itemize}
-  \begin{figure}[ht]
-  \centering
-  % \includegraphics[width=0.8\linewidth, height=18cm, keepaspectratio,]{../images/summary_trans.png}
-  \includegraphics[width=0.8\linewidth, keepaspectratio,]{../images/summary_trans.png}
-  \caption{
-    The overall workflow of AGEAS:
-    \textbf{\emph{(1)}} Reconstruct meta-level GRN (meta-GRN) with expression data of all samples.
-    \textbf{\emph{(2)}} Build pseudo-samples with sliding window algorithm and reconstruct GRNs with GRPs identified in meta-GRN accordingly.
-    \textbf{\emph{(3)}} Select best performing classifiers in predicting class labels of pseudo-sample GRNs (psGRNs).
-    \textbf{\emph{(4)}} Interpret how top models make classifications and gradually exclude GRPs with low weights or outlier-level high weights.
-    \textbf{\emph{(5)}} Repeatedly train classifiers with differnt set of psGRNs as training data to extract GRPs frequently ranked as top important features for decision.
-    \textbf{\emph{(6)}} Reconstruct GRNs with extracted GRPs and GRPs excluded as significant outliers.
-  }
-  \label{workflow}
-  \end{figure}
 
@@
     The main purpose of this step is to build pseudo-samples and reconstruct corresponding pseudo-sample GRNs (psGRNs).
-    % Instead of finding genes being important to differentiate sample classes and infer gene regulatory networks (GRNs) with the genes,
     For each sample class, gene expression matrices (GEMs) labeled with same class label are concatenated as one comprehensive expression matrix.
@@
       Firstly, genes included in the comprehensive GEMs are assessed and determined whether having potential to form informative GRPs with other genes.
-      Commonly, differentially expressed genes (DEGs) would be considered as important factors of studying feature.
+      Commonly, differentially expressed genes (DEGs) would be considered as important factors of studying  phenomena.
       Here we apply the Mann-Whitney U rank test (MWW) implemented by \emph{SciPy}\cite{2020SciPy-NMeth} to exclude genes having indistinguishable expression level distribution across GEMs of different classes.
-      The p-value for rejecting null hypothesis, that expression distribution underlying class 1 samples is the same as the expression distribution underlying class 2 samples, is set to 0.05 by default.
+      The p-value for rejecting null hypothesis, that expression profile underlying class 1 samples is the same as the expression profile underlying class 2 samples, is set to 0.05 by default.
       Furthermore, a $\log_2$ fold change (log2FC) filter is also implemented in AGEAS.
-      However, enabling the log2FC filter is not encouraged considering upstream TFs indirectly regulating key genes associated with feature of interest may not always have significant expression level difference between sample classes.
+      However, enabling the log2FC filter is not encouraged considering upstream TFs indirectly regulating key genes associated with phenomena of interest may not always have significant differential expression profiles.
       The lof2FC filter shall mostly be used in order to decrease meta-GRN's GRP total amount in a compromising position caused by limited computational resources.
-      After differential expression based filters, a standard deviation ($\sigma$) filter is applied to exclude genes either having low expression value or merely affected by dynamic expression status of other genes.
-      By default, the $\sigma$ threshold is set to 1.0, the lowest expression level in raw gene count matrix gained from RNA-Seq data.
+      After differential expression based filters, a standard deviation ($\sigma$) filter is applied to exclude genes either having low expression level or merely affected by dynamic expression status of other genes.
+      By default, the $\sigma$ threshold is set to 1.0, the lowest expression level in raw gene count matrix gained from RNA-seq data.
       The threshold value should be adjusted corresponding to prior knowledge of input GEMs, for example of what normalization method was applied to the GEMs.
@@
       Utilizing genetic interaction database like \emph{GTRD}\cite{gkaa1057} and \emph{BioGRID}\cite{biogrid}, AGEAS checks whether the binding ability of gene pair is confirmed or not.
-      By default, if TF being recorded to have binding site within target gene's promoter range (-1000 to +100) by Chromatin Immunoprecipitation Sequencing (ChIP-Seq) dataset retrieved from \emph{GTRD}\cite{gkaa1057}, the potential GRP gene pair will be passed to expression correlation assessment.
+      By default, if TF being recorded to have binding site within target gene's promoter range (-1000 to +100) by Chromatin Immunoprecipitation Sequencing (ChIP-seq) dataset retrieved from \emph{GTRD}\cite{gkaa1057}, the potential GRP gene pair will be passed to expression correlation assessment.
       For TFs not covered by interaction database, \emph{GRNBoost2}\cite{grnboost2}-like algorithm is initiated to predict potential regulatory target genes.
@@
       The order of GRPs in each psGRN is also unified through adding GRPs included in other psGRNs with 0.0 PCC value.
-
-    \begin{figure}[ht]
-      \centering
-      % \includegraphics[width=0.8\linewidth, height=12cm, keepaspectratio,]{../images/data_preprocess_trans.png}
-      \includegraphics[width=0.8\linewidth, keepaspectratio,]{../images/data_preprocess_trans.png}
-      \caption{
-        Workflow to reconstruct meta-GRN and psGRNs.
-        \textbf{\emph{(1)}} Filter genes from GEMs with log2FC filter(optional), MWW filter, and $\sigma$ filter.
-        \textbf{\emph{(2)}} Find candidate GRP gene pairs from either interaction database or predictions made by \emph{GRNBoost2}\cite{grnboost2}-like algorithm.
-        \textbf{\emph{(3)}} Filter candidate GRP gene pairs with PCC filter and reconstruct meta-GRN with validated GRPs.
-        \textbf{\emph{(4)}} Generate pseudo-samples with SWA.
-        \textbf{\emph{(5)}} Utilize GRPs in meta-GRN as generic guidance to form candidate GRPs for pseudo-samples.
-        \textbf{\emph{(6)}} Filter every candidate GRP for all pseudo-samples with PCC filter and reconstruct psGRNs with validated GRPs.
-      }
-      \label{data_preprocess}
-    \end{figure}
 
@@
     An example of 1D-CNN with 2 convolution layer sets is illustrated in Figure \ref{1dCNN}.
-
-    \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.8\linewidth]{../images/nn.png}
-      \caption{1D-CNN with 2 convolution layer set.}
-      \label{1dCNN}
-    \end{figure}
 
@@
   \label{res}
-  To assess AGEAS's predictive power, we first applied AGEAS to study somatic reprogramming to induced pluripotent stem cells (iPSC) achieved in mice by the year 2006, \cite{yamanaka_2006} milestone discovery of cell plasticity.
+  To assess predictive power of utilizing extraction result of AGEAS, we first applied AGEAS to study somatic reprogramming to induced pluripotent stem cells (iPSC) achieved in mice by the year 2006, \cite{yamanaka_2006} milestone discovery of cell plasticity.
 \cite{cell_repro_review}
-  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, public scRNA-Seq based gene expression matrices (GEMs) of embryonic stem cells (ESCs) and mouse embryonic fibroblasts (MEFs) shown in Table \ref{geo_table} were used as input.
-  The extraction result can be summarized as TF regulons, collections of a TF and corresponding direct regulatory targets, and TFs forming largest regulons with extracted GRPs are shown in Figure \ref{result_figs}(a).
-  Among TFs with sizeable regulons, Pou5f1 (Oct4), Nanog, and Sox2 are also most differentially expressed in MEF and ESC samples.
-  Thus, we can infer these TFs as import factors closely related with cell type differences.
-  Multiple previous studies confirmed that all of Oct4, Nanog, and Sox2 are playing important role in maintaing pluripotency \cite{niwa_2007} and inducing conversion from somatic cell to iPSC.
+  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, public scRNA-seq based GEMs of embryonic stem cells (ESCs) and mouse embryonic fibroblasts (MEFs) shown in Table \ref{geo_table} were used as input.
+  The extraction result can be summarized as TF regulons, and TFs having highest regulatory degree in all extracted GRPs are marked as top TFs (Figure \ref{result_figs}a).
+
+  Among top TFs, Pou5f1 (Oct4) has more association with GRPs extracted as important differential regulatory element between MEF and ESC than any other TFs while forming largest regulon and having expression pattern significantly favoring ESC.
+  Thus, we can infer Pou5f1 is key regulatory element associated with ESC identity.
+  Extensive studies already addressed Pou5f1's important role in maintaing pluripotency. \cite{niwa_2007, oct4_1, oct4_2}
+  Moreover, to implement cell reprogramming to iPSC, Nanog and Sox2 are also noteworthy since they are closely interacting with Pou5f1 in extracted network, having high regulatory degrees, and differentially expressed in ESC.
+  Multiple previous studies confirmed that all of Oct4, Nanog, and Sox2 are playing important role to induce cell conversion from somatic cell to iPSC.
 \cite{yamanaka_2006, ips7f, ipsOK, oct4_nanog_sox2_lin28, oct4_nanog_sox2}
+  Cebpb, Hdac2, and Smc3, extracted as top TFs frequently acting as regulatory source in extracted important GRPs and directly affecting Pou5f1 expression, were also reported with relevant functions.
+\cite{cebpb_ipsc, hdac2_ipsc, rad21_smc3_esc}
 
-  To further address AGEAS's applicability and limitation, we applied AGEAS to three other scRNA-Seq based studies in distinct research areas.
-  With all default settings and analytical procedure applied above, we can assess AGEAS's performance in following scenarios with public data set shown in Table \ref{geo_table}:
+  Therefore, we suppose investigating TFs acting as common regulatory sources in extracted important differential GRPs and correspond regulons can effectively study differences between cell types cell states.
+
+  \subsection*{In silico evaluations}
+    To further address AGEAS's applicability and limitation, we applied AGEAS to three other scRNA-seq based studies in distinct research areas.
+    With all default settings describe in \hyperref[method]{Method} section above, we can assess AGEAS's performance in following scenarios with public data set (Table \ref{geo_table}):
 
@@
 
-      Analyzing difference between human iPSC-derived radial glial / neuronal co-culture, as neural progenitors,\cite{ASCL1_dopaminergic_neuron_2021} and tyrosine hydroxylase (TH) expressing purified dopaminergic (DA) neurons, we address the applicability of AGEAS on cell subtype differentiation problems.
+        Analyzing difference between human iPSC-derived radial glial / neuronal co-culture, as neural progenitors,\cite{ASCL1_dopaminergic_neuron_2021} and tyrosine hydroxylase (TH) expressing purified dopaminergic neurons (DANs), we address the applicability of AGEAS on cell subtype differentiation problems.
 
-      From extracted TFs shown in Figure \ref{result_figs}(b), we hypothesize ISL1, PHOX2B, and ELF3, referring to their correspond regulon sizes and differential expression profiles, are regulating essential functions differentiating DA neurons from neural progenitors.
-      Both ISL1 and PHOX2B were found related with DA phenotype in previous studies:
-      ISL1 is essential for differentiation of prethalamic DA neurons,\cite{isl1_da}
-      and PHOX2B is connected with TH expression influencing DA neuron development and improving DA activity. \cite{phox2_caudal_da, phox2_rat_da}
-      Moreover, ELF3 was found to be neuronal precursor cell marker associated with neural stem cell development, \cite{ELF3_precursor_marker} consistent with it's high expression level in neuronal co-culture class.
+        From extracted TFs (Figure \ref{result_figs}b), we hypothesize ISL1, ELF3, and PBX3 playing important role in DAN differentiation due to their high regulatory degree in extracted important GRPs.
+        Previously, ISL1 was determined essential for differentiation of prethalamic DANs, \cite{isl1_da} and ELF3 was found to be neuronal precursor cell marker associated with neural stem cell development, \cite{ELF3_precursor_marker} consistent with it's high expression level in neuronal co-culture samples.
+        Moreover, a DAN development study reported PBX3 being required for correct differentiation of neuroblast, product of radial glial cell, into midbrain DAN and survival of midbrain DAN.
+\cite{pbx3_dan}
 
-      EBF1, which forms the largest regulon with extracted GRPs, was determined as key neuronal differentiation regulator in the ventral telencephalon, nature source of neuronal and glial cells.
+        Through substratification of all extracted GRPs, we only found HDAC2 and RBPJ as potential upstream regulatory elements of all ISL1, ELF3, and PBX3.
+        Few reports demonstrated HDAC2 is associated with neurogenesis of radial glial cells. \cite{hdac2_dan_1, hdac2_dan_2}
+        Nevertheless, HDAC2's role in DAN differentiation is yet to be clarified.
+        RBPJ was reported essential for DAN survival and affecting DAN development by regulating ASCL1 which is an essential factor in neurogenesis. \cite{rbpj_1, rbpj_2}
+        Original research where we retrieved scRNA-seq data also demonstrated ASCL1 as necessary factor regulating DA neurotransmitter selection. \cite{ASCL1_dopaminergic_neuron_2021}
+        Although AGEAS extracts ASCL1 as one of top TFs; however, no direct regulatory relationship between RBPJ and ASCL1 is identified.
+        % PHOX2B, and ELF3 are regulating essential functions differentiating DANs from neural progenitors referring to their correspond regulon sizes and differential expression profiles.
+        % Both ISL1 and PHOX2B were found related with DA phenotype in previous studies:
+        % ISL1 is
+        % and PHOX2B is connected with TH expression influencing DAN development and improving DA activity. \cite{phox2_caudal_da, phox2_rat_da}
+
+        % EBF1, which forms the largest regulon with extracted GRPs, was determined as key neuronal differentiation regulator in the ventral telencephalon, nature source of neuronal and glial cells.
 \cite{ebf1_striatum, ebf1_cell_diff}
-      Furthermore, EBF1 plays important role in mesodiencephalic DA neuron migration. \cite{ebf1_migration}
-      ASCL1, found as necessary factor regulating DA neurotransmitter selection by original research where we retrieved scRNA-Seq data,\cite{ASCL1_dopaminergic_neuron_2021} is also forming substantial regulon.
-      % SOX2 and NR3C1 also have reports in neuronal differentiation...
-      Remarkably, within extracted network, ASCL1 appears to act as upstream regulator of several large TF regulons, including ISL1 and PHOX2B, in purified DA neurons.
+        % Furthermore, EBF1 plays important role in mesodiencephalic DAN migration. \cite{ebf1_migration}
 
@@
 
-      To address the performance of AGEAS while analyzing cell physiological development, scRNA-Seq data of cardiomyocytes (CMs) in postnatal day 7 mice (P7) and day 28 mice (P28) are used as input for extracting key genetic regulatory elements in postnatal cardiomyocyte maturation.
+        To address the performance of AGEAS while analyzing cell physiological development, scRNA-seq data of cardiomyocytes (CMs) in postnatal day 7 mice (P7) and day 28 mice (P28) are used as input for extracting key genetic regulatory elements in postnatal cardiomyocyte maturation.
 
-      Following same regulon size and expression profile based analytical procedure, we primarily investigated three TFs shown in Figure \ref{result_figs}(c): Sp1, Esr1 ($ER\alpha$), and Cebpb.
-      Previous studies demonstrated that Sp1 promotes CM hypertrophy \cite{sp1_hypertrophy} and maturation of electrophysiology and $Ca^{2+}$ handling. \cite{Sp1_electrophysiologt, CM_mature}
+        As indicated by extracted differential GRPs, we primarily investigated Sp1 and Esr1 ($ER\alpha$) which also have top regulatory degrees and considerably expression changes (Figure \ref{result_figs}c).
+        Previous studies demonstrated that Sp1 promotes CM hypertrophy \cite{sp1_hypertrophy} and maturation of electrophysiology, $Ca^{2+}$ handling. \cite{Sp1_electrophysiologt, CM_mature}
         % trans-activation of the SERCA2 promoter
-      Esr1 was found modulating myocardial development for postnatal cardiac growth,\cite{esr1_cm, esr1_cm_growth} and Cebpb's role as repressor of CM growth and proliferation while preventing pathological CM hypertrophy also demonstrated by several studeis.\cite{cebpb_1, cebpb_2}
+        Esr1 was found modulating myocardial development for postnatal cardiac growth.\cite{esr1_cm, esr1_cm_growth}
 
-      Other TFs known playing important roles in CM maturation, such as Srf, \cite{CM_mature, cebpb_1} Nkx2-5,\cite{cebpb_1, nkx25, CM_posnatal_mature} and Yap1,\cite{CM_mature, yap1, CM_posnatal_mature} are also forming sizeable regulons in GRN atlas returned by AGEAS.
+        Beside inter-regulation between Sp1 and Esr1, 3 other top TFs (Srf, Cebpb, Rest) and 2 TFs forming relatively small regulons (Gata4, Prox1), are expected to have reversible regulation with both Sp1 and Esr1 based on extraction network.
+        All 5 TFs were found having CM maturation related functions. (Table \ref{interact_TFs})
+
+        \begin{table}[ht]
+            \centering
+            \begin{tabular}{|l|l|}
+              \hline
+              \textbf{Gene} & \textbf{Function}  \\
+              \hline
+              Srf & Regulate sarcomere genes and broadly impact almost every aspect of CM maturation\cite{CM_mature} \\
+              \hline
+              Cebpb & Repress CM proliferation and hypertrophy\cite{cebpb_1, cebpb_2}\\
+              \hline
+              Rest (Nrsf) & Repress CM hypertrophy; Prevent dilated cardiomyopathy\cite{rest_1}\\
+              \hline
+              Prox1 & Repress CM hypertrophy; Prevent dilated cardiomyopathy\cite{prox1_CM} \\
+              \hline
+              Gata4 & Promote CM proliferation and hypertrophy\cite{CM_posnatal_mature} \\
+              \hline
+            \end{tabular}
+            \caption{
+              \label{interact_TFs}
+              TFs interacting with both Sp1 and Esr1 order by extracted regulon size.
+            }
+        \end{table}
+
+        % Other top TFs expected to directly influence expression of either Sp1 or Esr1 are:
+        % \begin{table}[ht]
+        %     \centering
+        %     \begin{tabular}{|l|l|}
+        %       \hline
+        %       \textbf{Gene} & \textbf{Function}  \\
+        %       \hline
+        %       Nfe2l2 &  mitochondrial and cardiac oxidative stress, cardiac fibrosis (10.1089/ars.2016.6831) \\
+        %       \hline
+        %       Nfib & 1 \\
+        %       \hline
+        %       Cbfb & 1 \\
+        %       \hline
+        %       Fosl2 & 1 \\
+        %       \hline
+        %       Nkx2-5 & \cite{cebpb_1, nkx25, CM_posnatal_mature} \\
+        %       \hline
+        %       Rxra & 1 \\
+        %       \hline
+        %       Mef2a & 1 \\
+        %       \hline
+        %       Yap1 & \cite{CM_mature, yap1, CM_posnatal_mature} \\
+        %       \hline
+        %       Thra & 1 \\
+        %       \hline
+        %     \end{tabular}
+        %     \caption{
+        %       \label{interact_TFs}
+        %       Extracted top TFs interacting with either Sp1 or Esr1.
+        %     }
+        % \end{table}
 
@@
 
-      Within TFs shown in Figure \ref{result_figs}(d), we suppose Lhx2, Osr1, and Ebf1 are regulating HSC activation considering their correspond TF regulon sizes and expression changes.
-      Previously, Lhx2 was found indispensable for quiescent HSCs. \cite{lhx2_fibro, Lhx2_hsc_1}
-      Extensive studies found Osr1 related with pathological fibrogenic process in liver fibroblast. \cite{osr1_1, osr1_2, osr1_3}
-      However, little literature address Ebf1's role in liver fibrosis.
-      One recent study reported the expression of Ebf1 increases concurrent with Acta2, marker gene of myofibroblast formation\cite{acta2_myofb_marker} which is essential for fibrosis, in wound fibroblast.
-\cite{ebf1_fibroblast}
-      Also, Ebf1 was found associated with lung fibrosis.\cite{ebf1_lung}
+        Based on extracted important GRPs, we identified Mef2c, Jun, and Jund as potential representitives of key regulatory elements in HSC activation (Figure \ref{result_figs}d).
+        As TF extracted with most important GRPs, Mef2c has been well-documented as key regulator in HSC activation. \cite{mef2c_1, mef2c_2, mef2c_3}
+        Extensive studies also found Jun and Jund, both being functional components of the AP1 TF complex, essential for fibrosis-related HSC activation and profibrogenic process.
+\cite{ap1_hsc_1, ap1_hsc_2, ap1_hsc_3, ap1_hsc_4}
 
-      Furthermore, Mef2c, forming largest TF regulon, has been well-documented as key regulator in HSC activation. \cite{mef2c_1, mef2c_2, mef2c_3}
-
+        Analyzing TF regulons of Mef2c, Jun, and Jund, we suppose Mef2c is acting as targetome of Jund and inter-regulatory element of Jun.
+        While no regulatory relationship between Jund and Jun determined, 3 extracted top TFs (Lhx2, Nfib, Junb) can potentially influence expressions of both Jund and Jun.
+        Since Junb is also functional component of AP1, we infer it associated with HSC activaion in a similar manner.
+        Furthermore, Lhx2 was found indispensable for quiescent HSCs. \cite{lhx2_fibro, Lhx2_hsc_1}
+        Although, little literature addressed Nfib's role in HSC, Nfib was reported acting as anti-apoptotic gene for cell proliferation during $CCl_4$ induced liver damage. \cite{Nfib_sadly}
     \end{itemize}
 
-  \begin{figure}
-    \begin{subfigure}{0.49\linewidth}
-      \centering
-      \includegraphics[width=\linewidth, keepaspectratio,]{../images/MEF_ESC_top.png}
-      \caption{}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \centering
-      \includegraphics[width=\linewidth, keepaspectratio,]{../images/N_cocul_top.png}
-      \caption{}
-    \end{subfigure}
+  \subsection*{In vitro validation}
+    To demonstrate empirically the predictive capabilities of utilizing AGEAS extraction result, we further investigated the extraction result of $CCl_4$ induced liver fibrosis study setting scenario of identifying theraputic targets inhibiting pathological fibrogenic process in liver.
+    Through analyzing extracted TF regulons, we further confirmed Mef2c's role as key targetome noticing direct regulational relationships with HSC activation marker Acta2\cite{acta2_hsc_act} and fibrotic collagen Col1a1 (Figure \ref{regulons_figs}d).
+    Moreover, since only Lhx2 has all related GRPs mainly being functional in HSC (Figure \ref{regulons_figs}a) and significantly differential expression in HSC (Figure \ref{result_figs}d), we decided to proceed manipulation of Lhx2 expression.
+    Previous study already proved knockdown of Lhx2 promotes liver fibrosis in mice.\cite{lhx2_fibro}
+    Thus, we suppose overexpression of Lhx2 could assist to maintain quiescent of HSCs through Jun/Jund-Mef2c dependent pathways.
 
-    \begin{subfigure}{0.49\linewidth}
-      \centering
-      \includegraphics[width=\linewidth, keepaspectratio,]{../images/CMp7d_CMp28d_top.png}
-      \caption{}
-    \end{subfigure}
-    \begin{subfigure}{0.49\linewidth}
-      \centering
-      \includegraphics[width=\linewidth, keepaspectratio,]{../images/HSCp6w_PFp6w_top.png}
-      \caption{}
-    \end{subfigure}
+    To verify our hypothesis, we firstly validated the association between Lhx2 and HSC activation with $in$ $vitro$ experiments.
+    In mice primary HSC (mHSC) and human HSC cell lines (LX2), we detected the expression of Lhx2/LHX2 with the activation of HSC.
+    The results showed that the expression of Lhx2 was significantly decreased with the activation of HSC (Figure \ref{hsc_activation_mRNA}), consistent with our previous analysis result.
+    To further clarify the role of LHX2 in human cell, we knocked down LHX2 by small interfering RNA (siRNA) in LX2 cells.
+    The results showed that knockdown of LHX2 significantly promoted the expression of fibrosis-related genes in Figure \ref{hsc_activation_mRNA}d, compatible with previous knowledge in mice.
 
-    \caption{
-      TFs forming largest regulons with GRPs extracted by AGEAS.
-      Each TF has regulon size indicating amount of direct regulatory genes and $log_2$ gene expression levels in binary sample classes.
-      \textbf{\emph{(a)}} Mouse embryonic fibroblast vs. Embryonic stem cell
-      \textbf{\emph{(b)}} Purified dopaminergic neuron vs. Radial glial/neuronal co-culture
-      \textbf{\emph{(c)}} 7 days postnatal cardiomyocyte vs. 28 days postnatal cardiomyocyte
-      \textbf{\emph{(d)}} Hepatic stellate cell vs. Portal fibroblast (both after 6 weeks of CCl4 administration)
-    }
-    \label{result_figs}
-  \end{figure}
+    Subsequently, we overexpressed Lhx2/LHX2 in mHSCs and LX2 cells.
+    The results showed that overexpression of LHX2 directly affected the cell morphology of human HSCs and significantly inhibited the expression of fibrogenic genes (Figure \ref{LHX2_LX2_morphology} and \ref{LHX2_OEs}a).
+    In addition, observation in mHSCs further confirmed that Lhx2 could inhibit the expression of fibrosis-related genes (Figure \ref{LHX2_OEs}b).
+    In order to comprehensively understand the gene expression profile of HSC regulated by LHX2, RNA-seq results showed that the differential genes were mainly related to extracellular matrix structure and assembly (Figure \ref{LHX2_GO}), which was consistent with fibrosis-related phenotype.
 
-  To demonstrate empirically the predictive capabilities...
-  Since Lhx2's expression pattern is strongly favoring HSC than PF, and previous study proved Lhx2 KO promotes liver fibrosis\cite{lhx2_fibro}...
-  We suppose overexpression of Lhx2 could halt HSC as quiescent in order to prevent pathological fibrogenic process...
-  In vitro experiment goes here...
+    Thus, systematic and comprehensive $in$ $vitro$ verification showed that Lhx2/LHX2 is indeed capable to regulate fibrogenic gene expressions and inhibit HSC activation as we concluded from AGEAS extraction output.
+    However, the preliminarily identified regulatory pathways for Lhx2 to inhibit HSC activation is yet to be addressed.
+    % In vivo experiment will take longer time...
 
-  % \begin{table}[ht]
-  %     \centering
-  %     \begin{tabular}{|l|l|l|l|}
-  %       \hline
-  %       \textbf{Gene} & \textbf{Main Exp Class} & \textbf{$|log2FC|$} & \textbf{Description}  \\
-  %       \hline
-  %       Mef2c & 1 & 1.82 & sth \\
-  %       \hline
-  %     \end{tabular}
-  %     \caption{
-  %       \label{ccl4liver_result}
-  %       In total of 35 Genes
-  %     }
-  % \end{table}
+  \subsection*{Conclusion}
+    With result achieved so far, AGEAS shows robustness in extracting key regulatory elements for several biological researches.
+    Key TFs inferred by extracted important GRPs and regulon analysis in all 4 $in$ $silico$ cases were confirmed informative to reveal main functionalities responsible for biological process of interest.
+    Furthermore, the direct extractions of ISL1 in DAN differentiation and Jund in HSC activation as regulatory source in top amount of important GRPs can demonstrate that AGEAS is not focusing solely on TF regulon sizes in reconstructed meta-GRN nor expression differences between sample classes.
+    Also, $in$ $vitro$ experiments indicate great potential in AGEAS to promote method development in phenotypic manipulation.
+    % While TF regulons reconstructed with all extracted GRPs are having sizes proportional to meta-GRN... GO enrichment?
+    % However, whether extracted regulatory elements covering all functional aspects of studying biological phenomena, admittedly, remains undetermined due to lack of validation for GRPs' activities.
+    Overall, we anticipate that AGEAS will become useful in providing insightful regulatory information and promoting pioneer researches in revealing complicate mechanism behind biological phenomena.
 
@@
   \label{disc}
+  Considering the rapid development of both sequencing technology and machine learning algorithms, we implemented
+  AGEAS with modular design.
+  In data preprocessing part, the meta-GRN reconstruction section can be replaced with other methods to further increase fidelity of regulatory relationships or integrating more information such as cis-regulatory elements (CREs) accessibility which can be obtained from Assay for Transposase-Accessible Chromatin Sequencing (ATAC-seq) data.
+  Moreover, CRE accessibility information combining with motif enrichment analysis is proved capable to identity potential regulatory pathways replacing ChIP-seq based dataset AGEAS utilizing in present study.
+\cite{scREMOTE}
+  Refine meta-GRN reconstruction method in consideration of having input data from simultaneous scRNA-seq and single cell ATAC-seq (scATAC-seq), such as SHARE-seq published in late 2020, \cite{share_seq} can potentially further improve applicability of AGEAS; however, accessibility of corresponding datasets will be essential for performance assessment and method development.
+  Similarly, initial set of classificaion models is also subject to be changed responding to future computational studies.
 
-  In present study, we showed AGEAS's applicability in analyzing scRNA-Seq derived data in cell reprogramming development, cell subtype differentiation .
-  According to test cases so far, key TFs closely related with sample class difference appear to either form substantial regulon with extracted GRPs or high regulatory influence on other key genes.
-  Without any previous knowledge on studying CSs, Gene Ontology (GO) enrichment analysis can potentially narrow down key cellular functions changed in different CSs.
+  Also, it is important to note that AGEAS can be applied with GEMs normalized with different methods on user's choice as well as derived from other sequencing technologies such as bulk RNA-seq or spatial sequencing in revealing tissue differences.
+  Replacing transcriptiomic data with proteomic data may also be achievable to analysis protein interaction networks.
+  However, larger scale of applicability tests shall be performed in advance.
 
-  However, larger scales of applicability test can further confirm AGEAS's capability on guiding frontier researches.
-  While more computational resources become available, other classification algorithms and according interpretation methods will be added and tested with current version on larger scales.
+  Due to the stochastic nature of AGEAS, extraction results of AGEAS are not expected to stay identical for repeated applications with exactly same inputs.
+  Main reason underlying the inconsistency is caused by how AGEAS attempt to obtain top performing models for later prediction interpretations.
+  Repeated random subsets of psGRNs using in model training and selection are expected to vary for each application hence resulting in different performance of classification models and ranking results.
+  As a result, the importance values of GRPs might differ and slightly affect top TFs extracted later.
 
-  With result achieved so far, we anticipate that AGEAS will become useful in providing insightful advices on not only learning differences between CSs and cell subtypes, but also finding key GFs to induce CS conversions unachievable so far.
+  Two possible workarounds of inconsistent issue would be:
+  (i) manually set random seed for every process influencing subset selection.
+  (ii) set multiple extractor unit and combine extraction results.
+  In present study, we found n = 4 units yielding relatively stable results, but this value could vary based on application scenario.
 
-  Limitations...
-  Fidelity of GRPs...
-  Reconstruct GRN with ATAC-Seq by motif enrichment instead of ChIP-Seq... (especially considering technology like Share-Seq which can perform scRNA-Seq with scATAC-Seq in same cell simultaneously...)
-  Apply AGEAS on tissue studies with spatial transcriptomics...
-
-% \section*{Conclusion}
-  % \label{conc}
-  % Conclusion goes here
+  Although Lhx2 extracted by AGEAS-based analysis indeed shows capability to inhibit HSC activation during liver fibrosis as predicted, the corresponding inference of functional pathways still need to be proved.
+  Furthermore, $in$ $vivo$ experiments are also necessary to evaluate functionality of Lhx2 and associated pathways for higher fidelity.
 
@@
   \textbf{M.N.}: Methodology, Software
-\textbf{J.T.}: Writing - Review \& Editing, Project administration
+  \textbf{J.T.}: Methodology, Writing- Original draft preparation, Project administration
+% Writing - Review \& Editing,
 
 \section*{Additional information}
-All scRNA-Seq datasets are retrieved from Gene Expression Omnibus(GEO) as described in the Table below.
+  All scRNA-seq datasets are retrieved from Gene Expression Omnibus(GEO) as described in the Table below.
 
@@
     \hline
-  purified DA neurons & GSM5609930 \\
+    purified DANs & GSM5609930 \\
 
@@
 
+\begin{figure}[ht]
+  \centering
+  % \includegraphics[width=0.8\linewidth, height=18cm, keepaspectratio,]{../images/summary_trans.png}
+  \includegraphics[width=0.8\linewidth, keepaspectratio,]{../images/summary_trans.png}
+  \caption{
+    The overall workflow of AGEAS:
+    \textbf{\emph{(1)}} Reconstruct meta-level GRN (meta-GRN) with expression data of all samples.
+    \textbf{\emph{(2)}} Build pseudo-samples with sliding window algorithm and reconstruct GRNs with GRPs identified in meta-GRN accordingly.
+    \textbf{\emph{(3)}} Select best performing classifiers in predicting class labels of pseudo-sample GRNs (psGRNs).
+    \textbf{\emph{(4)}} Interpret how top models make classifications and gradually exclude GRPs with low weights or outlier-level high weights.
+    \textbf{\emph{(5)}} Repeatedly train classifiers with different set of psGRNs as training data to extract GRPs frequently ranked as top important features for decision.
+    \textbf{\emph{(6)}} Reconstruct GRNs with extracted GRPs and GRPs excluded as significant outliers.
+  }
+  \label{workflow}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+  % \includegraphics[width=0.8\linewidth, height=12cm, keepaspectratio,]{../images/data_preprocess_trans.png}
+  \includegraphics[width=0.8\linewidth, keepaspectratio,]{../images/data_preprocess_trans.png}
+  \caption{
+    Workflow to reconstruct meta-GRN and psGRNs.
+    \textbf{\emph{(1)}} Filter genes from GEMs with log2FC filter(optional), MWW filter, and $\sigma$ filter.
+    \textbf{\emph{(2)}} Find candidate GRP gene pairs from either interaction database or predictions made by \emph{GRNBoost2}\cite{grnboost2}-like algorithm.
+    \textbf{\emph{(3)}} Filter candidate GRP gene pairs with PCC filter and reconstruct meta-GRN with validated GRPs.
+    \textbf{\emph{(4)}} Generate pseudo-samples with SWA.
+    \textbf{\emph{(5)}} Utilize GRPs in meta-GRN as generic guidance to form candidate GRPs for pseudo-samples.
+    \textbf{\emph{(6)}} Filter every candidate GRP for all pseudo-samples with PCC filter and reconstruct psGRNs with validated GRPs.
+  }
+  \label{data_preprocess}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{../images/nn.png}
+  \caption{1D-CNN with 2 convolution layer set.}
+  \label{1dCNN}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/top_TFs/MEF_ESC.png}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/top_TFs/N_cocul.png}
+    \caption{}
+  \end{subfigure}
+
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/top_TFs/CMp7d_CMp28d.png}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/top_TFs/HSCp6w_PFp6w.png}
+    \caption{}
+  \end{subfigure}
+
+  \caption{
+    Top 15 TFs ranked by regulatory degrees in all GRPs extracted by AGEAS.
+    % Heatmap at right indicates relative $log_2$ gene expression levels in binary sample classes.
+    \textbf{\emph{(a)}} Mouse embryonic fibroblast vs. Embryonic stem cell
+    \textbf{\emph{(b)}} Purified dopaminergic neuron vs. Radial glial/neuronal co-culture
+    \textbf{\emph{(c)}} 7 days postnatal cardiomyocyte vs. 28 days postnatal cardiomyocyte
+    \textbf{\emph{(d)}} Hepatic stellate cell vs. Portal fibroblast (both after 6 weeks of CCl4 administration)
+  }
+  \label{result_figs}
+\end{figure}
+
+\begin{figure}
+
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/lhx2_class.png}
+    \caption{Lhx2 regulon}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/junb_class.png}
+    \caption{Junb regulon}
+  \end{subfigure}
+
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/nfib_class.png}
+    \caption{Nfib regulon}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/mef2c_class.png}
+    \caption{Mef2c regulon}
+  \end{subfigure}
+
+  \caption{
+    Regulons of extracted top TFs interacting with both Jund and Jun and Mef2c.
+    Class 1 stands for HSC; class 2 stands for PF.
+  }
+  \label{regulons_figs}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_a.png}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_b.png}
+    \caption{}
+  \end{subfigure}
+
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_c.png}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_h.png}
+    \caption{}
+  \end{subfigure}
+  \caption{
+    Relative mRNA expression levels during HSC activation.
+    \textbf{\emph{(a)}} Fibrosis-related gene (Col1a1, Col3a1, Acta2) expression in mHSCs were increased with the extension of culture time, indicating HSC activation.
+    n = 3.
+    \textbf{\emph{(b)}} With the activation of mHSC, expression of Lhx2 decreased gradually.
+    n = 3.
+    \textbf{\emph{(c)}} In human HSC cell line LX2, TGF-$\beta$ can remarkably activate HSC and promote expressions of fibrosis-related genes. % Reference ?
+    Meanwhile, the expression of LHX2 decreased with the activation of HSC.
+    \textbf{\emph{(d)}} Knockdown of LHX2 by siRNA (si-LHX2) significantly increased the expression of fibrosis-related genes in LX2 cells compared with negative control (si-NC).
+    n = 4.
+  }
+  \label{hsc_activation_mRNA}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_d_lx2_wt.png}
+    \caption{LX2-WT}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_d_lx2_pcdh_oe.png}
+    \caption{LX2-PCDH-OE}
+  \end{subfigure}
+
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_d_lx2_lhx2_oe.png}
+    \caption{LX2-LHX2-OE}
+  \end{subfigure}
+  \caption{
+    Overexpression of LHX2 significantly altered cell morphology in LX2 cell lines.
+    \textbf{\emph{(a)}} LX2 wild type.
+    \textbf{\emph{(b)}} LX2 overexpressing negative control vector.
+    \textbf{\emph{(c)}} LX2 overexpressing LHX2.
+  }
+  \label{LHX2_LX2_morphology}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_e.png}
+    \caption{LX2}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
+    \centering
+    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_f.png}
+    \caption{mHSC}
+  \end{subfigure}
+
+  \caption{
+    Overexpression of Lhx2/LHX2 significantly decreased the expression of fibrosis-related genes.
+    \textbf{\emph{(a)}} in LX2 cells. n = 3.
+    \textbf{\emph{(b)}} in mHSCs. n = 3.
+  }
+  \label{LHX2_OEs}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{../images/wet_lab/tao_g.png}
+  \caption{
+    RNA-seq results of LHX2 overexpressed cells showed that gene ontology (GO) enrichment of differentially expressed genes was mainly concentrated in extracellular matrix related genes.
+  }
+  \label{LHX2_GO}
+\end{figure}
+
 % $CASH$        & Combined Algorithm Selection and Hyperparameter optimization\\

### 2022-10-09 docs/manuscript/main.tex
v0.0.1a9
Minor stuffs

@@
   Indeed, a regulation trajectory of DEGs or regulons showing significant activity difference after GRN reconstruction would be able to reveal the developmental pathways as generalized approach, but numerous noisy signals are expected due to general gene regulatory nature of TFs.
-  Therefore, here we present AGEAS with feasibility in extracting key regulatory elements for biological phenomena of interest even with scarce prior knowledge and potentially promote further experiments.
+  Therefore, here we present AGEAS with feasibility in extracting key regulatory elements for biological phenomena of interest even with scarce prior knowledge and potentially promoting further discoveries.
 

### 2022-10-12 docs/manuscript/main.tex
v0.0.1a9
Remove in vitro stuffs

@@
   With several case studies in divergent research areas, we show that AGEAS can indeed extract informative regulatory elements and reconstruct networks referring biological phenomena of interest.
-  Furthermore, we validated applicability of AGEAS with empirical evidence that LIM homeobox 2 (Lhx2), key quiescent hepatic stellate cell (HSC) factor AGEAS extracted through analyzing chronic carbon tetrachloride ($CCl_4$) induced liver fibrosis data, can indeed halt HSC activation to prevent fibrogenic process.
+  % Furthermore, we validated applicability of AGEAS with empirical evidence that LIM homeobox 2 (Lhx2), key quiescent hepatic stellate cell (HSC) factor AGEAS extracted through analyzing chronic carbon tetrachloride ($CCl_4$) induced liver fibrosis data, can indeed halt HSC activation to prevent fibrogenic process.
 
@@
   To evaluate performance of AGEAS, we primarily applied AGEAS in studying somatic cell reprogramming process and then further addressed performance in analyzing 3 other biological process in cell subtype differentiation, physiological and pathological development.
-  Later, we also addressed the applicability of AGEAS extraction result in guiding further studies about biological phenomena with $in$ $vitro$ experiments in determining Lhx2, key TF regulating liver fibrosis extracted with AGEAS, can indeed inhibit HSC activation.
+  % Later, we also addressed the applicability of AGEAS extraction result in guiding further studies about biological phenomena with $in$ $vitro$ experiments in determining Lhx2, key TF regulating liver fibrosis extracted with AGEAS, can indeed inhibit HSC activation.
 
@@
   Therefore, we suppose investigating TFs acting as common regulatory sources in extracted important differential GRPs and correspond regulons can effectively study differences between cell types cell states.
-
-  \subsection*{In silico evaluations}
+  % \subsection*{In silico evaluations}
   To further address AGEAS's applicability and limitation, we applied AGEAS to three other scRNA-seq based studies in distinct research areas.
@@
 
-  \subsection*{In vitro validation}
-    To demonstrate empirically the predictive capabilities of utilizing AGEAS extraction result, we further investigated the extraction result of $CCl_4$ induced liver fibrosis study setting scenario of identifying theraputic targets inhibiting pathological fibrogenic process in liver.
-    Through analyzing extracted TF regulons, we further confirmed Mef2c's role as key targetome noticing direct regulational relationships with HSC activation marker Acta2\cite{acta2_hsc_act} and fibrotic collagen Col1a1 (Figure \ref{regulons_figs}d).
-    Moreover, since only Lhx2 has all related GRPs mainly being functional in HSC (Figure \ref{regulons_figs}a) and significantly differential expression in HSC (Figure \ref{result_figs}d), we decided to proceed manipulation of Lhx2 expression.
-    Previous study already proved knockdown of Lhx2 promotes liver fibrosis in mice.\cite{lhx2_fibro}
-    Thus, we suppose overexpression of Lhx2 could assist to maintain quiescent of HSCs through Jun/Jund-Mef2c dependent pathways.
+  % \subsection*{In vitro validation}
+  %   To demonstrate empirically the predictive capabilities of utilizing AGEAS extraction result, we further investigated the extraction result of $CCl_4$ induced liver fibrosis study setting scenario of identifying theraputic targets inhibiting pathological fibrogenic process in liver.
+  %   Through analyzing extracted TF regulons, we further confirmed Mef2c's role as key targetome noticing direct regulational relationships with HSC activation marker Acta2\cite{acta2_hsc_act} and fibrotic collagen Col1a1 (Figure \ref{regulons_figs}d).
+  %   Moreover, since only Lhx2 has all related GRPs mainly being functional in HSC (Figure \ref{regulons_figs}a) and significantly differential expression in HSC (Figure \ref{result_figs}d), we decided to proceed manipulation of Lhx2 expression.
+  %   Previous study already proved knockdown of Lhx2 promotes liver fibrosis in mice.\cite{lhx2_fibro}
+  %   Thus, we suppose overexpression of Lhx2 could assist to maintain quiescent of HSCs through Jun/Jund-Mef2c dependent pathways.
+  %
+  %   To verify our hypothesis, we firstly validated the association between Lhx2 and HSC activation with $in$ $vitro$ experiments.
+  %   In mice primary HSC (mHSC) and human HSC cell lines (LX2), we detected the expression of Lhx2/LHX2 with the activation of HSC.
+  %   The results showed that the expression of Lhx2 was significantly decreased with the activation of HSC (Figure \ref{hsc_activation_mRNA}), consistent with our previous analysis result.
+  %   To further clarify the role of LHX2 in human cell, we knocked down LHX2 by small interfering RNA (siRNA) in LX2 cells.
+  %   The results showed that knockdown of LHX2 significantly promoted the expression of fibrosis-related genes in Figure \ref{hsc_activation_mRNA}d, compatible with previous knowledge in mice.
+  %
+  %   Subsequently, we overexpressed Lhx2/LHX2 in mHSCs and LX2 cells.
+  %   The results showed that overexpression of LHX2 directly affected the cell morphology of human HSCs and significantly inhibited the expression of fibrogenic genes (Figure \ref{LHX2_LX2_morphology} and \ref{LHX2_OEs}a).
+  %   In addition, observation in mHSCs further confirmed that Lhx2 could inhibit the expression of fibrosis-related genes (Figure \ref{LHX2_OEs}b).
+  %   In order to comprehensively understand the gene expression profile of HSC regulated by LHX2, RNA-seq results showed that the differential genes were mainly related to extracellular matrix structure and assembly (Figure \ref{LHX2_GO}), which was consistent with fibrosis-related phenotype.
+  %
+  %   Thus, systematic and comprehensive $in$ $vitro$ verification showed that Lhx2/LHX2 is indeed capable to regulate fibrogenic gene expressions and inhibit HSC activation as we concluded from AGEAS extraction output.
+  %   However, the preliminarily identified regulatory pathways for Lhx2 to inhibit HSC activation is yet to be addressed.
+  %   % In vivo experiment will take longer time...
 
-    To verify our hypothesis, we firstly validated the association between Lhx2 and HSC activation with $in$ $vitro$ experiments.
-    In mice primary HSC (mHSC) and human HSC cell lines (LX2), we detected the expression of Lhx2/LHX2 with the activation of HSC.
-    The results showed that the expression of Lhx2 was significantly decreased with the activation of HSC (Figure \ref{hsc_activation_mRNA}), consistent with our previous analysis result.
-    To further clarify the role of LHX2 in human cell, we knocked down LHX2 by small interfering RNA (siRNA) in LX2 cells.
-    The results showed that knockdown of LHX2 significantly promoted the expression of fibrosis-related genes in Figure \ref{hsc_activation_mRNA}d, compatible with previous knowledge in mice.
-
-    Subsequently, we overexpressed Lhx2/LHX2 in mHSCs and LX2 cells.
-    The results showed that overexpression of LHX2 directly affected the cell morphology of human HSCs and significantly inhibited the expression of fibrogenic genes (Figure \ref{LHX2_LX2_morphology} and \ref{LHX2_OEs}a).
-    In addition, observation in mHSCs further confirmed that Lhx2 could inhibit the expression of fibrosis-related genes (Figure \ref{LHX2_OEs}b).
-    In order to comprehensively understand the gene expression profile of HSC regulated by LHX2, RNA-seq results showed that the differential genes were mainly related to extracellular matrix structure and assembly (Figure \ref{LHX2_GO}), which was consistent with fibrosis-related phenotype.
-
-    Thus, systematic and comprehensive $in$ $vitro$ verification showed that Lhx2/LHX2 is indeed capable to regulate fibrogenic gene expressions and inhibit HSC activation as we concluded from AGEAS extraction output.
-    However, the preliminarily identified regulatory pathways for Lhx2 to inhibit HSC activation is yet to be addressed.
-    % In vivo experiment will take longer time...
-
-  \subsection*{Conclusion}
+\section*{Conclusion}
   With result achieved so far, AGEAS shows robustness in extracting key regulatory elements for several biological researches.
@@
   Furthermore, the direct extractions of ISL1 in DAN differentiation and Jund in HSC activation as regulatory source in top amount of important GRPs can demonstrate that AGEAS is not focusing solely on TF regulon sizes in reconstructed meta-GRN nor expression differences between sample classes.
-    Also, $in$ $vitro$ experiments indicate great potential in AGEAS to promote method development in phenotypic manipulation.
+  % Also, $in$ $vitro$ experiments indicate great potential in AGEAS to promote method development in phenotypic manipulation.
   % While TF regulons reconstructed with all extracted GRPs are having sizes proportional to meta-GRN... GO enrichment?
@@
 
-  Although Lhx2 extracted by AGEAS-based analysis indeed shows capability to inhibit HSC activation during liver fibrosis as predicted, the corresponding inference of functional pathways still need to be proved.
-  Furthermore, $in$ $vivo$ experiments are also necessary to evaluate functionality of Lhx2 and associated pathways for higher fidelity.
+  % Although Lhx2 extracted by AGEAS-based analysis indeed shows capability to inhibit HSC activation during liver fibrosis as predicted, the corresponding inference of functional pathways still need to be proved.
+  % Furthermore, $in$ $vivo$ experiments are also necessary to evaluate functionality of Lhx2 and associated pathways for higher fidelity.
 
@@
 
-\begin{figure}
+% \begin{figure}
+%
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/lhx2_class.png}
+%     \caption{Lhx2 regulon}
+%   \end{subfigure}
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/junb_class.png}
+%     \caption{Junb regulon}
+%   \end{subfigure}
+%
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/nfib_class.png}
+%     \caption{Nfib regulon}
+%   \end{subfigure}
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/mef2c_class.png}
+%     \caption{Mef2c regulon}
+%   \end{subfigure}
+%
+%   \caption{
+%     Regulons of extracted top TFs interacting with both Jund and Jun and Mef2c.
+%     Class 1 stands for HSC; class 2 stands for PF.
+%   }
+%   \label{regulons_figs}
+% \end{figure}
 
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/lhx2_class.png}
-    \caption{Lhx2 regulon}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/junb_class.png}
-    \caption{Junb regulon}
-  \end{subfigure}
-
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/nfib_class.png}
-    \caption{Nfib regulon}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/mef2c_class.png}
-    \caption{Mef2c regulon}
-  \end{subfigure}
-
-  \caption{
-    Regulons of extracted top TFs interacting with both Jund and Jun and Mef2c.
-    Class 1 stands for HSC; class 2 stands for PF.
-  }
-  \label{regulons_figs}
-\end{figure}
-
-\begin{figure}
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_a.png}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_b.png}
-    \caption{}
-  \end{subfigure}
-
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_c.png}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_h.png}
-    \caption{}
-  \end{subfigure}
-  \caption{
-    Relative mRNA expression levels during HSC activation.
-    \textbf{\emph{(a)}} Fibrosis-related gene (Col1a1, Col3a1, Acta2) expression in mHSCs were increased with the extension of culture time, indicating HSC activation.
-    n = 3.
-    \textbf{\emph{(b)}} With the activation of mHSC, expression of Lhx2 decreased gradually.
-    n = 3.
-    \textbf{\emph{(c)}} In human HSC cell line LX2, TGF-$\beta$ can remarkably activate HSC and promote expressions of fibrosis-related genes. % Reference ?
-    Meanwhile, the expression of LHX2 decreased with the activation of HSC.
-    \textbf{\emph{(d)}} Knockdown of LHX2 by siRNA (si-LHX2) significantly increased the expression of fibrosis-related genes in LX2 cells compared with negative control (si-NC).
-    n = 4.
-  }
-  \label{hsc_activation_mRNA}
-\end{figure}
-
-\begin{figure}
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_d_lx2_wt.png}
-    \caption{LX2-WT}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_d_lx2_pcdh_oe.png}
-    \caption{LX2-PCDH-OE}
-  \end{subfigure}
-
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_d_lx2_lhx2_oe.png}
-    \caption{LX2-LHX2-OE}
-  \end{subfigure}
-  \caption{
-    Overexpression of LHX2 significantly altered cell morphology in LX2 cell lines.
-    \textbf{\emph{(a)}} LX2 wild type.
-    \textbf{\emph{(b)}} LX2 overexpressing negative control vector.
-    \textbf{\emph{(c)}} LX2 overexpressing LHX2.
-  }
-  \label{LHX2_LX2_morphology}
-\end{figure}
-
-\begin{figure}
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_e.png}
-    \caption{LX2}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_f.png}
-    \caption{mHSC}
-  \end{subfigure}
-
-  \caption{
-    Overexpression of Lhx2/LHX2 significantly decreased the expression of fibrosis-related genes.
-    \textbf{\emph{(a)}} in LX2 cells. n = 3.
-    \textbf{\emph{(b)}} in mHSCs. n = 3.
-  }
-  \label{LHX2_OEs}
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=0.8\linewidth]{../images/wet_lab/tao_g.png}
-  \caption{
-    RNA-seq results of LHX2 overexpressed cells showed that gene ontology (GO) enrichment of differentially expressed genes was mainly concentrated in extracellular matrix related genes.
-  }
-  \label{LHX2_GO}
-\end{figure}
+% \begin{figure}
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_a.png}
+%     \caption{}
+%   \end{subfigure}
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_b.png}
+%     \caption{}
+%   \end{subfigure}
+%
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_c.png}
+%     \caption{}
+%   \end{subfigure}
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_h.png}
+%     \caption{}
+%   \end{subfigure}
+%   \caption{
+%     Relative mRNA expression levels during HSC activation.
+%     \textbf{\emph{(a)}} Fibrosis-related gene (Col1a1, Col3a1, Acta2) expression in mHSCs were increased with the extension of culture time, indicating HSC activation.
+%     n = 3.
+%     \textbf{\emph{(b)}} With the activation of mHSC, expression of Lhx2 decreased gradually.
+%     n = 3.
+%     \textbf{\emph{(c)}} In human HSC cell line LX2, TGF-$\beta$ can remarkably activate HSC and promote expressions of fibrosis-related genes. % Reference ?
+%     Meanwhile, the expression of LHX2 decreased with the activation of HSC.
+%     \textbf{\emph{(d)}} Knockdown of LHX2 by siRNA (si-LHX2) significantly increased the expression of fibrosis-related genes in LX2 cells compared with negative control (si-NC).
+%     n = 4.
+%   }
+%   \label{hsc_activation_mRNA}
+% \end{figure}
+%
+% \begin{figure}
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_d_lx2_wt.png}
+%     \caption{LX2-WT}
+%   \end{subfigure}
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_d_lx2_pcdh_oe.png}
+%     \caption{LX2-PCDH-OE}
+%   \end{subfigure}
+%
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_d_lx2_lhx2_oe.png}
+%     \caption{LX2-LHX2-OE}
+%   \end{subfigure}
+%   \caption{
+%     Overexpression of LHX2 significantly altered cell morphology in LX2 cell lines.
+%     \textbf{\emph{(a)}} LX2 wild type.
+%     \textbf{\emph{(b)}} LX2 overexpressing negative control vector.
+%     \textbf{\emph{(c)}} LX2 overexpressing LHX2.
+%   }
+%   \label{LHX2_LX2_morphology}
+% \end{figure}
+%
+% \begin{figure}
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_e.png}
+%     \caption{LX2}
+%   \end{subfigure}
+%   \begin{subfigure}{0.49\linewidth}
+%     \centering
+%     \includegraphics[width=\linewidth, keepaspectratio,]{../images/wet_lab/tao_f.png}
+%     \caption{mHSC}
+%   \end{subfigure}
+%
+%   \caption{
+%     Overexpression of Lhx2/LHX2 significantly decreased the expression of fibrosis-related genes.
+%     \textbf{\emph{(a)}} in LX2 cells. n = 3.
+%     \textbf{\emph{(b)}} in mHSCs. n = 3.
+%   }
+%   \label{LHX2_OEs}
+% \end{figure}
+%
+% \begin{figure}[ht]
+%   \centering
+%   \includegraphics[width=0.8\linewidth]{../images/wet_lab/tao_g.png}
+%   \caption{
+%     RNA-seq results of LHX2 overexpressed cells showed that gene ontology (GO) enrichment of differentially expressed genes was mainly concentrated in extracellular matrix related genes.
+%   }
+%   \label{LHX2_GO}
+% \end{figure}
 

### 2022-10-12 setup.py

@@ -5,7 +5,7 @@ with open("README.md", "r", encoding="utf-8") as fh:
 
 setuptools.setup(
     name = "Ageas",
-    version = "v0.0.1-alpha7",
+    version = "v0.0.1-alpha8",
     author = "nkmtmsys and JackSSK",
     author_email = "gyu17@alumni.jh.edu",
     description = "AutoML-based Genetic regulatory Element extrAction System",

### 2022-10-12 docs/manuscript/main.tex
v0.0.1a9
Editing stuffs

@@
   As rapid progress in sequencing technology since last decade, numerous mechanisms underlying cell functions and developmental processes have been revealed as complex regulations of gene expressions.
-  While single-cell RNA sequencing (scRNA-seq) made high-resolution transcriptomic view increasingly accessible, precise identification of gene regulatory network (GRN) describing cell types and cell states became achievable.
-  However, extracting key regulatory elements, including gene regulatory pathways (GRPs), transcription factors (TFs), and targetomes, accurately and completely reflecting functionality changes in biological phenomena remains challenging.
-  Herein, we describe AGEAS, an semi-supervised automated machine learning (AutoML) based genetic regulatory element extraction system that assesses importances of GRPs in resulting biological phenomena, such as cell type differentiation, physiological and pathological development, and reconstruct GRNs with extracted important GRPs for comprehensive inference.
-  With several case studies in divergent research areas, we show that AGEAS can indeed extract informative regulatory elements and reconstruct networks referring biological phenomena of interest.
+  Since single-cell RNA sequencing (scRNA-seq) made high-resolution transcriptomic view increasingly accessible, precise identification of gene regulatory network (GRN) describing cell types and cell states became achievable.
+  However, extracting key regulatory elements, including gene regulatory pathways (GRPs), transcription factors (TFs), and targetomes, that accurately and completely reflects functionality changes in biological phenomena remains challenging.
+  Herein, we describe AGEAS, an semi-supervised automated machine learning (AutoML) based genetic regulatory element extraction system that assesses importances of GRPs in resulting biological phenomena, such as cell type differentiation, physiological and pathological development, and reconstructs GRNs with extracted important GRPs for comprehensive inference.
+  With several case studies in divergent research areas, we show that AGEAS can indeed extract informative regulatory elements and reconstruct networks to indicate regulatory changes in biological phenomena of interest.
   % Furthermore, we validated applicability of AGEAS with empirical evidence that LIM homeobox 2 (Lhx2), key quiescent hepatic stellate cell (HSC) factor AGEAS extracted through analyzing chronic carbon tetrachloride ($CCl_4$) induced liver fibrosis data, can indeed halt HSC activation to prevent fibrogenic process.
@@
 \cite{Scenic, pySCENIC}
-  Even though limited computational methods are capable to completely and precisly extract key genetic regulatory elements in biological process of interest, Mogrify\cite{mogrify_2016} and CellNet\cite{cellnet_2014} have demonstrated GRN based methods can help to analysis cell type differentiation and implement cell reprogramming.
-  However, either method may require large scale of additional background data to be applicable in other studies such as analyzing physiological or pathological development of selected cell type.
-  The scREMOTE \cite{scREMOTE} published in 2022 shows great potential as generalized regulatory element extraction method since limited background data is required with sequencing data representing sample classes.
+  Even though limited computational methods are capable of completely and precisly extracting key genetic regulatory elements in biological process of interest, Mogrify\cite{mogrify_2016} and CellNet\cite{cellnet_2014} have demonstrated GRN based methods can help to analyze cell type differentiation and to implement cell reprogramming.
+  However, both methods may require large scale of additional background data to be applicable in other studies such as analyzing physiological or pathological development of selected cell type.
+  The scREMOTE \cite{scREMOTE} published in 2022 is a potential method to extract generalized regulatory elements since limited background data is required with sequencing data representing sample classes.
   But prior knowledge on key TFs and marker genes is still indispensable.

### 2022-10-12 docs/manuscript/main.tex
v0.0.1a9
manuscript stuffs

@@
   The scREMOTE \cite{scREMOTE} published in 2022 is a potential method to extract generalized regulatory elements since limited background data is required with sequencing data representing sample classes.
-  But prior knowledge on key TFs and marker genes is still indispensable.
-  Indeed, a regulation trajectory of DEGs or regulons showing significant activity difference after GRN reconstruction would be able to reveal the developmental pathways as generalized approach, but numerous noisy signals are expected due to general gene regulatory nature of TFs.
-  Therefore, here we present AGEAS with feasibility in extracting key regulatory elements for biological phenomena of interest even with scarce prior knowledge and potentially promoting further discoveries.
+  But prior knowledge on key TFs and marker genes is indispensable.
+  A regulation trajectory of DEGs or regulons showing significant activity difference after GRN reconstruction would be able to reveal the developmental pathways as generalized approach.
+  Due to general gene regulatory nature of TFs, numerous noisy signals are expected.
+  Therefore, here we present AGEAS, an algorithm with feasibility in extracting key regulatory elements for biological phenomena of interest and can potentially promote further discoveries, even with scarce prior knowledge.
 
   Several reasons motivated us to develop semi-supervised AutoML based method.
-  Firstly, accurate labeling of regulatory elements' relativeness in biological phenomena would require extensive prior knowledge in according research area that may hardly available.
-  While unsupervised clustering can potentially extract factos playing important roles, this approach would result in lossing comprehensiveness through focusing on specific aspects with regulatory elements showing similar patterns.
-  As a result, we chose to apply biological phenomena reflecting sample classes, such as cell types and cell states which should be easily retrievable, as labels for classification models to predict with masked GRN as input and then interpret success predictions to extract key regulatory elements.
-  Secondly, developing a generalized classificaton model in differentiating GRNs is still hard to guarantee comprehensiveness considering that capturing few significant differences would be sufficient for the model to reach outstanding accuracy.
-  Hence, a extraction system with multiple independent classification models implemented with various algorithms should be helpful to recover from potential comprehensiveness loss.
-  Thirdly, the process of interpreting all success prediction made by every classificaion model and integrating corresponding interpretation results is expected to be extremely computational expensive.
-  Thus, applying AutoML-based model and feature selection procedure that can effectively decreas interpretation cost would be necessary to increase feasibility of the method.
+  Firstly, accurate labeling of regulatory elements' relatedness in biological phenomena would require extensive prior knowledge may be unavailable.
+  While unsupervised clustering can potentially extract factors playing important roles, this approach may focus on specific aspects with regulatory elements showing similar patterns and result in losing comprehensiveness.
+  As a result, we chose to apply biological phenomena associating sample classes, such as cell types and cell states which should be easily retrievable, as labels for classification models to predict with masked GRN as input and then interpret success predictions to extract key regulatory elements.
+  Secondly, it is also hard to guarantee comprehensiveness when developing a generalized classification model in differentiating GRNs, considering that capturing few significant differences would be sufficient for the model to reach outstanding accuracy.
+  Hence, an extraction system with multiple independent classification models implemented with various algorithms should be helpful to recover from potential comprehensiveness loss.
+  Thirdly, the process of interpreting all success prediction made by every classification model and integrating corresponding interpretation results may be computational expensive.
+  Thus, applying an AutoML-based model and feature selection procedure that can effectively decrease interpretation cost would be necessary to increase feasibility of the method.
 
-  To evaluate performance of AGEAS, we primarily applied AGEAS in studying somatic cell reprogramming process and then further addressed performance in analyzing 3 other biological process in cell subtype differentiation, physiological and pathological development.
+  To evaluate the performance of AGEAS, we primarily applied it on studying somatic cell reprogramming process and further addressed performance in analyzing 3 other biological processes in cell subtype differentiation, physiological and pathological development.
   % Later, we also addressed the applicability of AGEAS extraction result in guiding further studies about biological phenomena with $in$ $vitro$ experiments in determining Lhx2, key TF regulating liver fibrosis extracted with AGEAS, can indeed inhibit HSC activation.
@@
   \label{method}
-  The basic principle of AGEAS is to find key regulatory elements associated with biological phenomena of interest through analyzing how well-performing classification models distinguish GRNs of sample with the phenomena from GRNs of samples without.
+  The basic principle of AGEAS is to find key regulatory elements associated with biological phenomena of interest through analyzing how well-performing classification models distinguish GRNs of sample with the phenomena from those without.
   To reconstruct sufficient GRNs for each class, RNA-seq based expression data is segmented into subsets while each one is analogized as a pseudo-sample having discrete expression data.
-  The pseudo-sample GRNs (psGRNs) are reconstructed accordingly; thus, classification models can be trained, evaluated, and interpreted having GRPs as input factors.
-  With heavily weighted GRPs and correspond genes repeatedly obtained from interpretations of success sample class predictions, GRNs could be formed and potentially playing important role in differentiating the studying sample classes.
-  The overall workflow can be summarized as Figure \ref{workflow}.
-  By default setting, four seperate extractor units in workflow run parallelly after data preprocessing part in order to increase output stability considering stochastic nature of AGEAS, and all extracted regulatory elements are used to form GRNs later combined into one atlas.
-  Following sections describe each step of AGEAS in more depth.
+  The pseudo-sample GRNs (psGRNs) are reconstructed accordingly; thus, classification models can be trained, evaluated, and interpreted with GRPs as input factors.
+  With heavily weighted GRPs and corresponding genes repeatedly obtained from interpretations of successful sample class predictions, GRNs could be formed and potentially play an important role in differentiating the studying sample classes.
+  The overall workflow can be summarized in Figure \ref{workflow}.
+  By default, four separate extractor units in workflow run in parallel after data preprocessing part in order to increase output stability considering the stochastic nature of AGEAS, and all extracted regulatory elements are used to form GRNs, which will later be combined into one atlas.
+  The following sections describe each step of AGEAS in more depth.
   % \begin{itemize}
@@
     \label{step1}
-    The main purpose of this step is to build pseudo-samples and reconstruct corresponding pseudo-sample GRNs (psGRNs).
-    For each sample class, gene expression matrices (GEMs) labeled with same class label are concatenated as one comprehensive expression matrix.
-    With comprehensive GEMs, a meta-level GRN (meta-GRN) is reconstructed in advance of psGRNs to provide generic guidance on reconstruction.
-    In general, the workflow of this step can be represented as Figure \ref{data_preprocess}.
+    The main purpose of this step is to build pseudo-samples and to reconstruct corresponding pseudo-sample GRNs (psGRNs).
+    For each sample class, gene expression matrices (GEMs) with the same class label are concatenated as one comprehensive expression matrix.
+    With comprehensive GEMs, a meta-level GRN (meta-GRN) is reconstructed before psGRNs to provide generic guidance on reconstruction.
+    In general, the workflow of this step can be summarized in Figure \ref{data_preprocess}.
 
@@
       Firstly, genes included in the comprehensive GEMs are assessed and determined whether having potential to form informative GRPs with other genes.
-      Commonly, differentially expressed genes (DEGs) would be considered as important factors of studying  phenomena.
-      Here we apply the Mann-Whitney U rank test (MWW) implemented by \emph{SciPy}\cite{2020SciPy-NMeth} to exclude genes having indistinguishable expression level distribution across GEMs of different classes.
+      Commonly, DEGs are considered as important factors of studying phenomena.
+      Here we apply the Mann-Whitney U rank test (MWW) implemented by \emph{SciPy}\cite{2020SciPy-NMeth} to exclude genes with indistinguishable expression level distribution across GEMs of different classes.
       The p-value for rejecting null hypothesis, that expression profile underlying class 1 samples is the same as the expression profile underlying class 2 samples, is set to 0.05 by default.
-      Furthermore, a $\log_2$ fold change (log2FC) filter is also implemented in AGEAS.
-      However, enabling the log2FC filter is not encouraged considering upstream TFs indirectly regulating key genes associated with phenomena of interest may not always have significant differential expression profiles.
-      The lof2FC filter shall mostly be used in order to decrease meta-GRN's GRP total amount in a compromising position caused by limited computational resources.
-      After differential expression based filters, a standard deviation ($\sigma$) filter is applied to exclude genes either having low expression level or merely affected by dynamic expression status of other genes.
+      Furthermore, a $\log_2$ fold change (log2FC) filter is implemented in AGEAS.
+      However, enabling the log2FC filter is not encouraged, considering that upstream TFs indirectly regulate key genes associated with phenomena of interest may not be significantly differential expressed.
+      The lof2FC filter shall mostly be used to decrease meta-GRN's total degree in a compromising position caused by limited computational resources.
+      After differential expression based filters, a standard deviation ($\sigma$) filter is applied to exclude genes with low expression level or merely affected by dynamic expression status of other genes.
       By default, the $\sigma$ threshold is set to 1.0, the lowest expression level in raw gene count matrix gained from RNA-seq data.
-      The threshold value should be adjusted corresponding to prior knowledge of input GEMs, for example of what normalization method was applied to the GEMs.
+      The threshold value should be adjusted based on prior knowledge of input GEMs, for example, the normalization method applied to the GEMs.
 
-      With candidate genes passed filters above, some gene pairs are formed and assessed potential of representing GRPs.
-      To reduce overall computational complexity, a gene pair shall be formed with at least one TF which could be the regulatory source of GRP.
-      If not further specified, TF list will be retrieved from integrated \emph{TRANSFAC}\cite{transfac} datasets according to the provided species information.
+      With candidate genes passing filters above, some gene pairs are formed and evaluated by the potential of representing GRPs.
+      To reduce overall computational complexity, a gene pair shall be formed with at least one TF, which could be the regulatory source of GRP.
+      If not further specified, a TF list will be retrieved from integrated \emph{TRANSFAC}\cite{transfac} dataset according to the provided species information.
       Utilizing genetic interaction database like \emph{GTRD}\cite{gkaa1057} and \emph{BioGRID}\cite{biogrid}, AGEAS checks whether the binding ability of gene pair is confirmed or not.
-      By default, if TF being recorded to have binding site within target gene's promoter range (-1000 to +100) by Chromatin Immunoprecipitation Sequencing (ChIP-seq) dataset retrieved from \emph{GTRD}\cite{gkaa1057}, the potential GRP gene pair will be passed to expression correlation assessment.
+      By default, if the TF recorded has at least one binding site within target gene's promoter range (-1000 to +100) by Chromatin Immunoprecipitation Sequencing (ChIP-seq) dataset retrieved from \emph{GTRD}\cite{gkaa1057}, the potential GRP gene pair will be passed to expression correlation assessment.
       For TFs not covered by interaction database, \emph{GRNBoost2}\cite{grnboost2}-like algorithm is initiated to predict potential regulatory target genes.
@@
       \noindent Here $GA()$ denotes \emph{GRNBoost2}\cite{grnboost2}-like algorithm;
-      $M_1$ is concatenated class 1 samples GEM with genes passed filters;
-      $M_2$ is concatenated class 2 samples GEM with genes passed filters;
-      $t$ is the TF having largest amount of recorded interaction in dataset;
-      $g$ is total amount of unique genes in all samples passed filters.
+      $M_1$ denotes concatenated class 1 samples GEM with genes passed filters;
+      $M_2$ denotes concatenated class 2 samples GEM with genes passed filters;
+      $t$ denotes the TF having largest amount of recorded interaction in dataset;
+      $g$ denotes total amount of unique genes in all samples passed filters.
 
-      After potential GRP gene pairs obtained, a expression correlation filter is used to exclude gene pairs having low covariance which implies weak relationship.
-      To assess expression correlation, AGEAS applies Pearson's Correlation coefficient\cite{pcc_2012} (PCC) whihc is one of the widely adopted methods.\cite{cid_2019}
-      With default setting, gene pairs can reach absolute correlation coefficient of 0.2 while keeping correspond p-value lower than 0.05 are included in meta-GRN as validated GRP.
+      After potential GRP gene pairs are obtained, an expression correlation filter is used to exclude gene pairs with low covariance.
+      To assess expression correlation, AGEAS applies Pearson's Correlation coefficient\cite{pcc_2012} (PCC), one of the widely adopted methods.\cite{cid_2019}
+      With default setting, gene pairs can reach absolute correlation coefficient of 0.2 and p-value lower than 0.05 are included in meta-GRN as validated GRP.
 
@@
     The model selection algorithm requires five inputs
-    (1)$R$, the maximum amount of training resource, equivalent to all avaliable psGRNs
+    (1)$R$, the maximum amount of training resource, equivalent to all available psGRNs
     (2)$C$, the total set of provided classification model configurations
@@
         Classification model algorithms integrated in AGEAS with correspond numbers of hyperparameter and preset model configurations.
-        Categorical hyperparameters and continuous numerical hyperparameters are clarifed beside total number of hyperparameters ($\# \lambda$).
+        Categorical hyperparameters and continuous numerical hyperparameters are clarified beside total number of hyperparameters ($\# \lambda$).
         Conditional hyperparameters which are required for selected other hyperparameters are shown in brackets if there is any.
@@
     However, few uninformative GRPs in training psGRNs merely relied by any model to make classification could be pruned in advance for saving computational power.
-    Furthermore, to prevent classification models focusing on a small group of GRPs regardless of training psGRNs, GRPs draw excessive attention shall also be seperated from psGRNs to improve extraction comprehensiveness.
-    Thus, in this step, AGEAS iteratively train classificaion models with dynamic $\alpha_{max}$ portion of psGRNs and obtain feature importance scores as described in \hyperref[features_importances]{subsection} below to find GRPs either scored extremely high or considerably low.
+    Furthermore, to prevent classification models focusing on a small group of GRPs regardless of training psGRNs, GRPs draw excessive attention shall also be separated from psGRNs to improve extraction comprehensiveness.
+    Thus, in this step, AGEAS iteratively train classification models with dynamic $\alpha_{max}$ portion of psGRNs and obtain feature importance scores as described in \hyperref[features_importances]{subsection} below to find GRPs either scored extremely high or considerably low.
 
     More specifically, at each iteration, GRPs having z-scores ranked as bottom $b$ portion (default set as 0.1) are discarded.
-    Also, an $i$-th ranked GRP will be seperated from psGRNs and passed to \hyperref[step5]{Step 5} directly if having z-score fulfilling the condition:
+    Also, an $i$-th ranked GRP will be separated from psGRNs and passed to \hyperref[step5]{Step 5} directly if having z-score fulfilling the condition:
 
@@
     \noindent The $Z_{score}^{thread}$ is input z-score threshold (default set as 3.0), and $IQR$ stands for interquartile range calculated by the beginning of each iteration.\
-    With this criterion, AGEAS ensures only GRPs draw significantly more attention shall be selected by each iteration despite the data distribution of varying z-score scalled importance values.
+    With this criterion, AGEAS ensures only GRPs draw significantly more attention shall be selected by each iteration despite the data distribution of varying z-score scaled importance values.
 
@@
       Specific Shapley value calculation or approximating methods are implemented with \emph{SHAP}\cite{lundberg2017unified} and applied to different algorithms as shown in Table \ref{shap}.
-      Regarding the standard differences between feature importance estimating methods, we utilize \emph{softmax} function to normalize feature importances and define the normalized importance calculation function as:
+      Regarding the standard differences between feature importance estimating methods, we utilize \emph{softmax} function to normalize feature importance and define the normalized importance calculation function as:
 
@@
       \noindent Here $X$ is total set of all features, and $F(x)$ is the importance estimating method of individual classification model being interpreted.\
-      If the feature importances can be approached with internalized method $f(x)$, $F(x)$ is set as:
+      If the feature importance can be approached with internalized method $f(x)$, $F(x)$ is set as:
 
@@
 
-      \noindent After all selected classification models $M$ have been interpreted, we can intergrate the feature importances matrices weighted with corresponding models' $L_{CE}$ to one matrix $A$ as:\
+      \noindent After all selected classification models $M$ have been interpreted, we can integrate the feature importance matrices weighted with corresponding models' $L_{CE}$ to one matrix $A$ as:\
 
@@
           Linear SVM implemented with \emph{scikit-learn}\cite{scikit-learn} can have the importance estimated with feature coefficient or using Linear Explainer.
-          However, for SVM with kernel function, the feature coefficient estimation would be inappropriate, and feature importances should be approximated with Kernel Explainer.
+          However, for SVM with kernel function, the feature coefficient estimation would be inappropriate, and feature importance should be approximated with Kernel Explainer.
         }
@@
     \label{step5}
-    Analoging every GRP previously extracted or seperated with high z-score in \hyperref[step3]{Step 3} as a directional edge connecting two gene vertices, equivalent to a TF and a gene, in graph theory, AGEAS attempts to reconstruct a network graph representing regulatory differences between query sample classes.
+    Analoging every GRP previously extracted or separated with high z-score in \hyperref[step3]{Step 3} as a directional edge connecting two gene vertices, equivalent to a TF and a gene, in graph theory, AGEAS attempts to reconstruct a network graph representing regulatory differences between query sample classes.
     Since there is no guarantee on all GRP edges can be connected, some regulatory relationships between gene vertices could be missed.
@@
   Thus, we can infer Pou5f1 is key regulatory element associated with ESC identity.
-  Extensive studies already addressed Pou5f1's important role in maintaing pluripotency. \cite{niwa_2007, oct4_1, oct4_2}
-  Moreover, to implement cell reprogramming to iPSC, Nanog and Sox2 are also noteworthy since they are closely interacting with Pou5f1 in extracted network, having high regulatory degrees, and differentially expressed in ESC.
+  Extensive studies already addressed Pou5f1's important role in pluripotency maintenance. \cite{niwa_2007, oct4_1, oct4_2}
+  Moreover, to implement cell reprogramming to iPSC, Nanog and Sox2 are also noteworthy since they are closely interacting with Pou5f1 in extracted network, having high regulatory degrees, and differently expressed in ESC.
   Multiple previous studies confirmed that all of Oct4, Nanog, and Sox2 are playing important role to induce cell conversion from somatic cell to iPSC.
@@
 
-        Through substratification of all extracted GRPs, we only found HDAC2 and RBPJ as potential upstream regulatory elements of all ISL1, ELF3, and PBX3.
+        Through stratification of all extracted GRPs, we only found HDAC2 and RBPJ as potential upstream regulatory elements of all ISL1, ELF3, and PBX3.
         Few reports demonstrated HDAC2 is associated with neurogenesis of radial glial cells. \cite{hdac2_dan_1, hdac2_dan_2}
@@
 
-        Based on extracted important GRPs, we identified Mef2c, Jun, and Jund as potential representitives of key regulatory elements in HSC activation (Figure \ref{result_figs}d).
+        Based on extracted important GRPs, we identified Mef2c, Jun, and Jund as potential representatives of key regulatory elements in HSC activation (Figure \ref{result_figs}d).
         As TF extracted with most important GRPs, Mef2c has been well-documented as key regulator in HSC activation. \cite{mef2c_1, mef2c_2, mef2c_3}
@@
         While no regulatory relationship between Jund and Jun determined, 3 extracted top TFs (Lhx2, Nfib, Junb) can potentially influence expressions of both Jund and Jun.
-        Since Junb is also functional component of AP1, we infer it associated with HSC activaion in a similar manner.
+        Since Junb is also functional component of AP1, we infer it associated with HSC activation in a similar manner.
         Furthermore, Lhx2 was found indispensable for quiescent HSCs. \cite{lhx2_fibro, Lhx2_hsc_1}

### 2022-10-13 docs/manuscript/main.tex
v0.0.1a9
Almost done with language

@@
     \subsubsection*{Reconstruct psGRNs}
-      The comprehensive GEMs is divided into few sample subsets with sliding window algorithm (SWA) to build pseudo-samples.
-      With SWA, we can gain GEM of \emph{i-th} pseudo-sample through:
+      The comprehensive GEMs are divided into sample subsets, and sliding window algorithm (SWA) is used to build pseudo-samples.
+      With SWA, we can gain GEMs of \emph{i-th} pseudo-sample through:
 
@@
 
-      \noindent Here $l$ is number of samples in a comprehensive GEM which can be expressed as $\left\{{x_j}_{j = 0}^{l}\right\}$; $k$ denotes window size; $p$ denotes padding stride.
+      \noindent Here $l$ denotes number of samples in a comprehensive GEM which can be expressed as $\left\{{x_j}_{j = 0}^{l}\right\}$; $k$ denotes window size; $p$ denotes padding stride.
 
-      If sample amount is considerably low or imbalanced, customized window size and padding stride can be applied to generate sufficient amount of pseudo-samples for later classifier training and assessment processes.
+      If sample amount is considerably low or imbalanced, customized window size and padding stride can be applied to generate sufficient pseudo-samples for later classifier training and assessment processes.
       Utilizing meta-GRN, psGRNs are reconstructed with GEMs of pseudo-sample.
-      Each GRP gene pair in meta-GRN is formed with expression data in pseudo-sample and filtered by same PCC filter in meta-GRN reconstruction process.
+      Each GRP gene pair in meta-GRN is formed with expression data in pseudo-sample and is filtered by the same PCC filter in meta-GRN reconstruction process.
 
-      After all pseudo-samples have been used to reconstruct psGRN, every psGRN can be represented as matrix comprising GRPs' PCC values.
+      After all pseudo-samples have been used to reconstruct psGRN, every psGRN can be represented as a matrix comprised of GRPs' PCC values.
       The order of GRPs in each psGRN is also unified through adding GRPs included in other psGRNs with 0.0 PCC value.
@@
     \label{step2}
-    Since AGEAS is not aiming to develop optimized model architectures for psGRN classification but gain insights from multiple models as divergent as possible, the main goal of this step is to select configurations of models capable to make correct psGRN classifications from provided configuration set.
-    Regarding the fact that computational power is limited resource, portion of less efficient model configurations shall be pruned although interpreting success predictions of more classification models would lead to more comprehensive insight into sample class differences.
-    Therefore, we apply a simple Hyperband\cite{hyperband}-based algorithm \ref{alg:one} which performs grid search for well-performing classification models with varying model training resource and pruning aggressiveness.
+    The primary goal of AGEAS is to gain insights from multiple models as divergent as possible instead of developing optimized classification model for psGRN classification.
+    Thus, this step is designed to select model configurations capable of predicting psGRN's masked sample class label.
+    Considering the limited computational resources, the portion of less efficient model configurations shall be pruned at the cost of potentially losing insight in sample class difference.
+    Therefore, we apply a simple Hyperband\cite{hyperband}-based algorithm \ref{alg:one} which performs a grid search for well-performing classification models with varying model training resources and pruning aggressiveness.
 
@@
     (5)$k_{min}$, the minimum portion of remaining model configurations will be kept by single pruning iteration (default set as 0.5).
-    Furthermore, two functions are also required while need to be defined based on input model configurations:
+    Furthermore, two required functions need to be defined based on input model configurations:
     \begin{itemize}
@@
 
-    \item \textbf{$top\_configs(C, P, k)$}: takes a set of model configurations $C$ with associated evaluation results $P$ and returns configurations having ACC, AUROC score, or $L_{CE}$ reaching top $k$ portion.
+    \item \textbf{$top\_configs(C, P, k)$}: takes a set of model configurations $C$ with associated evaluation results $P$ and returns configurations with ACC, AUROC score, or $L_{CE}$ reaching top $k$ portion.
     \end{itemize}
@@
         \label{models}
-        Classification model algorithms integrated in AGEAS with correspond numbers of hyperparameter and preset model configurations.
+        Classification model algorithms integrated in AGEAS with corresponding numbers of hyperparameter and preset model configurations.
         Categorical hyperparameters and continuous numerical hyperparameters are clarified beside total number of hyperparameters ($\# \lambda$).
-        Conditional hyperparameters which are required for selected other hyperparameters are shown in brackets if there is any.
-        $\#$ Configs indicates total amount of configurations AGEAS applies by default.
+        Conditional hyperparameters required for selected other hyperparameters are shown in brackets.
+        $\#$ Configs indicates the default total number of configurations.
       }
@@
 
-    The general architecture designs of 1D-CNN and Hybrid-CNN are implemented referring to 1D-CNN and 2D-Hybrid-CNN applied in recent cancer type prediction study.\cite{mostavi_chiu_huang_chen_2020}
-    However, taking one convolution layer and adjacent max-pooling layer as a layer set, we implemented both CNN models with flexibilities on number of layer set, which is fixed as 1 in original research.
-    An example of 1D-CNN with 2 convolution layer sets is illustrated in Figure \ref{1dCNN}.
+    The general architecture designs of 1D-CNN and Hybrid-CNN are implemented based on 1D-CNN and 2D-Hybrid-CNN in a recent cancer type prediction study.\cite{mostavi_chiu_huang_chen_2020}
+    However, taking one convolution layer and adjacent max-pooling layer as a layer set, we implemented both CNN models with flexibility on the number of layer set, which is fixed in the original paper.
+    An example of 1D-CNN with two convolution layer sets is illustrated in Figure \ref{1dCNN}.
 
-    For transformer models, considering psGRNs are already be represented by numerical data matrix while GRPs should barely have positional relationships in the matrix, the embedding layer and positional encoding layer designed for input data tokenization in standard architecture \cite{transformer} are replaced with a single linear layer in AGEAS.
+    For transformer models, the embedding layer and positional encoding layer designed for input data tokenization in standard architecture \cite{transformer} are replaced with a single linear layer in AGEAS, considering psGRNs are already represented as numerical data matrix while GRPs should barely have positional relationships in the matrix.
 
@@
     With selected well-performing models, AGEAS already can start repetition of model training and interpretation in \hyperref[step4]{Step 4} to extract key GRPs.
-    However, few uninformative GRPs in training psGRNs merely relied by any model to make classification could be pruned in advance for saving computational power.
-    Furthermore, to prevent classification models focusing on a small group of GRPs regardless of training psGRNs, GRPs draw excessive attention shall also be separated from psGRNs to improve extraction comprehensiveness.
-    Thus, in this step, AGEAS iteratively train classification models with dynamic $\alpha_{max}$ portion of psGRNs and obtain feature importance scores as described in \hyperref[features_importances]{subsection} below to find GRPs either scored extremely high or considerably low.
+    However, the few uninformative GRPs in training psGRNs could be pruned in advance to save computational resource.
+    Furthermore, to prevent classification models from focusing on a small group of GRPs regardless of training psGRNs, GRPs draw excessive attention shall be separated from psGRNs to improve extraction comprehensiveness.
+    Thus, in this step, AGEAS iteratively trains classification models with dynamic $\alpha_{max}$ portion of psGRNs and obtains feature importance scores as described in \hyperref[features_importances]{subsection} below to exclude GRPs either scored considerably high or relatively low.
 
-    More specifically, at each iteration, GRPs having z-scores ranked as bottom $b$ portion (default set as 0.1) are discarded.
-    Also, an $i$-th ranked GRP will be separated from psGRNs and passed to \hyperref[step5]{Step 5} directly if having z-score fulfilling the condition:
+    More specifically, at each iteration, GRPs with z-scores ranked at the bottom $b$ portion (default set as 0.1) are discarded.
+    Also, an $i$-th ranked GRP will be separated from psGRNs and passed to \hyperref[step5]{Step 5} directly if it has a z-score fulfilling the condition:
 
@@
 
-    \noindent The $Z_{score}^{thread}$ is input z-score threshold (default set as 3.0), and $IQR$ stands for interquartile range calculated by the beginning of each iteration.\
-    With this criterion, AGEAS ensures only GRPs draw significantly more attention shall be selected by each iteration despite the data distribution of varying z-score scaled importance values.
+    \noindent The $Z_{score}^{thread}$ denotes input z-score threshold (default set as 3.0), and $IQR$ stands for interquartile range calculated at the beginning of each iteration.\
+    With this criterion, AGEAS ensures only GRPs draw significantly more attention be selected by each iteration, despite different data distribution of z-score scaled importance values.
 
-    By default, AGEAS iterates this feature selection step for 3 times.
+    By default, AGEAS iterates this feature selection step for three times.
 
@@
       \label{features_importances}
-      AGEAS applies concept of The Shapley value\cite{roth_1988} for estimating importance of each input feature, equivalent to GRP of input psGRN, in any kind of classification model while making predictions.
-      Specific Shapley value calculation or approximating methods are implemented with \emph{SHAP}\cite{lundberg2017unified} and applied to different algorithms as shown in Table \ref{shap}.
-      Regarding the standard differences between feature importance estimating methods, we utilize \emph{softmax} function to normalize feature importance and define the normalized importance calculation function as:
+      AGEAS applies concept of The Shapley value\cite{roth_1988} for estimating the importance of each input feature, equivalent to GRP of input psGRN, in any kind of classification model when making predictions.
+      Specific Shapley value calculation or approximation methods are implemented with \emph{SHAP}\cite{lundberg2017unified} and applied to different algorithms as shown in Table \ref{shap}.
+      We utilize \emph{softmax} function to normalize feature importance scores and define the normalization function as:
 
@@
 
-      \noindent Here $X$ is total set of all features, and $F(x)$ is the importance estimating method of individual classification model being interpreted.\
+      \noindent Here $X$ denotes the total set of all features, and $F(x)$ denotes importance score estimation method.\
       If the feature importance can be approached with internalized method $f(x)$, $F(x)$ is set as:
@@
 
-      \noindent After all selected classification models $M$ have been interpreted, we can integrate the feature importance matrices weighted with corresponding models' $L_{CE}$ to one matrix $A$ as:\
+      \noindent After all selected classification models $M$ have been interpreted, we can integrate the feature importance matrices weighted by the corresponding models' $L_{CE}$ to one matrix $A$ as:\
 
@@
 
-      \noindent Then, generalized importance values are obtained through z-score calculation and later sorted by descending order:\
+      \noindent Then, generalized importance values are obtained through z-score calculation and later sorted descendingly:\
 
@@
           \label{shap}
-          Classifier algorithms with applicable Shapley value approximating methods.
-          Algorithms marked with \textbf{*} have internalized feature importance estimating methods which will be applied with higher priority than Shapley value based methods.
-          GBDT implemented with \emph{XGBoost}\cite{chen2016xgboost} can have feature importance approximated with average weight gain at each split involving the feature.
-          Linear SVM implemented with \emph{scikit-learn}\cite{scikit-learn} can have the importance estimated with feature coefficient or using Linear Explainer.
-          However, for SVM with kernel function, the feature coefficient estimation would be inappropriate, and feature importance should be approximated with Kernel Explainer.
+          Classifier algorithms with applicable Shapley value approximation methods.
+          Algorithms marked with \textbf{*} have internalized feature importance estimation methods which will be applied with higher priority than Shapley value based methods.
+          GBDT implemented with \emph{XGBoost}\cite{chen2016xgboost} can have feature importance approximated by the average weight gain at each split involving the feature.
+          Linear SVM implemented with \emph{scikit-learn}\cite{scikit-learn} can have importance scores estimated with feature coefficients or using Linear Explainer.
+          However, the feature coefficient estimation should be inappropriate for SVM with kernel function, While feature importance scores should be approximated with Kernel Explainer only.
         }
@@
     \label{step4}
-    To extract GRPs can effectively define sample class differences, AGEAS iteratively initializes classification models with configurations gained from \hyperref[step2]{Step 2}, trains them with randomly selected $\alpha_{max}$ portion of psGRNs scaled after \hyperref[step3]{Step 3}, and interpret every models' correct predictions as mentioned in \hyperref[features_importances]{subsection} above.
-    At each iteration, AGEAS receives a z-score scaled feature importance matrix $A$ and add up each GRP's score accordingly from matrix $A'$ kept from previous iteration if there is one.
-    Then, top $a$ (default set as 100) ranked GRPs having z-score greater than $0.0$ extracted from $A$ are compared with GRPs extracted from $A'$ by same setting.
-    If less than $d$ (default set as 0.05) portion of GRPs are distinct for GRP sets stratified from $A$ and $A'$, AGEAS will consider the GRP extration result from this iteration being consistent with previous one.
-    Extraction iteration will terminate if either encountering $n$ (default set as 3) continuous consistent result or running out of preset iteration number (default set as 10).
-    All feature importance scores in matrix $A$ from last iteration are divided by total extraction iteration number processed, and top $a$ ranked GRPs are considered as key GRPs for sample class differentiation and passed to next step.
+    To extract GRPs capable to effectively define sample class differences, AGEAS iteratively initializes classification models with configurations kept from \hyperref[step2]{Step 2}, trains them with randomly selected $\alpha_{max}$ portion of rescaled psGRNs from \hyperref[step3]{Step 3}, and interpret every models' correct predictions with methods mentioned in \hyperref[features_importances]{subsection}.
+    At each iteration, AGEAS receives a z-score scaled feature importance score matrix $A$ and add up each GRP's score accordingly from matrix $A'$ kept from previous iteration if available.
+    Then, top $a$ (default set as 100) ranked GRPs, scored greater than $0.0$ as well, are compared with GRPs extracted from $A'$ by same setting.
+    If less than $d$ (default set as 0.05) portion of GRPs are distinct for top scored GRP sets from $A$ and $A'$, AGEAS will consider the GRP extration result of current iteration being consistent with previous iteration.
+    Extraction loop will terminate if AGEAS is either encountering $n$ (default set as 3) continuous consistent result or running out of preset iteration number (default set as 10).
+    All feature importance scores in matrix $A$ from last iteration are divided by total extraction iteration number processed, and top $a$ ranked GRPs are considered as important GRPs for sample class differentiation and passed to next step.
 
@@
     \label{step5}
-    Analoging every GRP previously extracted or separated with high z-score in \hyperref[step3]{Step 3} as a directional edge connecting two gene vertices, equivalent to a TF and a gene, in graph theory, AGEAS attempts to reconstruct a network graph representing regulatory differences between query sample classes.
-    Since there is no guarantee on all GRP edges can be connected, some regulatory relationships between gene vertices could be missed.
-    Hence, AGEAS utilizes meta-GRN gained from \hyperref[step1]{Step 1} to find GRPs which can further elucidate the regulatory relationships and adds the GRPs back to the network graph.
+    Analogizing every GRP previously extracted in \hyperref[step4]{Step 4} or separated as outlier in \hyperref[step3]{Step 3} as a directional edge connecting a TF vertex with a targetome vertex, AGEAS attempts to reconstruct a GRN graph representing regulatory differences between query sample classes.
+    Since there is no guarantee on whether all extracted GRP edges can be connected or not, some regulatory relationships between gene vertices could be absent.
+    Hence, AGEAS utilizes meta-GRN gained from \hyperref[step1]{Step 1} to find GRPs which can further elucidate the regulatory relationships and adds those GRPs as supportive edges.
 
-    For a limited iteration time (default set as  1), AGEAS exhaustively search meta-GRN for TFs which can directly regulate any genes or TFs already covered in the network graph and add the returned TFs as new vertices.
-    Next, any GRP in meta-GRN capable to connect two distinct vertices will be added if it is not covered yet.
-    The network graph after expansion above represents the key genetic regulatory differences AGEAS extracted from input sample classes.
+    For a limited iteration time (default set as  1), AGEAS exhaustively search meta-GRN for TFs which can directly interact with any gene or TF already covered in extracted GRPs and add the returned TFs as new vertices.
+    Next, any GRP in meta-GRN capable to connect two distinct vertices will be included as supportive GRP in extraction result.
+    After expansion procedure above, the extracted GRN graph represents key genetic regulatory differences between input sample classes.
 
@@
   \label{res}
-  To assess predictive power of utilizing extraction result of AGEAS, we first applied AGEAS to study somatic reprogramming to induced pluripotent stem cells (iPSC) achieved in mice by the year 2006, \cite{yamanaka_2006} milestone discovery of cell plasticity.
+  To assess predictive power of utilizing extraction result of AGEAS, we primarily applied AGEAS to study somatic reprogramming of induced pluripotent stem cells (iPSC) achieved in mice by the year 2006, \cite{yamanaka_2006} milestone discovery of cell plasticity.
 \cite{cell_repro_review}
   With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, public scRNA-seq based GEMs of embryonic stem cells (ESCs) and mouse embryonic fibroblasts (MEFs) shown in Table \ref{geo_table} were used as input.
-  The extraction result can be summarized as TF regulons, and TFs having highest regulatory degree in all extracted GRPs are marked as top TFs (Figure \ref{result_figs}a).
+  The extraction result can be summarized as TF regulons, and TFs having highest regulatory degree in extracted GRN atlas are marked as top TFs (Figure \ref{result_figs}a).
 
   Among top TFs, Pou5f1 (Oct4) has more association with GRPs extracted as important differential regulatory element between MEF and ESC than any other TFs while forming largest regulon and having expression pattern significantly favoring ESC.
-  Thus, we can infer Pou5f1 is key regulatory element associated with ESC identity.
+  Thus, we infer Pou5f1 is key regulatory element associated with ESC identity.
   Extensive studies already addressed Pou5f1's important role in pluripotency maintenance. \cite{niwa_2007, oct4_1, oct4_2}
-  Moreover, to implement cell reprogramming to iPSC, Nanog and Sox2 are also noteworthy since they are closely interacting with Pou5f1 in extracted network, having high regulatory degrees, and differently expressed in ESC.
+  Moreover, to implement cell reprogramming of iPSC, Nanog and Sox2 are also noteworthy since they are closely interacting with Pou5f1 in extracted network, having high regulatory degrees, and differently expressed in ESC.
   Multiple previous studies confirmed that all of Oct4, Nanog, and Sox2 are playing important role to induce cell conversion from somatic cell to iPSC.
@@
 
-  Therefore, we suppose investigating TFs acting as common regulatory sources in extracted important differential GRPs and correspond regulons can effectively study differences between cell types cell states.
+  Therefore, we suppose investigating TFs acting as common regulatory sources in extracted important differential GRPs and correspond regulons can effectively study differences between cell types or cell states.
   % \subsection*{In silico evaluations}
   To further address AGEAS's applicability and limitation, we applied AGEAS to three other scRNA-seq based studies in distinct research areas.
-  With all default settings describe in \hyperref[method]{Method} section above, we can assess AGEAS's performance in following scenarios with public data set (Table \ref{geo_table}):
+  With all default settings describe in \hyperref[method]{Method} section above, we evaluated AGEAS's performance in following scenarios with public data set (Table \ref{geo_table}):
 
@@
 
-        Through stratification of all extracted GRPs, we only found HDAC2 and RBPJ as potential upstream regulatory elements of all ISL1, ELF3, and PBX3.
+        Through stratification of all extracted GRPs, we only found HDAC2 and RBPJ can potentially regulate all of ISL1, ELF3, and PBX3.
         Few reports demonstrated HDAC2 is associated with neurogenesis of radial glial cells. \cite{hdac2_dan_1, hdac2_dan_2}
@@
         Original research where we retrieved scRNA-seq data also demonstrated ASCL1 as necessary factor regulating DA neurotransmitter selection. \cite{ASCL1_dopaminergic_neuron_2021}
-        Although AGEAS extracts ASCL1 as one of top TFs; however, no direct regulatory relationship between RBPJ and ASCL1 is identified.
+        Although AGEAS extracted ASCL1 as one of top TFs, no direct regulatory relationship between RBPJ and ASCL1 was identified.
         % PHOX2B, and ELF3 are regulating essential functions differentiating DANs from neural progenitors referring to their correspond regulon sizes and differential expression profiles.
@@
 
-        To address the performance of AGEAS while analyzing cell physiological development, scRNA-seq data of cardiomyocytes (CMs) in postnatal day 7 mice (P7) and day 28 mice (P28) are used as input for extracting key genetic regulatory elements in postnatal cardiomyocyte maturation.
+        To address the performance of AGEAS while analyzing cell physiological development, scRNA-seq data of cardiomyocytes (CMs) in postnatal day 7 mice (P7) and day 28 mice (P28) are used as input for extracting key genetic regulatory elements in postnatal CM maturation.
 
-        As indicated by extracted differential GRPs, we primarily investigated Sp1 and Esr1 ($ER\alpha$) which also have top regulatory degrees and considerably expression changes (Figure \ref{result_figs}c).
+        As indicated by extracted differential GRPs, we firstly investigated Sp1 and Esr1 ($ER\alpha$) which also have top regulatory degrees and considerably differential expression profiles (Figure \ref{result_figs}c).
         Previous studies demonstrated that Sp1 promotes CM hypertrophy \cite{sp1_hypertrophy} and maturation of electrophysiology, $Ca^{2+}$ handling. \cite{Sp1_electrophysiologt, CM_mature}
@@
 
-        Beside inter-regulation between Sp1 and Esr1, 3 other top TFs (Srf, Cebpb, Rest) and 2 TFs forming relatively small regulons (Gata4, Prox1), are expected to have reversible regulation with both Sp1 and Esr1 based on extraction network.
-        All 5 TFs were found having CM maturation related functions. (Table \ref{interact_TFs})
+        Beside inter-regulation between Sp1 and Esr1, three other top TFs (Srf, Cebpb, Rest) and two TFs forming relatively small regulons (Gata4, Prox1), are expected to interact with both Sp1 and Esr1 based on extraction network.
+        All five TFs were found having CM maturation related functions. (Table \ref{interact_TFs})
 
@@
 
-        Here we address AGEAS's applicability on cell pathological development studies through analyzing hepatic stellate cells (HSCs) in mice liver administrated with chronic carbon tetrachloride ($CCl_4$) for 6 weeks and according portal fibroblasts (PF) simulating activated HSCs.
+        Here we address AGEAS's applicability on cell pathological development studies through analyzing hepatic stellate cells (HSCs) in mice liver administrated with chronic carbon tetrachloride ($CCl_4$) for six weeks and according portal fibroblasts (PFs) simulating activated HSCs.
 
         Based on extracted important GRPs, we identified Mef2c, Jun, and Jund as potential representatives of key regulatory elements in HSC activation (Figure \ref{result_figs}d).
-        As TF extracted with most important GRPs, Mef2c has been well-documented as key regulator in HSC activation. \cite{mef2c_1, mef2c_2, mef2c_3}
-        Extensive studies also found Jun and Jund, both being functional components of the AP1 TF complex, essential for fibrosis-related HSC activation and profibrogenic process.
+        As the TF extracted with most important GRPs, Mef2c has been well-documented as key regulator in HSC activation. \cite{mef2c_1, mef2c_2, mef2c_3}
+        Extensive studies also found Jun and Jund, both being functional components of the AP1 TF complex, are essential for fibrosis-related HSC activation and profibrogenic process.
 \cite{ap1_hsc_1, ap1_hsc_2, ap1_hsc_3, ap1_hsc_4}
@@
         Analyzing TF regulons of Mef2c, Jun, and Jund, we suppose Mef2c is acting as targetome of Jund and inter-regulatory element of Jun.
-        While no regulatory relationship between Jund and Jun determined, 3 extracted top TFs (Lhx2, Nfib, Junb) can potentially influence expressions of both Jund and Jun.
-        Since Junb is also functional component of AP1, we infer it associated with HSC activation in a similar manner.
+        While no regulatory relationship between Jund and Jun determined, three extracted top TFs (Lhx2, Nfib, Junb) can potentially affect expressions of both Jund and Jun.
+        Junb, another functional component of AP1, is also reported affecting with HSC activation \cite{ap1_hsc_5}.
         Furthermore, Lhx2 was found indispensable for quiescent HSCs. \cite{lhx2_fibro, Lhx2_hsc_1}
@@
   With result achieved so far, AGEAS shows robustness in extracting key regulatory elements for several biological researches.
-  Key TFs inferred by extracted important GRPs and regulon analysis in all 4 $in$ $silico$ cases were confirmed informative to reveal main functionalities responsible for biological process of interest.
-  Furthermore, the direct extractions of ISL1 in DAN differentiation and Jund in HSC activation as regulatory source in top amount of important GRPs can demonstrate that AGEAS is not focusing solely on TF regulon sizes in reconstructed meta-GRN nor expression differences between sample classes.
+  Key TFs inferred by extracted important GRPs and regulon analysis in all four $in$ $silico$ cases were confirmed informative to reveal main functionalities responsible for biological process of interest.
+  Furthermore, the direct extractions of ISL1 in DAN differentiation and Jund in HSC activation as regulatory source in top amount of important GRPs can demonstrate that AGEAS is not solely focusing on TF regulon sizes in reconstructed meta-GRN nor expression differences between sample classes.
   % Also, $in$ $vitro$ experiments indicate great potential in AGEAS to promote method development in phenotypic manipulation.
@@
   \label{disc}
-  Considering the rapid development of both sequencing technology and machine learning algorithms, we implemented
-  AGEAS with modular design.
-  In data preprocessing part, the meta-GRN reconstruction section can be replaced with other methods to further increase fidelity of regulatory relationships or integrating more information such as cis-regulatory elements (CREs) accessibility which can be obtained from Assay for Transposase-Accessible Chromatin Sequencing (ATAC-seq) data.
+  Considering the rapid development of both sequencing technology and machine learning algorithms, we implemented AGEAS with modular design.
+  In data preprocessing part, the meta-GRN reconstruction section can be replaced with other methods to further increase fidelity of regulatory relationships or integrating more information, such as cis-regulatory elements (CREs) accessibility which can be obtained from Assay for Transposase-Accessible Chromatin Sequencing (ATAC-seq) data.
   Moreover, CRE accessibility information combining with motif enrichment analysis is proved capable to identity potential regulatory pathways replacing ChIP-seq based dataset AGEAS utilizing in present study.
@@
 
-  Due to the stochastic nature of AGEAS, extraction results of AGEAS are not expected to stay identical for repeated applications with exactly same inputs.
+  Due to the stochastic nature of AGEAS, extraction results of AGEAS are not expected to stay identical for repeated applications even with exactly same inputs.
   Main reason underlying the inconsistency is caused by how AGEAS attempt to obtain top performing models for later prediction interpretations.
@@
   % Furthermore, $in$ $vivo$ experiments are also necessary to evaluate functionality of Lhx2 and associated pathways for higher fidelity.
+
+\section*{Acknowledgement}
+  We sincerely thank Cher Li and Jie Wang for inspirations and supports.
 

### 2022-10-14 docs/manuscript/main.tex
v0.0.1a9
draft 1 finished

@@
       However, enabling the log2FC filter is not encouraged, considering that upstream TFs indirectly regulate key genes associated with phenomena of interest may not be significantly differential expressed.
-      The lof2FC filter shall mostly be used to decrease meta-GRN's total degree in a compromising position caused by limited computational resources.
+      The log2FC filter shall mostly be used to decrease meta-GRN's total degree in a compromising position caused by limited computational resources.
       After differential expression based filters, a standard deviation ($\sigma$) filter is applied to exclude genes with low expression level or merely affected by dynamic expression status of other genes.
@@
     \label{step4}
-    To extract GRPs capable to effectively define sample class differences, AGEAS iteratively initializes classification models with configurations kept from \hyperref[step2]{Step 2}, trains them with randomly selected $\alpha_{max}$ portion of rescaled psGRNs from \hyperref[step3]{Step 3}, and interpret every models' correct predictions with methods mentioned in \hyperref[features_importances]{subsection}.
-    At each iteration, AGEAS receives a z-score scaled feature importance score matrix $A$ and add up each GRP's score accordingly from matrix $A'$ kept from previous iteration if available.
-    Then, top $a$ (default set as 100) ranked GRPs, scored greater than $0.0$ as well, are compared with GRPs extracted from $A'$ by same setting.
-    If less than $d$ (default set as 0.05) portion of GRPs are distinct for top scored GRP sets from $A$ and $A'$, AGEAS will consider the GRP extration result of current iteration being consistent with previous iteration.
-    Extraction loop will terminate if AGEAS is either encountering $n$ (default set as 3) continuous consistent result or running out of preset iteration number (default set as 10).
-    All feature importance scores in matrix $A$ from last iteration are divided by total extraction iteration number processed, and top $a$ ranked GRPs are considered as important GRPs for sample class differentiation and passed to next step.
+    To extract GRPs capable of effectively defining sample class differences, AGEAS iteratively initializes classification models with configurations kept from \hyperref[step2]{Step 2}, trains them with randomly selected $\alpha_{max}$ portion of rescaled psGRNs from \hyperref[step3]{Step 3}, and interprets every models' accurate predictions with methods mentioned in \hyperref[features_importances]{subsection}.
+    At each iteration, AGEAS receives a feature importance matrix $A$ re-scaled by z-score and adds up each GRP's score accordingly from matrix $A'$ kept from previous iteration if available.
+    Then, top $a$, by default 100, ranked GRPs, whose scores are also greater than $0.0$, are compared with GRPs extracted from $A'$ by the same setting.
+    If changing portion of GRPs for top scored GRP sets from $A$ and $A'$ is less than $d$, by default 0.05, AGEAS will consider the GRP extraction result of current iteration consistent with previous iteration.
+    Extraction loop will terminate if AGEAS encounters $n$ (default set as 3) continuous consistent result or runs out of preset iteration number (default set as 10).
+    All feature importance scores in matrix $A$ from last iteration are divided by the total iteration number processed, and top $a$ ranked GRPs are considered as important GRPs for sample class differentiation.
 
@@
     Since there is no guarantee on whether all extracted GRP edges can be connected or not, some regulatory relationships between gene vertices could be absent.
-    Hence, AGEAS utilizes meta-GRN gained from \hyperref[step1]{Step 1} to find GRPs which can further elucidate the regulatory relationships and adds those GRPs as supportive edges.
+    Hence, AGEAS utilizes meta-GRN gained from \hyperref[step1]{Step 1} to find GRPs, which can further elucidate the regulatory relationships, and to use those GRPs as supportive edges.
 
-    For a limited iteration time (default set as  1), AGEAS exhaustively search meta-GRN for TFs which can directly interact with any gene or TF already covered in extracted GRPs and add the returned TFs as new vertices.
-    Next, any GRP in meta-GRN capable to connect two distinct vertices will be included as supportive GRP in extraction result.
+    For a limited iteration time (default set as  1), AGEAS exhaustively searches meta-GRN for TFs which can directly interact with any gene already covered in extracted GRPs and add the returned TFs as new vertices.
+    Next, any GRP in meta-GRN capable of connecting two distinct vertices will be included as supportive GRP in extraction result.
     After expansion procedure above, the extracted GRN graph represents key genetic regulatory differences between input sample classes.
@@
   \label{res}
-  To assess predictive power of utilizing extraction result of AGEAS, we primarily applied AGEAS to study somatic reprogramming of induced pluripotent stem cells (iPSC) achieved in mice by the year 2006, \cite{yamanaka_2006} milestone discovery of cell plasticity.
+  To assess predictive power of utilizing extraction result of AGEAS, we primarily applied AGEAS to study somatic reprogramming of induced pluripotent stem cells (iPSC) in mice, \cite{yamanaka_2006} a milestone discovery of cell plasticity.
 \cite{cell_repro_review}
-  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, public scRNA-seq based GEMs of embryonic stem cells (ESCs) and mouse embryonic fibroblasts (MEFs) shown in Table \ref{geo_table} were used as input.
-  The extraction result can be summarized as TF regulons, and TFs having highest regulatory degree in extracted GRN atlas are marked as top TFs (Figure \ref{result_figs}a).
+  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, we use public scRNA-seq based GEMs of embryonic stem cells (ESCs) and mouse embryonic fibroblasts (MEFs) shown in Table \ref{geo_table} as inputs.
+  The extraction result can be summarized as TF regulons, and TFs with highest regulatory degree in extracted GRN atlas are marked as top TFs (Figure \ref{result_figs}a).
 
-  Among top TFs, Pou5f1 (Oct4) has more association with GRPs extracted as important differential regulatory element between MEF and ESC than any other TFs while forming largest regulon and having expression pattern significantly favoring ESC.
-  Thus, we infer Pou5f1 is key regulatory element associated with ESC identity.
+  Among top TFs, Pou5f1 (Oct4) associates with GRPs extracted as important differential regulatory element between MEF and ESC more than any other TFs, while forming largest regulon and having expression pattern significantly favoring ESC.
+  Thus, we infer Pou5f1 is the key regulatory element associated with ESC identity.
   Extensive studies already addressed Pou5f1's important role in pluripotency maintenance. \cite{niwa_2007, oct4_1, oct4_2}
-  Moreover, to implement cell reprogramming of iPSC, Nanog and Sox2 are also noteworthy since they are closely interacting with Pou5f1 in extracted network, having high regulatory degrees, and differently expressed in ESC.
-  Multiple previous studies confirmed that all of Oct4, Nanog, and Sox2 are playing important role to induce cell conversion from somatic cell to iPSC.
+  Moreover, to implement cell reprogramming of iPSC, Nanog and Sox2 are noteworthy, since they closely interact with Pou5f1 in extracted network, have high regulatory degrees, and are differently expressed in ESC.
+  Multiple previous studies confirmed that all of Oct4, Nanog, and Sox2 are playing important roles to induce cell conversion from somatic cell to iPSC.
 \cite{yamanaka_2006, ips7f, ipsOK, oct4_nanog_sox2_lin28, oct4_nanog_sox2}
-  Cebpb, Hdac2, and Smc3, extracted as top TFs frequently acting as regulatory source in extracted important GRPs and directly affecting Pou5f1 expression, were also reported with relevant functions.
-\cite{cebpb_ipsc, hdac2_ipsc, rad21_smc3_esc}
+  Cebpb, Hdac2, and Smc3, extracted as top TFs directly affecting Pou5f1 expression, were also reported with relevant functions. \cite{cebpb_ipsc, hdac2_ipsc, rad21_smc3_esc}
 
-  Therefore, we suppose investigating TFs acting as common regulatory sources in extracted important differential GRPs and correspond regulons can effectively study differences between cell types or cell states.
+  Therefore, we infer that the investigation of TFs as common regulatory sources in important differential GRPs and corresponding regulons can effectively reflect differences between cell types or cell states.
   % \subsection*{In silico evaluations}
   To further address AGEAS's applicability and limitation, we applied AGEAS to three other scRNA-seq based studies in distinct research areas.
-  With all default settings describe in \hyperref[method]{Method} section above, we evaluated AGEAS's performance in following scenarios with public data set (Table \ref{geo_table}):
+  With default settings described in \hyperref[method]{Method} section above, we evaluated AGEAS's performance in following scenarios with public dataset (Table \ref{geo_table}):
 
@@
       \setlength\itemsep{0em}
-      \item {\textbf{Dopaminergic neuron generation}}:
+      \item {\textbf{Dopaminergic neuron differentiation}}:
 
-        Analyzing difference between human iPSC-derived radial glial / neuronal co-culture, as neural progenitors,\cite{ASCL1_dopaminergic_neuron_2021} and tyrosine hydroxylase (TH) expressing purified dopaminergic neurons (DANs), we address the applicability of AGEAS on cell subtype differentiation problems.
+        We address the applicability of AGEAS on cell subtype differentiation problems by analyzing the difference between human iPSC-derived radial glial / neuronal co-culture as neural progenitors\cite{ASCL1_dopaminergic_neuron_2021} and tyrosine hydroxylase (TH) expressing purified dopaminergic neurons (DANs).
 
-        From extracted TFs (Figure \ref{result_figs}b), we hypothesize ISL1, ELF3, and PBX3 playing important role in DAN differentiation due to their high regulatory degree in extracted important GRPs.
-        Previously, ISL1 was determined essential for differentiation of prethalamic DANs, \cite{isl1_da} and ELF3 was found to be neuronal precursor cell marker associated with neural stem cell development, \cite{ELF3_precursor_marker} consistent with it's high expression level in neuronal co-culture samples.
-        Moreover, a DAN development study reported PBX3 being required for correct differentiation of neuroblast, product of radial glial cell, into midbrain DAN and survival of midbrain DAN.
+        From extracted TFs (Figure \ref{result_figs}b), we hypothesized that ISL1, ELF3, and PBX3 play important roles in DAN differentiation due to their high regulatory degree in extracted important GRPs.
+        Previously, ISL1 was determined essential for differentiation of prethalamic DANs. \cite{isl1_da}
+        ELF3 was found to be the neuronal precursor cell marker associated with neural stem cell development. \cite{ELF3_precursor_marker}
+        This is consistent with ELF3's high expression level in neuronal co-culture samples.
+        Moreover, a DAN development study reported that PBX3 is required for correct differentiation of neuroblast, production of radial glial cell, into midbrain DAN and survival of midbrain DAN.
 \cite{pbx3_dan}
 
-        Through stratification of all extracted GRPs, we only found HDAC2 and RBPJ can potentially regulate all of ISL1, ELF3, and PBX3.
-        Few reports demonstrated HDAC2 is associated with neurogenesis of radial glial cells. \cite{hdac2_dan_1, hdac2_dan_2}
+        Through stratifying all extracted GRPs, we only found that HDAC2 and RBPJ can potentially regulate all of ISL1, ELF3, and PBX3.
+        Few reports demonstrated the association of HDAC2 with neurogenesis of radial glial cells. \cite{hdac2_dan_1, hdac2_dan_2}
         Nevertheless, HDAC2's role in DAN differentiation is yet to be clarified.
-        RBPJ was reported essential for DAN survival and affecting DAN development by regulating ASCL1 which is an essential factor in neurogenesis. \cite{rbpj_1, rbpj_2}
-        Original research where we retrieved scRNA-seq data also demonstrated ASCL1 as necessary factor regulating DA neurotransmitter selection. \cite{ASCL1_dopaminergic_neuron_2021}
-        Although AGEAS extracted ASCL1 as one of top TFs, no direct regulatory relationship between RBPJ and ASCL1 was identified.
+        RBPJ was reported to be essential for DAN survival and to affect DAN development by regulating ASCL1, a essential factor in neurogenesis. \cite{rbpj_1, rbpj_2}
+        The original research where we retrieved scRNA-seq data from also demonstrated that ASCL1 is a necessary factor to regulate DA neurotransmitter selection. \cite{ASCL1_dopaminergic_neuron_2021}
+        Although AGEAS extracted ASCL1 as one of the top TFs, no direct regulatory relationship between RBPJ and ASCL1 was identified.
         % PHOX2B, and ELF3 are regulating essential functions differentiating DANs from neural progenitors referring to their correspond regulon sizes and differential expression profiles.
@@
 
-        To address the performance of AGEAS while analyzing cell physiological development, scRNA-seq data of cardiomyocytes (CMs) in postnatal day 7 mice (P7) and day 28 mice (P28) are used as input for extracting key genetic regulatory elements in postnatal CM maturation.
+        To address the performance of AGEAS to analyze cell physiological development, scRNA-seq data of cardiomyocytes (CMs) in postnatal day 7 mice (P7) and day 28 mice (P28) are used as inputs for extracting key genetic regulatory elements in postnatal CM maturation.
 
-        As indicated by extracted differential GRPs, we firstly investigated Sp1 and Esr1 ($ER\alpha$) which also have top regulatory degrees and considerably differential expression profiles (Figure \ref{result_figs}c).
+        As indicated by important differential GRPs, we first investigated Sp1 and Esr1 ($ER\alpha$) that also have top regulatory degrees and considerably differential expression profiles (Figure \ref{result_figs}c).
         Previous studies demonstrated that Sp1 promotes CM hypertrophy \cite{sp1_hypertrophy} and maturation of electrophysiology, $Ca^{2+}$ handling. \cite{Sp1_electrophysiologt, CM_mature}
@@
 
-        Beside inter-regulation between Sp1 and Esr1, three other top TFs (Srf, Cebpb, Rest) and two TFs forming relatively small regulons (Gata4, Prox1), are expected to interact with both Sp1 and Esr1 based on extraction network.
-        All five TFs were found having CM maturation related functions. (Table \ref{interact_TFs})
+        Beside the inter-regulation between Sp1 and Esr1, three other top TFs (Srf, Cebpb, Rest) and two TFs forming relatively small regulons (Gata4, Prox1), are expected to interact with both Sp1 and Esr1 based on extraction network.
+        All five TFs were found to have CM maturation related functions. (Table \ref{interact_TFs})
 
@@
               \label{interact_TFs}
-              TFs interacting with both Sp1 and Esr1 order by extracted regulon size.
+              TFs interacting with both Sp1 and Esr1 order by regulatory degree in extracted GRNs.
             }
@@
 
-        Here we address AGEAS's applicability on cell pathological development studies through analyzing hepatic stellate cells (HSCs) in mice liver administrated with chronic carbon tetrachloride ($CCl_4$) for six weeks and according portal fibroblasts (PFs) simulating activated HSCs.
+        Here we address AGEAS's applicability on cell pathological development studies through analyzing hepatic stellate cells (HSCs) and portal fibroblasts (PFs) simulating activated HSCs in mice liver administrated with chronic carbon tetrachloride ($CCl_4$) for six weeks.
 
-        Based on extracted important GRPs, we identified Mef2c, Jun, and Jund as potential representatives of key regulatory elements in HSC activation (Figure \ref{result_figs}d).
-        As the TF extracted with most important GRPs, Mef2c has been well-documented as key regulator in HSC activation. \cite{mef2c_1, mef2c_2, mef2c_3}
-        Extensive studies also found Jun and Jund, both being functional components of the AP1 TF complex, are essential for fibrosis-related HSC activation and profibrogenic process.
+        Based on extracted important GRPs, we identified Mef2c, Jun, and JunD as potential representatives of key regulatory elements in HSC activation (Figure \ref{result_figs}d).
+        As the TF extracted with most important GRPs, Mef2c has been well-documented as the key regulator in HSC activation. \cite{mef2c_1, mef2c_2, mef2c_3}
+        Extensive studies also found Jun and JunD, functional components of the AP1 TF complex, are essential for fibrosis-related HSC activation and profibrogenic process.
 \cite{ap1_hsc_1, ap1_hsc_2, ap1_hsc_3, ap1_hsc_4}
 
-        Analyzing TF regulons of Mef2c, Jun, and Jund, we suppose Mef2c is acting as targetome of Jund and inter-regulatory element of Jun.
-        While no regulatory relationship between Jund and Jun determined, three extracted top TFs (Lhx2, Nfib, Junb) can potentially affect expressions of both Jund and Jun.
-        Junb, another functional component of AP1, is also reported affecting with HSC activation \cite{ap1_hsc_5}.
+        Analyzing TF regulons of Mef2c, Jun, and JunD, we believe that Mef2c is targetome of JunD and the inter-regulatory element of Jun.
+        While no regulatory relationship between JunD and Jun determined, three extracted top TFs (Lhx2, Nfib, JunB) can potentially affect expressions of both JunD and Jun.
+        JunB, another functional component of AP1, is also reported to  affect HSC activation \cite{ap1_hsc_5}.
         Furthermore, Lhx2 was found indispensable for quiescent HSCs. \cite{lhx2_fibro, Lhx2_hsc_1}
-        Although, little literature addressed Nfib's role in HSC, Nfib was reported acting as anti-apoptotic gene for cell proliferation during $CCl_4$ induced liver damage. \cite{Nfib_sadly}
+        Although little literature had addressed Nfib's role in HSC, Nfib was reported to be the anti-apoptotic gene for cell proliferation during $CCl_4$ induced liver damage. \cite{Nfib_sadly}
+
     \end{itemize}
@@
 \section*{Conclusion}
-  With result achieved so far, AGEAS shows robustness in extracting key regulatory elements for several biological researches.
-  Key TFs inferred by extracted important GRPs and regulon analysis in all four $in$ $silico$ cases were confirmed informative to reveal main functionalities responsible for biological process of interest.
-  Furthermore, the direct extractions of ISL1 in DAN differentiation and Jund in HSC activation as regulatory source in top amount of important GRPs can demonstrate that AGEAS is not solely focusing on TF regulon sizes in reconstructed meta-GRN nor expression differences between sample classes.
+  In summary, AGEAS shows robustness in extracting key regulatory elements in several biological studies.
+  Key TFs inferred by important differential GRPs and regulon analysis in all four $in$ $silico$ cases were confirmed informative to reveal main functionalities responsible for biological process of interest.
+  Furthermore, the direct extractions of ISL1 in DAN differentiation and JunD in HSC activation demonstrated that AGEAS is neither focusing solely on the regulatory degrees in reconstructed meta-GRN nor the expression differences between sample classes.
   % Also, $in$ $vitro$ experiments indicate great potential in AGEAS to promote method development in phenotypic manipulation.
@@
   % However, whether extracted regulatory elements covering all functional aspects of studying biological phenomena, admittedly, remains undetermined due to lack of validation for GRPs' activities.
-  Overall, we anticipate that AGEAS will become useful in providing insightful regulatory information and promoting pioneer researches in revealing complicate mechanism behind biological phenomena.
+  Overall, we anticipate that AGEAS is useful in providing insightful regulatory information and in promoting pioneer researches that reveal complicated mechanism behind biological phenomena.
 
@@
   Considering the rapid development of both sequencing technology and machine learning algorithms, we implemented AGEAS with modular design.
-  In data preprocessing part, the meta-GRN reconstruction section can be replaced with other methods to further increase fidelity of regulatory relationships or integrating more information, such as cis-regulatory elements (CREs) accessibility which can be obtained from Assay for Transposase-Accessible Chromatin Sequencing (ATAC-seq) data.
-  Moreover, CRE accessibility information combining with motif enrichment analysis is proved capable to identity potential regulatory pathways replacing ChIP-seq based dataset AGEAS utilizing in present study.
+  In the data preprocessing part, the meta-GRN reconstruction section can be replaced with other methods to further increase fidelity of regulatory relationships or integrating more information, such as cis-regulatory elements (CREs) accessibility, which can be obtained from Assay for Transposase-Accessible Chromatin Sequencing (ATAC-seq) data.
+  Moreover, CRE accessibility information combining with motif enrichment analysis is proved capable of identifying potential regulatory pathways to replace ChIP-seq based dataset utilized in the current study.
 \cite{scREMOTE}
-  Refine meta-GRN reconstruction method in consideration of having input data from simultaneous scRNA-seq and single cell ATAC-seq (scATAC-seq), such as SHARE-seq published in late 2020, \cite{share_seq} can potentially further improve applicability of AGEAS; however, accessibility of corresponding datasets will be essential for performance assessment and method development.
-  Similarly, initial set of classificaion models is also subject to be changed responding to future computational studies.
+  Refining meta-GRN reconstruction method in consideration of having input data from simultaneous scRNA-seq and single cell ATAC-seq (scATAC-seq), such as SHARE-seq published in late 2020, \cite{share_seq} can potentially further improve applicability of AGEAS; however, accessibility of corresponding datasets will be essential for performance assessment and method development.
+  Similarly, initial set of classification models is also subject to change in response to future computational studies.
 
-  Also, it is important to note that AGEAS can be applied with GEMs normalized with different methods on user's choice as well as derived from other sequencing technologies such as bulk RNA-seq or spatial sequencing in revealing tissue differences.
-  Replacing transcriptiomic data with proteomic data may also be achievable to analysis protein interaction networks.
-  However, larger scale of applicability tests shall be performed in advance.
+  Also, it is important to note that AGEAS can be applied with GEMs normalized with different methods on user's choice, as well as derived from other sequencing technologies, such as bulk RNA-seq or spatial sequencing in revealing tissue differences.
+  Replacing transcriptiomic data with proteomic data may also be achievable in the analysis of protein interaction networks.
+  However, larger scale of applicability tests are necessary.
 
-  Due to the stochastic nature of AGEAS, extraction results of AGEAS are not expected to stay identical for repeated applications even with exactly same inputs.
-  Main reason underlying the inconsistency is caused by how AGEAS attempt to obtain top performing models for later prediction interpretations.
-  Repeated random subsets of psGRNs using in model training and selection are expected to vary for each application hence resulting in different performance of classification models and ranking results.
-  As a result, the importance values of GRPs might differ and slightly affect top TFs extracted later.
+  Due to the stochastic nature of AGEAS, extraction results of AGEAS are not expected to stay identical for repeated applications even with exactly the same inputs.
+  The main reason underlying the inconsistency is how AGEAS attempts to obtain top performing models for later prediction interpretations.
+  Repeated random subsets of psGRNs used in model training and selection are expected to vary for each application, hence results in different performances of classification models and ranking results.
+  As a result, the importance scores of GRPs might differ and slightly affect top TFs extracted later.
 
-  Two possible workarounds of inconsistent issue would be:
+  Two possible workarounds of the inconsistent issue would be:
   (i) manually set random seed for every process influencing subset selection.
   (ii) set multiple extractor unit and combine extraction results.
-  In present study, we found n = 4 units yielding relatively stable results, but this value could vary based on application scenario.
+  In the present study, we found that n = 4 units yield relatively stable results, but this value could vary based on application scenario.
 
@@
 \section*{Acknowledgement}
-  We sincerely thank Cher Li and Jie Wang for inspirations and supports.
+  We sincerely thank Cher Li and Jie Wang for inspiration; Augustine(Xiaoran) Yuan for reviewing and support.
 

### 2022-10-16 docs/manuscript/main.tex
v0.0.v1a9
minor updates

@@
 
-\author[1,2,*1,+]{Jack Yu}
 % \author[1,2,*1]{Jack Yu}
-\author[2,+]{Masayoshi Nakamoto}
-\author[1,*2,+]{Jiawang Tao}
+\author[1,+]{Masayoshi Nakamoto}
+\author[2,*1,+]{Jiawang Tao}
+\author[1,2,*2,+]{Jack Yu}
 
 % \author[2,+]{Derek Author}
-\affil[1]{Center for Health Research, Guangzhou Institutes of Biomedicine and Health, Chinese Academy of Sciences, Guangzhou 510530, China}
-\affil[2]{Shenzhen Mozhou Technology Co., Ltd, Shenzhen, China}
+\affil[1]{Shenzhen Mozhou Technology Co., Ltd, Shenzhen, China}
+\affil[2]{Center for Health Research, Guangzhou Institutes of Biomedicine and Health, Chinese Academy of Sciences, Guangzhou 510530, China}
 % \affil[2]{Affiliation, department, city, postcode, country}
-\affil[*1]{Correspondence: gyu17@alumni.jh.edu}
-\affil[*2]{Correspondence: tao\_jiawang@gibh.ac.cn}
+\affil[*1]{Correspondence: tao\_jiawang@gibh.ac.cn}
+\affil[*2]{Correspondence: gyu17@alumni.jh.edu}
 
@@
 \section*{Acknowledgement}
-  We sincerely thank Cher Li and Jie Wang for inspiration; Augustine(Xiaoran) Yuan for reviewing and support.
+  We sincerely thank Cher Li and Jie Wang for inspiration; Augustine(Xiaoran) Yuan and Elizabeth Bania for reviewing and support.
 

### 2022-12-05 docs/manuscript/main.tex
v0.0.1b1

@@
   \label{res}
-  To assess predictive power of utilizing extraction result of AGEAS, we primarily applied AGEAS to study somatic reprogramming of induced pluripotent stem cells (iPSC) in mice, \cite{yamanaka_2006} a milestone discovery of cell plasticity.
+  To assess predictive power of utilizing extraction result of AGEAS, we primarily applied AGEAS to study somatic cell reprogramming to induced pluripotent stem cells (iPSCs) in mice, \cite{yamanaka_2006} a milestone discovery of cell plasticity.
 \cite{cell_repro_review}
@@
 
-        Here we address AGEAS's applicability on cell pathological development studies through analyzing hepatic stellate cells (HSCs) and portal fibroblasts (PFs) simulating activated HSCs in mice liver administrated with chronic carbon tetrachloride ($CCl_4$) for six weeks.
+        Here we address AGEAS's applicability on cell pathological development studies through analyzing hepatic stellate cells (HSCs) and portal fibroblasts (PFs) simulating activated HSCs in mice liver administrated with carbon tetrachloride ($CCl_4$) for six weeks.
 
